### 2014-02-25 bullet_groups.tex
Article

\documentclass[12pt,preprint]{aastex}
% To highlight comments 
\usepackage{color}
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}

\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage{epsfig}  
\usepackage{float}
%\bibliographystyle{apj}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\ba{\begin{eqnarray}}
\def\ea{\end{eqnarray}}

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}  
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}  
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\bullb}{MACS J0025.4-1222}
\newcommand{\bulla}{1E0657---56} 
\shorttitle{Bullet Groups}
\shortauthors{Fern\'andez-Trincado et al.}

\begin{document}

\title{Bullet Groups in the Bolshoi Cosmological Simulation}
\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$ and T. Vergudo$^3$}
\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne, Besan\c{c}on, France\\
       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264, M\'erida 5101-A, Venezuela}

\begin{abstract}

We estimate the expected distribution of displacements between the host halo of dark matter and the 
substructure of dark matter most massive of the host, using a halo catalog from the Bolshoi simulation detected 
with the Bound Density Maximun (BDM) algorithm. We found that the probability of finding a system similar to the Bullet
Group with displacements of $\sim$400 kpch$^{-1}$ is between 40\% for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard 
model predicts this scenario and is consistent with recently observations of the object SL2S J08544-0121 that is 
a gravitational lens found in the SL2S and located at z$=0.35$.

\end{abstract}

\begin{keywords}
{cosmology: theory -- dark matter} 
\end{keywords}

\section{Introduction}

This paper is organized as the follows: In Section
\ref{simulation} we present the simulations.

\section{Simulation}
\label{simulation}

The analysis presented in this paper uses mainly the Bolshoi (250 Mpch$^{-1}$ simulation box, 1 kpch$^{-1}$ resolution) Database simulation described in
\citet{2011ApJ...740..102K}. The simulation follows the evolution of 8.6 billion particle cosmological N-body simulation
from z=80 to z=0 in a comoving cube of $250$ Mpch$^{-1}$
on a side. The cosmology used  corresponds to  the spatially flat
concordance model with the
following parameters:  the density parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the density parameter for baryonic matter
 $\Omega_b=0.0469$, the density parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
parameter $h=0.7$, the normalization of the Power spectrum $n=0.95$ and
the amplitude of mass density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number of particles used for each of
the DM component was $2048^3$, resulting in a mass resolution of $1.35 \times
10^8$ M$_{\odot}$h$^{-1}$.

\section{Cumulative Probability Distributions}
\label{cumulative distribution}

We selected four snapshot of the simulation for four different redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the 
distribution of redshift in the Figure 1 by \citet{verdugo}, and 
for each sample in redshift we selected the host halo with circular velocities greater than 300 kms$^{-1}$ and was split in two 
principal groups: The first group correspond to host halo with circular velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$
with mass in the range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range of mass of the
Bullet Groups, and second group correspond to host halo with circular velocities greater than 
700 kms$^{-1}$ with mass $\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet Clusters, in 
the Table \ref{table1} is shown the two groups selected in this work. For each group, we 
classified the corresponding substructures most massive and associated with the corresponding 
host halo. The configuration of this system is shown in 
Figure \ref{configuration}, where you can distinguish the host halo and substructure for a particular configuration in z$=0$. In 
this work, we estimate the expected distribution of displacements ($d_{real,(X,Y)}$) in the projection 2-D that can estimate by 
observations, these displacements correspond to the separation between the minimal potential of the host halo and the 
minimal potential of the substructure, both are dark matter distributions.\\

\begin{table*}
\begin{center}
\begin{tabular}{ccccccc}\hline\hline
Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
\end{tabular} 
\caption{Mass ranges for the two groups selected in this work in different redshifts.}
\label{table1}
\end{center}
\end{table*}

In order to explore the distribution of displacements expected in the observational, we define a new parameter given by:\\

\begin{equation}
 \frac{\nu_{circ,sub}}{\nu_{circ,halo}}=0.5
\end{equation}

Figure \ref{newparameter} shows the scatter plot of the parameter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$ vs the 
displacement ($d_{2d,(X,Y)}$) between the host halo and the substructure and for different redshifts. This parameter is 
consistent with the observations. The red star simbol in the Figure \ref{newparameter} is equal to 0.54 corresponding to 
the fraction in velocity dispersion in the line-of-sigth of the group SL2S SJ08544-0121 ($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and $\sigma_{substructure}=185^{+30}_{-62}$), reported by \citet{2013A&A...552A..80M}.
Based in the parameter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)>0.5$, we estimate the expected distribution of
displacements and this is shown in the Figure \ref{displacements} for the two groups classified in this work.

\begin{figure*}
\begin{center}
\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
\end{center}
\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
\label{configuration}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_7_2.eps}
\includegraphics[width=1.0\textwidth]{figure_7_3.eps}
\end{center}
\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$ vs $d_{2d,(X,Y)}$ for different redshifts. The 
horizontal dashed line correpond to $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the red star simbol correspond
to $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S SJ08544-0121 in \citet{2013A&A...552A..80M}. The 
four top panels are the sample with circular velocities $>700$ kms$^{-1}$ and the four down panels are the sample with 
circular velocities between 300 km s$^{-1}$ to 700 kms$^{-1}$.}
\label{newparameter}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.1\textwidth]{figure_7_1.eps}
\end{center}
\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements for the projection (X,Y). {\bf Left panel:} Sample with $\nu_{max}>700$ kms$^{-1}$ 
for different redshifts. The vertical dashed line, correspond to the separation between dark matter to dark matter estimate
in this work as the double of separation between the collisional gas and dark matter of 124$\pm$20 kpc reported
by \citet{gastaldello} for the group SL2S J08544-0121. 
{\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $ kms$^{-1}$ for different redshifts.} 
\label{displacements}
\end{figure*}

\subsection{Number expected of Bullet Groups in the sample}

In order of estimate the number of Bullet Groups expected in the Bolshoi Cosmological Simulation, we 
define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
we make the scalar product between the velocity vector and position vector that defines the separation between 
 the host halo and the substructure, as shown below: \\

 \begin{equation}
  cos(\theta)=\frac{\vec{\nu{}}\cdotp{}\vec{r}}{\left\|\nu{}\right\| \left\|r\right\|}
 \end{equation}

where, $\vec{\nu{}}=\vec{\nu}_{sub}-\vec{\nu}_{halo}$ and $\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, in the Figure \ref{cos_theta}
is shown the scatter plot of $cos(\theta{})$ vs $X_{off,new}=\frac{d_{2d,(X,Y)}}{R_{virial,halo}}=\frac{d_{real,(X,Y)}}{R_{virial,halo}}$.

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_8_1_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cos_theta}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{figure_8_3_nu=0.5_300kms_700kms.eps}
\end{center}
\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
\label{cumulative_cos}
\end{figure*}

\section{Summary}
\label{summary}

\section{Conclusions}
\label{conclusions}

\section*{Acknowledgements}

The CosmoSim database used in this paper is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP). The 
BolshoiP simulation was performed within the Bolshoi project of the University of California High-Performance 
AstroComputing Center (UC-HIPACC) and was run at the NASA Ames Research Center.

\begin{thebibliography}{29}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

\bibitem[{{Klypin} {et~al.}(2011)}]{2011ApJ...740..102K}
{Klypin}, A.~A. and {Trujillo-Gomez}, S. and {Primack}, J.} 2011, \apj, 102

\bibitem[{{Verdugo} {et~al.}(2014)}]{verdugo}
{{Vedugo}, T., {Motta}, V., {Foex}, G., {Forero-Romero}, J. E., {Mu\~noz}, R. P., {Pello}, R., 
{Limousin}, M., {Gavazzi}, R., {More}, A., {Cabanac}, R., {Soucail}, G., {Blakeslee}, J. P., 
{Mej\'ia}, A., {Magris}, G. and {Fern\'andez-Trincado}, J. G.} 2014, \apj, in preparation

\bibitem[{{Gastaldello} {et~al.}(2014)}]{gastaldello}
{{Gastaldello}}, F., et al. 2014, \mnras, in preparation

\bibitem[{{Mu\~noz} {et~al.}(2013)}]{2013A&A...552A..80M}
{{Mu{\~n}oz}, R.~P. and {Motta}, V. and {Verdugo}, T. and {Garrido}, F. and 
{Limousin}, M. and {Padilla}, N. and {Fo{\"e}x}, G. and {Cabanac}, R. and 
{Gavazzi}, R. and {Barrientos}, L.~F. and {Richard}, J.} 2013, \aap, A80

%%%%%%%%%%%%%%%%%%%%%%

%\bibitem[{{Tormen}(1997)}]{1997MNRAS.290..411T}
%{Tormen}, G. 1997, \mnras, 290, 411

%\bibitem[{{Tormen} {et~al.}(2004){Tormen}, {Moscardini}, \&
%  {Yoshida}}]{2004MNRAS.350.1397T}
%{Tormen}, G., {Moscardini}, L., \& {Yoshida}, N. 2004, \mnras, 350, 1397

%\bibitem[{{Vitvitska} {et~al.}(2002){Vitvitska}, {Klypin}, {Kravtsov},
%  {Wechsler}, {Primack}, \& {Bullock}}]{2002ApJ...581..799V}
%{Vitvitska}, M., {Klypin}, A.~A., {Kravtsov}, A.~V., {Wechsler}, R.~H.,
%  {Primack}, J.~R., \& {Bullock}, J.~S. 2002, \apj, 581, 799

%\bibitem[{{Yepes} {et~al.}(2007){Yepes}, {Sevilla}, {Gottl{\"o}ber}, \&
%  {Silk}}]{2007ApJ...666L..61Y}
%{Yepes}, G., {Sevilla}, R., {Gottl{\"o}ber}, S., \& {Silk}, J. 2007, \apjl,
%  666, L61

\end{thebibliography}

\end{document}

### 2014-02-27 paper/ms.tex
new structure

--- 2014-02-25 bullet_groups.tex
@@
-\documentclass[12pt,preprint]{aastex}
-% To highlight comments 
-\usepackage{color}
-\definecolor{red}{rgb}{1,0.0,0.0}
-\newcommand{\red}{\color{red}}
+\documentclass{emulateapj}
+\submitted{{\it Submitted for publication in ApJL}}
+\usepackage{multirow,color,wrapfig,ulem}
+\usepackage {graphicx}
 
@@
 \usepackage{float}
-%\bibliographystyle{apj}
+\bibliographystyle{apj}
 \def\be{\begin{equation}}
@@
 
-\title{Bullet Groups in the Bolshoi Cosmological Simulation}
-\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$ and T. Vergudo$^3$}
-\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
-       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne, Besan\c{c}on, France\\
-       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264, M\'erida 5101-A, Venezuela}
+\title{Bullet Groups as a test of $\Lambda$CDM}
+\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$
+  and T. Verdugo$^3$} 
+\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
+  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\ 
+       $^2$ Institute Utinam, CNRS UMR6213, Universit\'e de
+  Franche-Comt\'e, OSU THETA de Franche-Comt\'e-Bourgogne,
+  Besan\c{c}on, France\\ 
+       $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
+  M\'erida 5101-A, Venezuela}
 
 \begin{abstract}
-
-We estimate the expected distribution of displacements between the host halo of dark matter and the 
-substructure of dark matter most massive of the host, using a halo catalog from the Bolshoi simulation detected 
-with the Bound Density Maximun (BDM) algorithm. We found that the probability of finding a system similar to the Bullet
-Group with displacements of $\sim$400 kpch$^{-1}$ is between 40\% for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard 
-model predicts this scenario and is consistent with recently observations of the object SL2S J08544-0121 that is 
-a gravitational lens found in the SL2S and located at z$=0.35$.
-
+We estimate the expected distribution of displacements between the two
+dominand dark matter peaks in halos within a mass range corresponding
+to galaxy groups. We find that the probability of finding a system
+similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
+for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
+correspond to the observational constraint the object SL2S J08544-0121
+that is  a gravitational lens found in the SL2S and located at
+z$=0.35$. Given the larger abundance of groups with respect to
+clusters, finding multi-modal groups and baryonic-dark matter
+displacements.  
 \end{abstract}
@@
 
-This paper is organized as the follows: In Section
-\ref{simulation} we present the simulations.
+This paper is organized as the follows. In Section
+\ref{sec:simulation} we present the simulation and the halo catalogs
+used in this work. We continue in Section \ref{sec:setup} with the
+geometry of the problem at hand and the measurements setup. Next in
+Section \ref{sec:results} we present our results to finish with a
+discussion and conclusion in Sections \ref{sec:discussion} and
+\ref{sec:conclusions}.
 
-\section{Simulation}
-\label{simulation}
+\section{Simulation and halo catalogs}
+\label{sec:simulation}
 
-The analysis presented in this paper uses mainly the Bolshoi (250 Mpch$^{-1}$ simulation box, 1 kpch$^{-1}$ resolution) Database simulation described in
-\citet{2011ApJ...740..102K}. The simulation follows the evolution of 8.6 billion particle cosmological N-body simulation
-from z=80 to z=0 in a comoving cube of $250$ Mpch$^{-1}$
+The analysis presented in this paper uses mainly the Bolshoi (250
+Mpch$^{-1}$ simulation box, 1 kpch$^{-1}$ resolution) Database
+simulation described in \citet{2011ApJ...740..102K}. The simulation
+follows the evolution of 8.6 billion particle cosmological N-body
+simulation from z=80 to z=0 in a comoving cube of $250$ Mpch$^{-1}$
 on a side. The cosmology used  corresponds to  the spatially flat
-concordance model with the
-following parameters:  the density parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the density parameter for baryonic matter
- $\Omega_b=0.0469$, the density parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
-parameter $h=0.7$, the normalization of the Power spectrum $n=0.95$ and
-the amplitude of mass density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number of particles used for each of
-the DM component was $2048^3$, resulting in a mass resolution of $1.35 \times
-10^8$ M$_{\odot}$h$^{-1}$.
+concordance model with the following parameters:  the density
+parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the
+density parameter for baryonic matter  $\Omega_b=0.0469$, the density
+parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
+parameter $h=0.7$, the 
+normalization of the Power spectrum $n=0.95$ and the amplitude of mass
+density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number
+of particles used for each of the DM component was $2048^3$, resulting
+in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$.
 
-\section{Cumulative Probability Distributions}
-\label{cumulative distribution}
+\section{Bullet Geometry and Measurement Setup}
+\label{sec:setup}
 
-We selected four snapshot of the simulation for four different redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the 
-distribution of redshift in the Figure 1 by \citet{verdugo}, and 
-for each sample in redshift we selected the host halo with circular velocities greater than 300 kms$^{-1}$ and was split in two 
-principal groups: The first group correspond to host halo with circular velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$
-with mass in the range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range of mass of the
-Bullet Groups, and second group correspond to host halo with circular velocities greater than 
-700 kms$^{-1}$ with mass $\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet Clusters, in 
-the Table \ref{table1} is shown the two groups selected in this work. For each group, we 
-classified the corresponding substructures most massive and associated with the corresponding 
-host halo. The configuration of this system is shown in 
-Figure \ref{configuration}, where you can distinguish the host halo and substructure for a particular configuration in z$=0$. In 
-this work, we estimate the expected distribution of displacements ($d_{real,(X,Y)}$) in the projection 2-D that can estimate by 
-observations, these displacements correspond to the separation between the minimal potential of the host halo and the 
-minimal potential of the substructure, both are dark matter distributions.\\
+\section{Results}
+\label{sec:results}
+
+\subsection{Cumulative Probability Distributions}
+\label{cumulative_distribution}
+
+We selected four snapshot of the simulation for four different
+redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the
+distribution of redshift in the Figure 1 by \citet{verdugo}, and  for
+each sample in redshift we selected the host halo with circular
+velocities greater than 300 kms$^{-1}$ and was split in two  principal
+groups: The first group correspond to host halo with circular
+velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$ with mass in the
+range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range
+of mass of the Bullet Groups, and second group correspond to host halo
+with circular velocities greater than 700 kms$^{-1}$ with mass
+$\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet
+Clusters, in  the Table \ref{table1} is shown the two groups selected
+in this work. For each group, we  classified the corresponding
+substructures most massive and associated with the corresponding host
+halo. The configuration of this system is shown in  Figure
+\ref{configuration}, where you  an distinguish the host halo and
+substructure for a particular configuration in z$=0$. In  this work,
+we estimate the expected distribution of displacements
+($d_{real,(X,Y)}$) in the projection 2-D that can estimate by
+observations, these displacements correspond to the separation between
+the minimal potential of the host halo and the  minimal potential of
+the substructure, both are dark matter distributions.
 
@@
 \begin{center}
-\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
+%\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_7_2.eps}
-\includegraphics[width=1.0\textwidth]{figure_7_3.eps}
+%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
+%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
 \end{center}
-\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$ vs $d_{2d,(X,Y)}$ for different redshifts. The 
-horizontal dashed line correpond to $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the red star simbol correspond
-to $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S SJ08544-0121 in \citet{2013A&A...552A..80M}. The 
-four top panels are the sample with circular velocities $>700$ kms$^{-1}$ and the four down panels are the sample with 
-circular velocities between 300 km s$^{-1}$ to 700 kms$^{-1}$.}
+\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$
+  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
+  line correpond to
+  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the
+  red star simbol correspond to
+  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S
+  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
+  are the sample with circular velocities $>700$ kms$^{-1}$ and the
+  four down panels are the sample with  circular velocities between
+  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
 \label{newparameter}
@@
 \begin{center}
-\includegraphics[width=1.1\textwidth]{figure_7_1.eps}
+\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
 \end{center}
-\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements for the projection (X,Y). {\bf Left panel:} Sample with $\nu_{max}>700$ kms$^{-1}$ 
-for different redshifts. The vertical dashed line, correspond to the separation between dark matter to dark matter estimate
-in this work as the double of separation between the collisional gas and dark matter of 124$\pm$20 kpc reported
-by \citet{gastaldello} for the group SL2S J08544-0121. 
-{\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $ kms$^{-1}$ for different redshifts.} 
+\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
+  for the projection (X,Y). {\bf Left panel:} Sample with
+  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
+  dashed line, correspond to the separation between dark matter to
+  dark matter estimate in this work as the double of separation
+  between the collisional gas and dark matter of 124$\pm$20 kpc
+  reported by \citet{gastaldello} for the group SL2S J08544-0121.
+  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
+  kms$^{-1}$ for different redshifts.}  
 \label{displacements}
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_8_1_nu=0.5_300kms_700kms.eps}
+%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_8_3_nu=0.5_300kms_700kms.eps}
+%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
 \end{center}
@@
 
-\section{Summary}
-\label{summary}
+\section{Discussion}
+\label{sec:discussion}
 
 \section{Conclusions}
-\label{conclusions}
+\label{sec:conclusions}
 
@@
 
-The CosmoSim database used in this paper is a service by the Leibniz-Institute for Astrophysics Potsdam (AIP). The 
-BolshoiP simulation was performed within the Bolshoi project of the University of California High-Performance 
-AstroComputing Center (UC-HIPACC) and was run at the NASA Ames Research Center.
+The CosmoSim database used in this paper is a service by the
+Leibniz-Institute for Astrophysics Potsdam (AIP). The  BolshoiP
+simulation was performed within the Bolshoi project of the University
+of California High-Performance  AstroComputing Center (UC-HIPACC) and
+was run at the NASA Ames Research Center.
 
-\begin{thebibliography}{29}
-\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
-
-\bibitem[{{Klypin} {et~al.}(2011)}]{2011ApJ...740..102K}
-{Klypin}, A.~A. and {Trujillo-Gomez}, S. and {Primack}, J.} 2011, \apj, 102
-
-\bibitem[{{Verdugo} {et~al.}(2014)}]{verdugo}
-{{Vedugo}, T., {Motta}, V., {Foex}, G., {Forero-Romero}, J. E., {Mu\~noz}, R. P., {Pello}, R., 
-{Limousin}, M., {Gavazzi}, R., {More}, A., {Cabanac}, R., {Soucail}, G., {Blakeslee}, J. P., 
-{Mej\'ia}, A., {Magris}, G. and {Fern\'andez-Trincado}, J. G.} 2014, \apj, in preparation
-
-\bibitem[{{Gastaldello} {et~al.}(2014)}]{gastaldello}
-{{Gastaldello}}, F., et al. 2014, \mnras, in preparation
-
-\bibitem[{{Mu\~noz} {et~al.}(2013)}]{2013A&A...552A..80M}
-{{Mu{\~n}oz}, R.~P. and {Motta}, V. and {Verdugo}, T. and {Garrido}, F. and 
-{Limousin}, M. and {Padilla}, N. and {Fo{\"e}x}, G. and {Cabanac}, R. and 
-{Gavazzi}, R. and {Barrientos}, L.~F. and {Richard}, J.} 2013, \aap, A80
-
-%%%%%%%%%%%%%%%%%%%%%%
-
-%\bibitem[{{Tormen}(1997)}]{1997MNRAS.290..411T}
-%{Tormen}, G. 1997, \mnras, 290, 411
-
-%\bibitem[{{Tormen} {et~al.}(2004){Tormen}, {Moscardini}, \&
-%  {Yoshida}}]{2004MNRAS.350.1397T}
-%{Tormen}, G., {Moscardini}, L., \& {Yoshida}, N. 2004, \mnras, 350, 1397
-
-%\bibitem[{{Vitvitska} {et~al.}(2002){Vitvitska}, {Klypin}, {Kravtsov},
-%  {Wechsler}, {Primack}, \& {Bullock}}]{2002ApJ...581..799V}
-%{Vitvitska}, M., {Klypin}, A.~A., {Kravtsov}, A.~V., {Wechsler}, R.~H.,
-%  {Primack}, J.~R., \& {Bullock}, J.~S. 2002, \apj, 581, 799
-
-%\bibitem[{{Yepes} {et~al.}(2007){Yepes}, {Sevilla}, {Gottl{\"o}ber}, \&
-%  {Silk}}]{2007ApJ...666L..61Y}
-%{Yepes}, G., {Sevilla}, R., {Gottl{\"o}ber}, S., \& {Silk}, J. 2007, \apjl,
-%  666, L61
-
-\end{thebibliography}
+\bibliographystyle{apj}
+\bibliography{references}
 

### 2014-02-27 paper/ms.tex
intro

@@
 \newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
 \newcommand{\bullb}{MACS J0025.4-1222}
@@
 \section{Introduction}
+
+The Bullet Cluster provided a new kind of observational evidence of
+the existece of dark matter. Quantifying the displacement between dark
+matter and the dominant baryonic component (hot X-ray emitting gas)
+has been used to test the CDM paradigm itself by quantifying the
+substructure velocity requiered to produce such displacement and also
+by estimating the expected abundance of such events in the Universe.
+
+Since that time there are other observations of other Bullet-like
+systems [...].
+
+Recently \citep{Gastaldello} observed baryonic-DM displacement if
+$124\pm 20$ kpc in a group-like system with a total mass $2.4\pm 0.6
+\times 10^{14}$\Msun. Systems of this mass are $\sim 10$ times more massive
+than cluster systems in the mass range $>10^{15}$\hMsun, this opens
+up the possibility of observationally finding bullet groups in a fair
+amount to impose constraints on $\Lambda$CDM. This greater abundance
+has to be weighted by the fraction of systems that present large
+displacements. Such study has been performed for clusters but not for
+lower mass systems.
+
+In this Letter we present prediction for the abundance of group-like
+systems that might show a DM-baryon displacement. To this end we use a
+N-body cosmological simulation with such a resolution that allows us
+to identify multimodal dark matter clumps in the circular velocity
+range $300-1000$\kms.
 
@@
 \begin{center}
-\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
+%\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
 \end{center}
@@
   between the collisional gas and dark matter of 124$\pm$20 kpc
-  reported by \citet{gastaldello} for the group SL2S J08544-0121.
+  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
   {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
@@
 
-In order of estimate the number of Bullet Groups expected in the Bolshoi Cosmological Simulation, we 
-define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
+In order to estimate the number of Bullet Groups expected in the
+Bolshoi Cosmological Simulation, we define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
 we make the scalar product between the velocity vector and position vector that defines the separation between 

### 2014-02-27 paper/ms.tex
empezando a estructurar el texto

@@
 
-The analysis presented in this paper uses mainly the Bolshoi (250
-Mpch$^{-1}$ simulation box, 1 kpch$^{-1}$ resolution) Database
-simulation described in \citet{2011ApJ...740..102K}. The simulation
-follows the evolution of 8.6 billion particle cosmological N-body
-simulation from z=80 to z=0 in a comoving cube of $250$ Mpch$^{-1}$
-on a side. The cosmology used  corresponds to  the spatially flat
+We use the Bolshoi Run, a cosmological DM only simulation over a cubic
+volume of 250 comoving \hMpc on a side. The simulation uses the ART code to
+follow the evolution of  a dark matter density field sampled with
+$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds to  the spatially flat
 concordance model with the following parameters:  the density
@@
 in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$.
+
+\citet{2011ApJ...740..102K}.
 

### 2014-02-28 paper/ms.tex
Update ms.tex

@@
 We estimate the expected distribution of displacements between the two
-dominand dark matter peaks in halos within a mass range corresponding
+dominant dark matter peaks in halos within a mass range corresponding
 to galaxy groups. We find that the probability of finding a system

### 2014-03-01 src/Analysis_5_all_z.py
source code

@@ -80,10 +80,10 @@ af1_m2.plot(d_real2_z2,Y_2_z2,color='red',ls='--',label='z=0.5')
 af1_m2.plot(d_real2_z1,Y_2_z1,color='green',ls='--',label='z=1')
 
 af1_m1.set_xlabel(r'$d_{real}$ (kpch$^{-1}$)',fontsize='x-large')
-af1_m1.set_ylabel(r'P(>$d$)',fontsize='x-large')
+af1_m1.set_ylabel(r'P(>$d_{real}$)',fontsize='x-large')
 af1_m1.legend(loc=1,numpoints=1,fontsize='medium')
 af1_m2.set_xlabel(r'$d_{real}$ (kpch$^{-1}$)',fontsize='x-large')
-af1_m2.set_ylabel(r'P(>$d$)',fontsize='x-large')
+af1_m2.set_ylabel(r'P(>$d_{real}$)',fontsize='x-large')
 af1_m2.legend(loc=1,numpoints=1,fontsize='medium')
 
 #Figure 2

### 2014-03-01 src/Analysis_6_all_z.py

@@ -7,17 +7,23 @@ import pylab as plt
 
 z_=[0,1,0.25,0.5]
 
-for i in np.arange(4):
 
-	halo_=sc.genfromtxt('Host_700kms_z'+str(int(i))+'.dat')
-	sub_=sc.genfromtxt('Host_700kms_z'+str(int(i))+'.dat_substructure.dat')
-	label_=r'V$_{max}$ > 700 km s$^{-1}$ & z='+str(z_[i]) 
-	siz1, siz2=2E-2, 4E-2
+for k in np.arange(len(z_)):
 
-#	halo_=sc.genfromtxt('Host_300kms_700kms_z'+str(int(i))+'.dat')
-#	sub_=sc.genfromtxt('Host_300kms_700kms_z'+str(int(i))+'.dat_substructure.dat')
-#	label_=r'300 km s$^{-1}$ < $\nu_{max}$ < 700 km s$^{-1}$ & z='+str(z_[i])
+#	halo_=sc.genfromtxt('Host_300kms_700kms_z'+str(int(k))+'.dat')
+#	sub_=sc.genfromtxt('Host_300kms_700kms_z'+str(int(k))+'.dat_substructure.dat')
+#	label_=r'300 km s$^{-1}$ < $\nu_{max}$ < 700 km s$^{-1}$ & z='+str(z_[k])
 #	siz1, siz2=2E-4, 4E-4
+#	etq='figure_6_300kms_700kms_'
+
+
+	halo_=sc.genfromtxt('Host_700kms_z'+str(int(k))+'.dat')
+	sub_=sc.genfromtxt('Host_700kms_z'+str(int(k))+'.dat_substructure.dat')
+	label_=r'$\nu_{max}$ > 700 km s$^{-1}$ & z='+str(z_[k])
+	siz1, siz2=2E-4, 4E-4
+	etq='figure_6_700kms_'
+
+
 		
 	#Variables
 	
@@ -67,13 +73,14 @@ for i in np.arange(4):
 	YZ=np.sort(dist_2d_YZ_[mask_v])
 	XZ=np.sort(dist_2d_XZ_[mask_v])
 	XYZ=np.sort(dist_3d_[mask_v])
+
 	
-	f=plt.figure(1)
-	f2=plt.figure(2)
-	f3=plt.figure(3)
-	f4=plt.figure(4)
-	f5=plt.figure(5)
-	
+	f=plt.figure(1+(k*5),(20,18))
[…]

### 2014-03-01 src/Analysis_7_all_z.py

@@ -77,8 +77,8 @@ a1.plot(XY_h_z3,Y_h_z3,color='blue',label='z=0.25')
 a1.plot(XY_h_z2,Y_h_z2,color='red',label='z=0.5')
 a1.plot(XY_h_z1,Y_h_z1,color='green',label='z=1')
 a1.set_yscale('log')
-a1.set_ylabel(r'P(>$d_{2d,(X,Y)}$)',fontsize='x-large')
-a1.set_xlabel(r'$d_{2d,(X,Y)}$ (kpch$^{-1}$)',fontsize='x-large')
+a1.set_ylabel(r'P(>$d_{real,(X,Y)}$)',fontsize='x-large')
+a1.set_xlabel(r'$d_{real,(X,Y)}$ (h$^{-1}$kpc)',fontsize='x-large')
 a1.legend(loc=1,numpoints=1,fontsize='medium')
 #a1.text(55,4E-2,r'V$_{max}$ < 700 km s$^{-1}$',fontsize='x-large')
 #a1.text(55,2E-2,r'$(V_{circ,sub}/V_{circ,Halo}) > 0.5$',fontsize='x-large')
@@ -91,8 +91,8 @@ a2.plot(XY_s_z3,Y_s_z3,ls='--',color='blue',label='z=0.25')
 a2.plot(XY_s_z2,Y_s_z2,ls='--',color='red',label='z=0.5')
 a2.plot(XY_s_z1,Y_s_z1,ls='--',color='green',label='z=1')
 a2.set_yscale('log')
-a2.set_ylabel(r'P(>$d_{2d,(X,Y)}$)',fontsize='x-large')
-a2.set_xlabel(r'$d_{2d,(X,Y)}$ (kpch$^{-1}$)',fontsize='x-large')
+a2.set_ylabel(r'P(>$d_{real,(X,Y)}$)',fontsize='x-large')
+a2.set_xlabel(r'$d_{real,(X,Y)}$ (h$^{-1}$kpc)',fontsize='x-large')
 a2.legend(loc=1,numpoints=1,fontsize='medium')
 #a2.text(55,2E-4,r'$(V_{circ,sub}/V_{circ,Halo}) > 0.5$',fontsize='x-large')
 #a2.text(55,4E-4,r'300 km s$^{-1}$ < V$_{max}$ < 700 km s$^{-1}$',fontsize='x-large')
@@ -111,22 +111,22 @@ col2='red'
 
[…]

### 2014-03-01 src/Analysis_8_velocities_all_z.py

@@ -15,7 +15,7 @@ def fun_(var1,var2):
 	Xoff_new_, V_circ_,dist_3d_,dist_2d_XY_, dist_2d_YZ_, dist_2d_XZ_=np.array([]), np.array([]), np.array([]),np.array([]), np.array([]), np.array([])#, Xoff_old_, V_circ_, dist_3d_, dist_2d_XY_, dist_2d_YZ_, dist_2d_XZ_, Rvirial_host_=np.array([]), np.array([]), np.array([]), np.array([]), np.array([]), np.array([]), np.array([]), np.array([])
 	angulo_=np.array([])	
 	#h=1
-	Parameter=0.5
+	Parameter=0.
 	
 	for i in np.arange(len(halo_[:,0])):
 	
@@ -173,7 +173,7 @@ af22.set_xlabel(r'$d_{real, (X,Y)}$ (kpch$^{-1}$)',fontsize='x-large')
 af22.tick_params(labelsize='x-large')
 af22.legend(loc=1,numpoints=1,fontsize='medium')
 af22.set_yscale('log')
-#af22.axvline(x=(124./0.6777)*2.,color='gray',linestyle='-')
+af22.axvline(x=(124./0.6777)*2.,color='gray',linestyle='-')
 
 
 #af23.plot(np.sort(dist_2d_YZ_s_z0[mask_ang0]),Y_z0,lw=3,ls='--',color='black',label='z=0')

### 2014-03-01 src/Plot.py

@@ -1,0 +1,39 @@
+#!/usr/bin/python
+
+
+
+
+import numpy as np
+import scipy as sc
+import pylab as plt
+
+
+data=sc.genfromtxt('Host.dat')
+
+r_host=((data[0,8]/0.7)/1000.)
+x_host=data[0,0]/0.7
+y_host=data[0,1]/0.7
+
+r_sub=((data[1,8]/0.7)/1000.)
+x_sub=data[1,0]/0.7
+y_sub=data[1,1]/0.7
+
+an = np.linspace(0,2*np.pi,100)
+plt.plot(r_sub*np.cos(an)+(x_sub),r_sub*np.sin(an)+(y_sub),color='black',label=r'$\nu_{circ,Sub}=$'+str(data[1,10])+' kms$^{-1}$')
+plt.plot(r_host*np.cos(an)+(x_host),r_host*np.sin(an)+(y_host),ls='--',color='gray',label=r'$\nu_{circ,Halo}=$'+str(data[0,10])+' kms$^{-1}$')
+plt.plot((x_host,x_sub),(y_host,y_sub),lw=3,color='black')
+#plt.plot((0,x_sub),(0,y_sub),color='black')
+#plt.plot((0,x_host),(0,y_host),color='black')
+plt.title('Fernandez-Trincado et al. (2014)')
+plt.text(333.701,148.78,'Bullet Group',fontsize='xx-large')
+plt.text(333.701,146.27,r'X$_{off,new}=d_{real,(X,Y)}/R_{virial,Halo}$',fontsize='xx-large')
+plt.text(334.89,148.,'Halo',fontsize='xx-large')
+plt.text(335.729,146.626,'Sub',fontsize='xx-large')
+plt.text(335.264,147.394,r'$d_{real,(X,Y)}$',fontsize='xx-large')
+plt.xlabel('X (Mpc)')
+plt.ylabel('Y (Mpc)')
+plt.ylim(146,149)
+plt.xlim(333.5,336.5)
+
+plt.legend(loc=1,numpoints=1,fontsize='large')
+plt.show()

### 2014-03-01 src/table.py

@@ -1,0 +1,40 @@
+#!/usr/bin/python
+
+
+
+
+import numpy as np
+import scipy as sc
+import pylab as plt
+
+
+host_z0=sc.genfromtxt('Host_700kms_z0.dat')
+sub_z0=sc.genfromtxt('Host_700kms_z0.dat_substructure.dat')
+
+host_z3=sc.genfromtxt('Host_700kms_z3.dat')
+sub_z3=sc.genfromtxt('Host_700kms_z3.dat_substructure.dat')
+
+host_z2=sc.genfromtxt('Host_700kms_z2.dat')
+sub_z2=sc.genfromtxt('Host_700kms_z2.dat_substructure.dat')
+
+host_z1=sc.genfromtxt('Host_700kms_z1.dat')
+sub_z1=sc.genfromtxt('Host_700kms_z1.dat_substructure.dat')
+
+
+print "z=0 :", "Host Halo="+str(len(host_z0[:,0])), "Sub="+str(len(sub_z0[:,0]))
+print "z=0 :", "Host Halo="+str(np.max(host_z0[:,6])),str(np.min(host_z0[:,6])), "Sub="+str(np.max(sub_z0[:,6])), str(np.min(sub_z0[:,6]))
+
+print "z=0.25 :", "Host Halo="+str(len(host_z3[:,0])), "Sub="+str(len(sub_z3[:,0]))
+print "z=0.25 :", "Host Halo="+str(np.max(host_z3[:,6])),str(np.min(host_z3[:,6])), "Sub="+str(np.max(sub_z3[:,6])), str(np.min(sub_z3[:,6]))
+
+
+print "z=0.5 :", "Host Halo="+str(len(host_z2[:,0])), "Sub="+str(len(sub_z2[:,0]))
+print "z=0.5 :", "Host Halo="+str(np.max(host_z2[:,6])),str(np.min(host_z2[:,6])), "Sub="+str(np.max(sub_z2[:,6])), str(np.min(sub_z2[:,6]))
+
+
+print "z=1 :", "Host Halo="+str(len(host_z1[:,0])), "Sub="+str(len(sub_z1[:,0]))
+print "z=1 :", "Host Halo="+str(np.max(host_z1[:,6])),str(np.min(host_z1[:,6])), "Sub="+str(np.max(sub_z1[:,6])), str(np.min(sub_z1[:,6]))
+
+
+
+

### 2014-03-03 paper/ms.tex
article

@@
-\documentclass{emulateapj}
+%\documentclass{emulateapj}
+\documentclass{aastex}
 \submitted{{\it Submitted for publication in ApJL}}
@@
 \begin{abstract}
+
 We estimate the expected distribution of displacements between the two
@@
 \begin{center}
-%\includegraphics[width=0.90\textwidth]{Bullet_Group.eps}
+\includegraphics[width=0.90\textwidth]{Figures_eps/Bullet_Group.eps}
 \end{center}
@@
 \begin{center}
-%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
-%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
 \end{center}
@@
 \begin{center}
-%\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
+\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
 \end{center}
@@
 \begin{center}
-%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
 \end{center}
@@
 \begin{center}
-%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
 \end{center}

### 2014-03-03 paper/ms.tex
article

@@
 of particles used for each of the DM component was $2048^3$, resulting
-in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$.
-
-\citet{2011ApJ...740..102K}.
+in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$. \citet{2011ApJ...740..102K}.
 
@@
 \label{sec:setup}
+
+The configuration of this system is shown in  Figure
+\ref{configuration}, where can be distinguish the host halo and
+substructure for the a particular configuration in z$=0$ and the 
+mass ranges and number of host halos and substructures 
+are summary in the Table \ref{table1}. Of all the possible configurations that can be presented
+in Figure \ref{configuration}, we are interested in estimate in the simulation the number 
+of Bullet Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this we selected 
+of the simulations all the substructures  
+whose velocities indicate a movement out of the host halo. Each halo in this sample has a quantity
+called $X_{off}$ that corresponds to the distance halo center (the minimum of the gravitational potential) to 
+the center of mass normalized by the
+virial radius ($R_{vir}$). Values of $X_{off}$
+equal to zero indicate relaxed halos, while $X_{off}>0$ indicates the existence
+of perturbed halos which can be considered candidates to be Bullet Groups and this ditribution is shown 
+in a scatter plot in the Figure \ref{cos_theta1} and the distribution of $\nu_{circ,Halo}/\nu_{circ,Sub}$ 
+is shown in  Figure \ref{cos_theta2}, both figures for differents z.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{ccccccc}\hline\hline
+Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
+             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
+Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
+Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
+\end{tabular} 
+\caption{Mass ranges for the two groups selected in this work in different redshifts.}
+\label{table1}
+\end{center}
+\end{table}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.90\textwidth]{Figures_eps/Bullet_Group.eps}
+\end{center}
+\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
+\label{configuration}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_4.eps}
+\end{center}
+\caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
+for different z. The top panel is represented to the sample with $\nu>700$ kms$^{-}1$ and down panel is represented 
+for $\nu<700$ kms$^{-1}$} 
+\label{cos_theta1}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
+\end{center}
+\caption{Distributions of $\nu_{circ,Halo}/\nu_{circ,Sub}$ for differents z. The left panel correpond to the sample 
+with $\v>700$ kms$^{-1}$ and right panel correpond to the sample with $\nu<700$ kms$^{-1}$.} 
+\label{cos_theta2}
+\end{figure*}
 
@@
 substructures most massive and associated with the corresponding host
-halo. The configuration of this system is shown in  Figure
-\ref{configuration}, where you  an distinguish the host halo and
-substructure for a particular configuration in z$=0$. In  this work,
+halo.  In  this work,
 we estimate the expected distribution of displacements
-($d_{real,(X,Y)}$) in the projection 2-D that can estimate by
+($d_{real,(X,Y)}$) in the projection 2-D that can estimated by
 observations, these displacements correspond to the separation between
@@
 the substructure, both are dark matter distributions.
-
-\begin{table*}
-\begin{center}
-\begin{tabular}{ccccccc}\hline\hline
-Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
-             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
-Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
-Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
-\end{tabular} 
-\caption{Mass ranges for the two groups selected in this work in different redshifts.}
-\label{table1}
-\end{center}
-\end{table*}
 
@@
 displacements and this is shown in the Figure \ref{displacements} for the two groups classified in this work.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.90\textwidth]{Figures_eps/Bullet_Group.eps}
-\end{center}
-\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
-\label{configuration}
-\end{figure*}
 

### 2014-03-03 paper/ms.tex
rewriting

@@
-%\documentclass{emulateapj}
-\documentclass{aastex}
+\documentclass{emulateapj}
+%\documentclass{aastex}
 \submitted{{\it Submitted for publication in ApJL}}
@@
 follow the evolution of  a dark matter density field sampled with
-$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds to  the spatially flat
-concordance model with the following parameters:  the density
-parameter for matter (dark matter$+$baryons) $\Omega_m=0.27$, the
-density parameter for baryonic matter  $\Omega_b=0.0469$, the density
-parameter for dark energy $\Omega_{\Lambda}=0.73$, the Hubble
-parameter $h=0.7$, the 
+$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds
+to  the spatially flat concordance model with the following
+parameters:  the density parameter for matter (dark matter$+$baryons)
+$\Omega_m=0.27$, the density parameter for baryonic matter
+$\Omega_b=0.0469$, the density parameter for dark energy
+$\Omega_{\Lambda}=0.73$, the Hubble parameter $h=0.7$, the
 normalization of the Power spectrum $n=0.95$ and the amplitude of mass
@@
 of particles used for each of the DM component was $2048^3$, resulting
-in a mass resolution of $1.35 \times 10^8$ M$_{\odot}$h$^{-1}$. \citet{2011ApJ...740..102K}.
+in a mass resolution of $1.35 \times 10^8$
+M$_{\odot}$h$^{-1}$. \citet{2011ApJ...740..102K}.
 
@@
 
-The configuration of this system is shown in  Figure
-\ref{configuration}, where can be distinguish the host halo and
-substructure for the a particular configuration in z$=0$ and the 
+The configuration of the BGs in the simulations is shown in Figure
+\ref{configuration}. There we depict a host and its most massive
+sub-halo from in a particular case found at z$=0$. The arrows show the
+position and the velocity vectors sub-halo in a frame of reference
+where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
+$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
+vectors characterized by,
+\begin{equation}
+  \mu\equiv \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|v{}\right\| \left\|r\right\|}
+ \end{equation} 
+%
+encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
+can be considered as head-on collisions while $|\mu|\approx 0$
+describe a grazing trajectory.
+
+The bullet-like encounter can be instantaneously described by
+quantities the following quantities the circular velocity of the host
+and the sub-halo, $V_{\rm c,host}$ and $V_{\rm c,  sub}$; the size of
+the host halo $R_{\rm vir}$; the relative position and velocity of the
+substructre, $\vec{v}$ and $\vec{r}$; and the angle between the
+position and velocity $\mu$.
+
+Using these quantities one can describe three main stages in a
+Bullet-like collision. First, the sub-halo crosses the virial radius
+of the host halo in a head-on fashion, $|\vec{r}|/R_{\rm vir}\approx
+1$ and $\mu\approx<0.0$. Second, as the sub-halo crosses for the first
+time the center of the host halo $|\vec{r}|/R_{\rm vir} <
+1.0$ and $\mu>0.0$. Third, as the sub-halo reaches apogee and
+comes back to the center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
+$\mu<0.0$.
+
+the 
 mass ranges and number of host halos and substructures 
@@
 
-\begin{table}
+\begin{table*}
 \begin{center}
 \begin{tabular}{ccccccc}\hline\hline
-Sample       & Minimum Mass           & Maximum Mass          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
-             & M$_{\odot}$h$^{-1}$    & M$_{\odot}$h$^{-1}$   &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
-Host Halo    & 0.35$\times{}10^{14}$  & 1.09$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\
-Substructure & 0.38$\times{}10^{11}$  & 0.30$\times{}10^{14}$ &    400    &   362     &   310    &  192   \\\hline
+Sample       & Minimum $V_{\rm c}$         & Maximum $V_{\rm c}$          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
+             & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
+Host   & 300\kms & XX &    400    &   362     &   310    &  192   \\ 
+Sub-structure & 75\kms  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
 \end{tabular} 
-\caption{Mass ranges for the two groups selected in this work in different redshifts.}
+\caption{Circular velocity ranges for the halos and subhalos at
+  different redshifts.}  
 \label{table1}
 \end{center}
-\end{table}
+\end{table*}
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-\includegraphics[width=0.90\textwidth]{Figures_eps/Bullet_Group.eps}
+\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
 \end{center}
-\caption{Configuration for a host halo (dashed circle) and sub-structure (black circle) in the sample. } 
+\caption{Configuration for a host halo (dashed circle) and
+  sub-structure (black circle) in the sample.}  
 \label{configuration}
-\end{figure*}
+\end{figure}
 
@@
 \caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
-for different z. The top panel is represented to the sample with $\nu>700$ kms$^{-}1$ and down panel is represented 
-for $\nu<700$ kms$^{-1}$} 
+for different z. The top panel is represented to the sample with $v > 700$ \kms and down panel is represented 
+for $v<700$ \kms} 
 \label{cos_theta1}
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
+%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
 \end{center}
-\caption{Distributions of $\nu_{circ,Halo}/\nu_{circ,Sub}$ for differents z. The left panel correpond to the sample 
-with $\v>700$ kms$^{-1}$ and right panel correpond to the sample with $\nu<700$ kms$^{-1}$.} 
+\caption{Integrated distributions of $|\vec{v}|/V_{\rm c,host}$ at all
+  $z$. The left panel correponds to the sample with $V_{\rm c, host}>700$ \kms and
+  right panel correpond to the sample with $V_{\rm c,host}<700\kms$.} 
 \label{cos_theta2}
@@
 \begin{equation}
- \frac{\nu_{circ,sub}}{\nu_{circ,halo}}=0.5
+ \frac{v_{circ,sub}}{v_{circ,halo}}=0.5
 \end{equation}
 
-Figure \ref{newparameter} shows the scatter plot of the parameter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$ vs the 
+Figure \ref{newparameter} shows the scatter plot of the parameter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$ vs the 
 displacement ($d_{2d,(X,Y)}$) between the host halo and the substructure and for different redshifts. This parameter is 
@@
 the fraction in velocity dispersion in the line-of-sigth of the group SL2S SJ08544-0121 ($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and $\sigma_{substructure}=185^{+30}_{-62}$), reported by \citet{2013A&A...552A..80M}.
-Based in the parameter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)>0.5$, we estimate the expected distribution of
+Based in the parameter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)>0.5$, we estimate the expected distribution of
 displacements and this is shown in the Figure \ref{displacements} for the two groups classified in this work.
@@
 \end{center}
-\caption{Scatter $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)$
+\caption{Scatter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$
   vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
   line correpond to
-  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.5$ and the
+  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.5$ and the
   red star simbol correspond to
-  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)=0.54$ for SL2S
+  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.54$ for SL2S
   SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
@@
   for the projection (X,Y). {\bf Left panel:} Sample with
-  $\nu_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
+  $v_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
   dashed line, correspond to the separation between dark matter to
@@
   reported by \citet{Gastaldello} for the group SL2S J08544-0121.
-  {\bf Right panel:} Sample with $300 $ kms$^{-1} <\nu_{max}<700 $
+  {\bf Right panel:} Sample with $300 $ kms$^{-1} <v_{max}<700 $
   kms$^{-1}$ for different redshifts.}  
@@
 
- \begin{equation}
-  cos(\theta)=\frac{\vec{\nu{}}\cdotp{}\vec{r}}{\left\|\nu{}\right\| \left\|r\right\|}
- \end{equation}
-
-where, $\vec{\nu{}}=\vec{\nu}_{sub}-\vec{\nu}_{halo}$ and $\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, in the Figure \ref{cos_theta}
-is shown the scatter plot of $cos(\theta{})$ vs $X_{off,new}=\frac{d_{2d,(X,Y)}}{R_{virial,halo}}=\frac{d_{real,(X,Y)}}{R_{virial,halo}}$.
-
 \begin{figure*}
@@
 \caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
-where the substructure is emerging from the host halo and  $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
+where the substructure is emerging from the host halo and  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
 cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
@@
 \end{center}
-\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{\nu_{circ,sub}}{\nu_{circ,halo}}\right)\geq0.5$, 
+\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
 cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 

### 2014-03-04 paper/ms.tex
geometry and measurement setup

@@
 \begin{equation}
-  \mu\equiv \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|v{}\right\| \left\|r\right\|}
+  \mu\equiv
+  \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
+    \left\|\vec{r}\right\|} 
  \end{equation} 
@@
 
-Using these quantities one can describe three main stages in a
-Bullet-like collision. First, the sub-halo crosses the virial radius
-of the host halo in a head-on fashion, $|\vec{r}|/R_{\rm vir}\approx
-1$ and $\mu\approx<0.0$. Second, as the sub-halo crosses for the first
-time the center of the host halo $|\vec{r}|/R_{\rm vir} <
-1.0$ and $\mu>0.0$. Third, as the sub-halo reaches apogee and
-comes back to the center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
-$\mu<0.0$.
+As a first approximation there are two quantities that are available
+from observations of these Bullet-like systems. The projected distance
+between two dominand dark matter clumps and the ratio of the
+galaxies' luminosities associated to them. From the simulation point
+of view this can be translated into the 2D projected values of
+$||\vec{r}||$, its value relative to the virial radius $\chi =
+||\vec{r}||_{2D}/R_{\rm vir}$ and the ratio of the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. Then, in order to gain better insight we use
+the sub-structure velocity as a fraction of the host's circular
+velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
+of the interaction.  Finally, an even more detailed picture of the
+collision can be obtained through the values of $\mu$.
 
-the 
+All the physical quantities described above can be used to describe
+the tree main stages in a bullet-like encounter. First, the sub-halo
+crosses the virial radius of the host halo starting a head on
+collission, $|\vec{r}|/R_{\rm vir}\approx 1$ and
+$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
+the center of the host halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
+$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
+center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
+this quantities in Section XXX to fully characterize the different
+kind of interactions observed in the Bolshoi simulation.
+
+The ranges of circular velocities for the host and sub-halos and the
+corresponding number of halos at every redshift are listed in Table
+\ref{table1}.
+
 mass ranges and number of host halos and substructures 
-are summary in the Table \ref{table1}. Of all the possible configurations that can be presented
-in Figure \ref{configuration}, we are interested in estimate in the simulation the number 
-of Bullet Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this we selected 
-of the simulations all the substructures  
-whose velocities indicate a movement out of the host halo. Each halo in this sample has a quantity
-called $X_{off}$ that corresponds to the distance halo center (the minimum of the gravitational potential) to 
-the center of mass normalized by the
-virial radius ($R_{vir}$). Values of $X_{off}$
-equal to zero indicate relaxed halos, while $X_{off}>0$ indicates the existence
-of perturbed halos which can be considered candidates to be Bullet Groups and this ditribution is shown 
-in a scatter plot in the Figure \ref{cos_theta1} and the distribution of $\nu_{circ,Halo}/\nu_{circ,Sub}$ 
-is shown in  Figure \ref{cos_theta2}, both figures for differents z.
+are summary in the Table \ref{table1}. Of all the possible
+configurations that can be presented in Figure \ref{configuration}, we
+are interested in estimate in the simulation the number  of Bullet
+Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this
+we selected  of the simulations all the substructures   
+whose velocities indicate a movement out of the host halo. Each halo
+in this sample has a quantity called $X_{off}$ that corresponds to the
+distance halo center (the minimum of the gravitational potential) to
+the center of mass normalized by the virial radius ($R_{vir}$). Values
+of $X_{off}$ equal to zero indicate relaxed halos, while $X_{off}>0$
+indicates the existence of perturbed halos which can be considered
+candidates to be Bullet Groups and this ditribution is shown  in a
+scatter plot in the Figure \ref{cos_theta1} and the distribution of
+$\nu_{circ,Halo}/\nu_{circ,Sub}$ is shown in  Figure \ref{cos_theta2},
+both figures for differents z.
 

### 2014-03-04 paper/ms.tex
re-estructurando las secciones y subsecciones

@@
 to galaxy groups. We find that the probability of finding a system
-similar with displacements of $\sim$400 kpch$^{-1}$ is between 40\%
+similar with displacements of $\sim$400 \hkpc is between 40\%
 for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
@@
 
+The ranges of circular velocities for the host and sub-halos and the
+corresponding number of halos at every redshift are listed in Table
+\ref{table1}.
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{ccccccc}\hline\hline
+Sample  & Minimum $V_{\rm c}$ & Maximum $V_{\rm c}$  & \# Halos & \#
+Halos  & \# Halos & \# Halos \\ 
+ & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
+Host   & 300 & XX &    400    &   362     &   310    &  192   \\ 
+Sub-structure & 75  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
+\end{tabular} 
+\caption{Circular velocity ranges for the halos and subhalos at
+  different redshifts.}  
+\label{table1}
+\end{center}
+\end{table*}
+
 \section{Bullet Geometry and Measurement Setup}
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
+\end{center}
+\caption{Configuration for a host halo (dashed circle) and
+  sub-structure (black circle) in the sample.}  
+\label{fig:configuration}
+\end{figure}
+
 The configuration of the BGs in the simulations is shown in Figure
-\ref{configuration}. There we depict a host and its most massive
+\ref{fig:configuration}. There we depict a host and its most massive
 sub-halo from in a particular case found at z$=0$. The arrows show the
@@
 of view this can be translated into the 2D projected values of
-$||\vec{r}||$, its value relative to the virial radius $\chi =
-||\vec{r}||_{2D}/R_{\rm vir}$ and the ratio of the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. Then, in order to gain better insight we use
+$||\vec{r}||$, its value relative to the virial radius $X_{\rm 2D}=
+||\vec{r}||_{\rm 2D}/R_{\rm vir}$ and the ratio of the circular velocities
+of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. In a higher degree
+of detail, in order to gaint better insight we use
 the sub-structure velocity as a fraction of the host's circular
 velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
-of the interaction.  Finally, an even more detailed picture of the
-collision can be obtained through the values of $\mu$.
+of the interaction.  Finally, we also measure the geometry of each
+interaction through the values for $\mu$.
 
@@
 crosses the virial radius of the host halo starting a head on
-collission, $|\vec{r}|/R_{\rm vir}\approx 1$ and
+collission, $||\vec{r}||/R_{\rm vir}\approx 1$ and
 $\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
-the center of the host halo $|\vec{r}|/R_{\rm vir} < 1.0$ and
+the center of the host halo $||\vec{r}||/R_{\rm vir} < 1.0$ and
 $\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
-center of the halo $|\vec{r}|/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
+center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
 this quantities in Section XXX to fully characterize the different
@@
 
-The ranges of circular velocities for the host and sub-halos and the
-corresponding number of halos at every redshift are listed in Table
-\ref{table1}.
+\section{Results}
+\label{sec:results}
 
-mass ranges and number of host halos and substructures 
-are summary in the Table \ref{table1}. Of all the possible
-configurations that can be presented in Figure \ref{configuration}, we
-are interested in estimate in the simulation the number  of Bullet
-Groups that may be present in an Universe of 250 $h^{-1}$Mpc. For this
-we selected  of the simulations all the substructures   
-whose velocities indicate a movement out of the host halo. Each halo
-in this sample has a quantity called $X_{off}$ that corresponds to the
-distance halo center (the minimum of the gravitational potential) to
-the center of mass normalized by the virial radius ($R_{vir}$). Values
-of $X_{off}$ equal to zero indicate relaxed halos, while $X_{off}>0$
-indicates the existence of perturbed halos which can be considered
-candidates to be Bullet Groups and this ditribution is shown  in a
-scatter plot in the Figure \ref{cos_theta1} and the distribution of
-$\nu_{circ,Halo}/\nu_{circ,Sub}$ is shown in  Figure \ref{cos_theta2},
-both figures for differents z.
+\subsection{Separations and Relative Circular Velocities}
+\label{fig:separations}
 
-\begin{table*}
-\begin{center}
-\begin{tabular}{ccccccc}\hline\hline
-Sample       & Minimum $V_{\rm c}$         & Maximum $V_{\rm c}$          & \# Halos  & \# Halos  & \# Halos & \# Halos \\
-             & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
-Host   & 300\kms & XX &    400    &   362     &   310    &  192   \\ 
-Sub-structure & 75\kms  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
-\end{tabular} 
-\caption{Circular velocity ranges for the halos and subhalos at
-  different redshifts.}  
-\label{table1}
-\end{center}
-\end{table*}
+\subsection{Relative Velocities}
+\label{fig:velocities}
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
-\end{center}
-\caption{Configuration for a host halo (dashed circle) and
-  sub-structure (black circle) in the sample.}  
-\label{configuration}
-\end{figure}
+\subsection{Collision Geometries}
+\label{fig:geometry}
+
+\section{Discussion}
+\label{sec:discussion}
+Strictly speaking our results apply to multimodal groups and the e
+expected separation betwen dark matter clumps. [...]
+
+Expected displacement between dark and baryonic components are better
+described by systems where the collision already occurred.[...]
+(comparison with the old bullet clusters paper?)
+
+The expectations to quantify this effects observationally are
+high. [...]
+
+\section{Conclusions}
+\label{sec:conclusions}
 
@@
 \end{figure*}
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Cumulative Probability Distributions}
-\label{cumulative_distribution}
 

### 2014-03-04 paper/ms.tex
first subsection

@@
 \newcommand{\bulla}{1E0657---56} 
+\newcommand{\bullg}{SL2S J08544-0121}
 \shorttitle{Bullet Groups}
@@
 
-\subsection{Separations and Relative Circular Velocities}
-\label{fig:separations}
+\subsection{Displacements and Relative Circular Velocities}
+\label{fig:displacement}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{Figures_eps/figure_7_1.eps}
+\end{center}
+\caption{Integrated probability distribution for the displacement
+  between the host halo and its dominand sub-halo. The left panel
+  shows the results in terms of the physical displacements and the
+  right panel the same displacement normalized by the virial radius of
+  the host halo. The continous line corrresponds to the halos in the
+  group sample $V_{\rm c,host}>700\kms$ and the dashed lines to the 
+  The vertical stripe corresponds to the estimate of the separation
+  between the two dark matter clumps in the results reported by
+  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
+  shows the same results normalized by the virial radius of the host
+  halo.} 
+\label{fig:displacement}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
+\end{center}
+\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
+    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
+  right panel to clusters. The circle with error bars corresponds to
+  \bullg data reported from \citet{2013A&A...552A..80M} and
+  \citet{Gastaldello}. The data used to construct the histograms
+  integrates the objects at all redshifts. }
+\label{fig:mass_displacement}
+\end{figure*}
+
+The main result of this paper is summarized in Figure
+\ref{fig:displacement}, it presents the integrated
+probability distribution for the displacement between the center of
+the host halo and its dominant sub-halo. The left pannel shows
+the displacement in physical units and the right pannel as a fraction
+of the virial radius of the host halo.
+
+Figure \ref{fig:displacement} shows the results for two different
+populations; groups with $300\kms < V_{\rm c, host}<700\kms$ and
+clusters with $V_{\rm c,host}>700\kms$. Additionally, this is
+presented for all redshifts $z=0.0, 0.25, 0.5$ and $1.0$.
+
+The panel with the physical displacements also shows a vertical stripe
+with the estimated displacement for the Bullet-group reported by
+\cite{Gastaldello}. Considering this system as consistent withe the
+groups sample we see that a fraction of $\sim XX\pm XX\%$ of the groups
+should present a displacement equal or larger than the one estimated
+for \bullg. The panel with the normalized displacements shows a
+distribution that can be considered close to universal in the sense
+that the two samples (groups and clusters) at all redshifts present a
+similar trend.[...]
+
+Figure \ref{fig:mass_displacement} shows 2D histograms in a plane
+composed by the ratio of the two circular velocities $V_{\rm c,
+  sub}/V_{\rm c, host}$ and the physical displacements. In each of the
+halo samples (left, groups; right, clusters) the two-dimensional
+distributions are similar and have been therefore integrated to build
+the 2D histogram.
+
+On top of these 2D histograms there is an circle with error bars that
+represents the observational estimates for the system \bullg. [...]
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_3.eps}
-\end{center}
-\caption{Scatter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$
-  vs $d_{2d,(X,Y)}$ for different redshifts. The  horizontal dashed
-  line correpond to
-  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.5$ and the
-  red star simbol correspond to
-  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)=0.54$ for SL2S
-  SJ08544-0121 in \citet{2013A&A...552A..80M}. The  four top panels
-  are the sample with circular velocities $>700$ kms$^{-1}$ and the
-  four down panels are the sample with  circular velocities between
-  300 km s$^{-1}$ to 700 kms$^{-1}$.} 
-\label{newparameter}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.1\textwidth]{Figures_eps/figure_7_1.eps}
-\end{center}
-\caption{Cumulative distribution (P$>d_{2d,(X,Y)}$) of displacements
-  for the projection (X,Y). {\bf Left panel:} Sample with
-  $v_{max}>700$ kms$^{-1}$  for different redshifts. The vertical
-  dashed line, correspond to the separation between dark matter to
-  dark matter estimate in this work as the double of separation
-  between the collisional gas and dark matter of 124$\pm$20 kpc
-  reported by \citet{Gastaldello} for the group SL2S J08544-0121.
-  {\bf Right panel:} Sample with $300 $ kms$^{-1} <v_{max}<700 $
-  kms$^{-1}$ for different redshifts.}  
-\label{displacements}
-\end{figure*}
-
 \subsection{Number expected of Bullet Groups in the sample}

### 2014-03-04 paper/ms.tex
seeding paragraphs

@@
 \end{center}
-\caption{Integrated probability distribution for the displacement
+\caption{
+Integrated probability distribution for the displacement
   between the host halo and its dominand sub-halo. The left panel
@@
 \subsection{Relative Velocities}
+\label{sec:velocities}
+
+\begin{figure*}
+\begin{center}
+%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
+\end{center}
+\caption{Integrated probability distribution for the relative velocity of the
+sub-halo with respect to its host. The left panel shows the results
+in physical units while the right panel show the same values
+normalized by the circular velocity of the host halo. The line coding
+follows the same structure as Figure \ref{fig:displacements}}
 \label{fig:velocities}
+\end{figure*}
+
+In Figure \ref{fig:velocities} we present the integrated probability
+of the relative peculiar velocities of the sub-halos with respect to
+the host halo. The left panel presents this velocity in physical units
+while the left panel presents them as a fraction of the circular
+velocity of the host halo.
 
@@
 high. [...]
+
+In order to facilitate the reproducibility and reuse of our results we
+have made available all the data and the source code available in a public
+repository. [...]
 

### 2014-03-05 paper/ms.tex
new figures

@@
 \begin{center}
-\includegraphics[width=0.45\textwidth]{Figures_eps/Bullet_Group.eps}
+\includegraphics[width=0.45\textwidth]{New_figures/Bullet_Group.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{Figures_eps/figure_7_1.eps}
+\includegraphics[width=0.8\textwidth]{New_figures/figure_2.eps}
 \end{center}
@@
   the host halo. The continous line corrresponds to the halos in the
-  group sample $V_{\rm c,host}>700\kms$ and the dashed lines to the 
+  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
+  sample $V_{\rm circ,host}<700\kms$.
   The vertical stripe corresponds to the estimate of the separation

### 2014-03-06 paper/ms.tex
improving the first subsection

@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
+\includegraphics[width=0.8\textwidth]{Figures_eps/figure_4_VcircsubVcirchalo_300kms_700kms.eps}
 \end{center}
@@
 \cite{Gastaldello}. Considering this system as consistent withe the
-groups sample we see that a fraction of $\sim XX\pm XX\%$ of the groups
+groups sample we see that a fraction of $\sim 15\pm 2\%$ of the groups
 should present a displacement equal or larger than the one estimated
-for \bullg. The panel with the normalized displacements shows a
-distribution that can be considered close to universal in the sense
-that the two samples (groups and clusters) at all redshifts present a
-similar trend.[...]
+for \bullg, this fraction is close to $45\pm2\% $. The panel with the
+normalized displacements shows a  distribution that can be considered
+close to universal in the sense that the two samples (groups and
+clusters) at all redshifts present a similar trend.[...]
 
@@
 composed by the ratio of the two circular velocities $V_{\rm c,
-  sub}/V_{\rm c, host}$ and the physical displacements. In each of the
-halo samples (left, groups; right, clusters) the two-dimensional
-distributions are similar and have been therefore integrated to build
-the 2D histogram.
+  sub}/V_{\rm c, host}$ and the physical displacements. This is
+revealing because these two quantities can be constrained by
+observations. The displacement is a direct observable, while the ratio
+of the circular velocities can be estimated from lensing studies or
+approximated by the ratio of the total galaxy luminosity associated
+with the galaxy peaks.
 
-On top of these 2D histograms there is an circle with error bars that
-represents the observational estimates for the system \bullg. [...]
+To construct this figure we co-add all the halos in the sample (left,
+groups; right, clusters) at all redshifts. We stack the data because
+we do not observe any strong time evolution, aditionally this allows
+us to increase the signal in each bin. Overplotted there is an circle
+with error bars that represents the observational estimates for the
+system \bullg.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_7_2.eps}
+\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
 \end{center}
@@
 \label{fig:velocities}
-\end{figure*}
+\end{figure}
 
@@
 
+The panel with the normalized velocities shows that the distribution
+of sub-halo velocities is close to universal. Regardless
+of the mass of the host halo and the redshift the integrated
+distributions lie very close to each other.
+
+The median of this distribution is located at $v/V_{\rm
+  c,host}=1.1$. We also note the strong break at $v/V_{\rm
+  c,host}=3.0$ that is present in the data from the group sample that
+allows us to probe fractions on the order of $10^{-4}$.  This break is
+located close the escape velocity of $v/V_{\rm c,host}$ for dark
+matter halos following a NFW profile with a concentration value
+$c\approx 6$ \citep{Hayashi2006}.
+
 \subsection{Collision Geometries}
 \label{fig:geometry}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{Figures_eps/figure_4_300kms_700kms.eps}
+\end{center}
+\caption{x}
+\label{fig:velocities}
+\end{figure*}
 
@@
 \label{sec:conclusions}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_4.eps}
-\end{center}
-\caption{Scatter plot for $X_{off}$ as function of the relation between velocities of substructures and the host halos and 
-for different z. The top panel is represented to the sample with $v > 700$ \kms and down panel is represented 
-for $v<700$ \kms} 
-\label{cos_theta1}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-%\includegraphics[width=1.0\textwidth]{Figures_eps/figure_5_2.eps}
-\end{center}
-\caption{Integrated distributions of $|\vec{v}|/V_{\rm c,host}$ at all
-  $z$. The left panel correponds to the sample with $V_{\rm c, host}>700$ \kms and
-  right panel correpond to the sample with $V_{\rm c,host}<700\kms$.} 
-\label{cos_theta2}
-\end{figure*}
 
@@
 
-Figure \ref{newparameter} shows the scatter plot of the parameter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$ vs the 
-displacement ($d_{2d,(X,Y)}$) between the host halo and the substructure and for different redshifts. This parameter is 
-consistent with the observations. The red star simbol in the Figure \ref{newparameter} is equal to 0.54 corresponding to 
-the fraction in velocity dispersion in the line-of-sigth of the group SL2S SJ08544-0121 ($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and $\sigma_{substructure}=185^{+30}_{-62}$), reported by \citet{2013A&A...552A..80M}.
-Based in the parameter $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)>0.5$, we estimate the expected distribution of
-displacements and this is shown in the Figure \ref{displacements} for the two groups classified in this work.
-
-\subsection{Number expected of Bullet Groups in the sample}
-
-In order to estimate the number of Bullet Groups expected in the
-Bolshoi Cosmological Simulation, we define the configuration of this system as one where the substructure is coming out of the host halo ($cos(\theta)>0.5$). For this 
-we make the scalar product between the velocity vector and position vector that defines the separation between 
- the host halo and the substructure, as shown below: \\
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_1_nu=0.5_300kms_700kms.eps}
-\end{center}
-\caption{Scatter of $cos(\theta)$ vs $X_{off,new}$. The red dashed line correpond to the limit for $cos(\theta{})>0.5$,  
-where the substructure is emerging from the host halo and  $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
-cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
-\label{cos_theta}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_8_3_nu=0.5_300kms_700kms.eps}
-\end{center}
-\caption{Cumulative distribution of $d_{real, (X,Y)}$ for $cos(\theta)>0.5$, $\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)\geq0.5$, 
-cicular velocities $<700$ kms$^{-1}$ and different redshifts.} 
-\label{cumulative_cos}
-\end{figure*}
+Figure \ref{newparameter} shows the scatter plot of the parameter
+$\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$ vs the  displacement
+($d_{2d,(X,Y)}$) between the host halo and the substructure and for
+different redshifts. This parameter is  consistent with the
+observations. The red star simbol in the Figure \ref{newparameter} is
+equal to 0.54 corresponding to  the fraction in velocity dispersion in
+the line-of-sigth of the group SL2S SJ08544-0121
+($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and
+$\sigma_{substructure}=185^{+30}_{-62}$), reported by
+\citet{2013A&A...552A..80M}. Based in the parameter
+$\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)>0.5$, we estimate the
+expected distribution of displacements and this is shown in the Figure
+\ref{displacements} for the two groups classified in this work.
 

### 2014-03-06 paper/ms.tex
descoping to have a letter

@@
 
-\section{Simulation and halo catalogs}
+\section{Simulation, halo catalogs and pairs}
 \label{sec:simulation}
@@
 
-The ranges of circular velocities for the host and sub-halos and the
-corresponding number of halos at every redshift are listed in Table
-\ref{table1}.
+We use halo catalogs constructed using the BDM algorithm. [...]
 
-\begin{table*}
-\begin{center}
-\begin{tabular}{ccccccc}\hline\hline
-Sample  & Minimum $V_{\rm c}$ & Maximum $V_{\rm c}$  & \# Halos & \#
-Halos  & \# Halos & \# Halos \\ 
- & \kms    & \kms  &   $z=0$   & $z=0.25$  & $z=0.5$  & $z=1$  \\\hline
-Host   & 300 & XX &    400    &   362     &   310    &  192   \\ 
-Sub-structure & 75  & XX &    XX   &   XX     &   XX    &  XX   \\\hline
-\end{tabular} 
-\caption{Circular velocity ranges for the halos and subhalos at
-  different redshifts.}  
-\label{table1}
-\end{center}
-\end{table*}
+In the snapshots at redshift $z=0.0,0.25, 0.5$ and $1.0$ there are
+$XX, XX, XX, XX$ host halos with circular velocities $V_{\rm c}>
+300$\kms and $XX, XX, XX, XX$ sub-halos with circular velocities
+$V_{\rm c}>75$\kms. These two sets of halos constitute the basis for
+our analysis.
+
+For each host halo in the sample we find its most massive
+sub-halo. Each pair host/sub-halo is considererd as a potential Bullet
+Group and is kept for the measurement and analysis described in the
+next section.
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.45\textwidth]{New_figures/Bullet_Group.eps}
-\end{center}
-\caption{Configuration for a host halo (dashed circle) and
-  sub-structure (black circle) in the sample.}  
-\label{fig:configuration}
-\end{figure}
+The Bullet groups is composed by two halos. the host halo and the sub
+halo. This configuration is described by the position and velocity of
+the sub-halo in a frame of reference where the main halo is at rest;
+thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and 
+$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, where the subscripts $host$
+and $sub$ refer to the host and sub-halo in the frame of reference of
+the simulation, respectively.
 
-The configuration of the BGs in the simulations is shown in Figure
-\ref{fig:configuration}. There we depict a host and its most massive
-sub-halo from in a particular case found at z$=0$. The arrows show the
-position and the velocity vectors sub-halo in a frame of reference
-where the main halo is at rest; thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
-$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$.  The angle between these two
-vectors characterized by, 
+The angle between these two vectors characterized by, 
 \begin{equation}
@@
 
+Figure \ref{fig:} presents the geometry of the bullet groups in our 
+ the relative geometry of the collision using the
+variables $\mu$ and $X_{\rm off}$.
+
 \begin{figure*}
@@
 \caption{x}
-\label{fig:velocities}
+\label{fig:geometry}
 \end{figure*}
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-\section{Conclusions}
-\label{sec:conclusions}
-
 \section*{Acknowledgements}

### 2014-03-06 paper/ms.tex
new results subsection

@@
 matter and the dominant baryonic component (hot X-ray emitting gas)
-has been used to test the CDM paradigm itself by quantifying the
-substructure velocity requiered to produce such displacement and also
-by estimating the expected abundance of such events in the Universe.
+\citep{ForeroRomero2011} has been used to test the CDM paradigm itself
+by quantifying the substructure velocity requiered to produce such
+displacement \citep{Hayashi2006} to finally estimate the expected
+abundance of such events in the Universe.
 
@@
 of view this can be translated into the 2D projected values of
-$||\vec{r}||$, its value relative to the virial radius $X_{\rm 2D}=
+$||\vec{r}||$, its value relative to the virial radius $D_{\rm off}=
 ||\vec{r}||_{\rm 2D}/R_{\rm vir}$ and the ratio of the circular velocities
@@
 with error bars that represents the observational estimates for the
-system \bullg.
+system \bullg using the fraction in velocity dispersion in
+the line-of-sigth of the group SL2S SJ08544-0121
+($\sigma_{host}=341^{+43}_{-109}$\kms and
+$\sigma_{sub}=185^{+30}_{-62}$\kms) reported by
+\citet{2013A&A...552A..80M} and the DM displacement inferred from the
+data presented by \cite{Gastaldello}.
 
@@
 normalized by the circular velocity of the host halo. The line coding
-follows the same structure as Figure \ref{fig:displacements}}
+follows the same structure as Figure \ref{fig:displacement}}
 \label{fig:velocities}
@@
 The panel with the normalized velocities shows that the distribution
-of sub-halo velocities is close to universal. Regardless
-of the mass of the host halo and the redshift the integrated
-distributions lie very close to each other.
+of sub-halo velocities is close to universal. Regardless of the mass
+of the host halo and the redshift the integrated distributions lie
+very close to each other.
 
@@
 
-Figure \ref{fig:} presents the geometry of the bullet groups in our 
- the relative geometry of the collision using the
-variables $\mu$ and $X_{\rm off}$.
-
 \begin{figure*}
@@
 
-\section{Discussion}
-\label{sec:discussion}
-Strictly speaking our results apply to multimodal groups and the e
-expected separation betwen dark matter clumps. [...]
+Figure \ref{fig:} presents the geometry of the bullet groups using the 
+variables $\mu$ and $D_{\rm off}$. The first evident feature is that
+most of the configurations have $|mu|>0.9$ ($\theta\leq 30^{\circ}$),
+meaning that most of the collisions can be described as a head-on while
+only a minority with $|mu|<0.9$ have more tangential trajectories. For
+the pairs on radial trajectories there are three regions of interest
+in this plane that describe different stages in the collision,
+assuming that the sub-halo merges or falls below the detection
+threshold after the first pass through the center of the host halo.
 
-Expected displacement between dark and baryonic components are better
-described by systems where the collision already occurred.[...]
-(comparison with the old bullet clusters paper?)
+The first region has $\mu\approx-1$ and $D_{\rm off}>0.6$, which
+locates the systems where a head-on collision has just started. The
+sub-halo is close to the boundary of the host halo and is
+infalling. The second region has $\mu\approx 1$ and $D_{\rm off}<0.6$;
+at this stage the collision continues after the first crossing of the
+host's center, the low number of halos with radial infalling velocities
+and displacements $D_{\rm off}>0.6$ sugesst that this the maximum
+range of radii for the apogee.  The third region corresponds to
+$\mu\approx-1$ and $D_{\rm off}<0.6$ which corresponds to the
+secondary infall after apogee.
 
-The expectations to quantify this effects observationally are
-high. [...]
+\subsection{Displacement between Dark Matter and Baryons}
+\label{sec:baryonic_displacements}
+
+\begin{figure}
+\begin{center}
+%\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
+\end{center}
+\caption{Integrated probability distribution for the estimated
+  baryonic displacements in the group and cluster samples at all redshifts.}
+\label{fig:baryonic_displacements}
+\end{figure}
+
+These different collision geometries will produce different results in
+terms of the displacement between dark matter and baryons. Strictly
+speaking, the results we have derived so far, apply to multimodal groups and their
+expected separation betwen the two dominant dark matter clumps but it
+should not be interpreted that all have a corresponding DM-baryon
+displacement. The systems where the halo is starting to fall into the
+host ($\mu\approx-1$, $D_{\rm off}>0.6$) should not present a
+detectable DM-baryon displacement.
+
+We clearly expect such displacement in the case where the
+sub-structure has already passed through the center of the host
+halo. In this section we attempt an estimation for the DM-baryon
+displacement statistics. We work under the following
+hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
+baryonic displacement, $d_{2D}^{\prime}$, equal to zero. Second, we
+consider that all systems with infalling velocities $\mu<-0.9$ and
+large displacements $D_{\rm off}>0.6$ also have baryonic displacements
+equal to zero. Third, for all the other cases we estimate the
+displacement between the baryons and the dominand DM peak by the
+distances between the dominant peak and the center of mass of the main
+halo, $d_{2D}^{\prime}=D_{\rm off} R_{\rm vir}$, where $X_{\rm off}$
+is the offset computed for each host halo in the original catalog.
+
+This simplified modeldoes not take into account that there is a
+fraction of halos with $\mu<-0.9$ and $D_{\rm off}<0.6$ for which the
+collision has not started and should have $d_{2D}^{\prime}=0$. A detailed
+modeling of this fraction requires the study of the complete merger
+tree of the halo and sub-halo, a study beyond the scope of this
+Letter. Instead we cautio the reader that the derived fraction of
+halos with a displacement $<d_{2D}^{\prime}$ can be considered as an
+upper limit.
+
+The results for the integrated distributions for $>d_{2D}^{\prime}$
+are shown in Figure \ref{fig:baryonic_displacements}.[..]
 
@@
 
-In order to explore the distribution of displacements expected in the observational, we define a new parameter given by:\\
-
-\begin{equation}
- \frac{v_{circ,sub}}{v_{circ,halo}}=0.5
-\end{equation}
-
-Figure \ref{newparameter} shows the scatter plot of the parameter
-$\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)$ vs the  displacement
-($d_{2d,(X,Y)}$) between the host halo and the substructure and for
-different redshifts. This parameter is  consistent with the
-observations. The red star simbol in the Figure \ref{newparameter} is
-equal to 0.54 corresponding to  the fraction in velocity dispersion in
-the line-of-sigth of the group SL2S SJ08544-0121
-($\sigma_{host,halo}=341^{+43}_{-109}$ kms$^{-1}$ and
-$\sigma_{substructure}=185^{+30}_{-62}$), reported by
-\citet{2013A&A...552A..80M}. Based in the parameter
-$\left(\frac{v_{circ,sub}}{v_{circ,halo}}\right)>0.5$, we estimate the
-expected distribution of displacements and this is shown in the Figure
-\ref{displacements} for the two groups classified in this work.
-
 \section*{Acknowledgements}

### 2014-03-06 paper/ms.tex
conclusions

@@
 
-\title{Bullet Groups as a test of $\Lambda$CDM}
+\title{The abundance of Bullet Groups in $\Lambda$CDM}
 \author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$
@@
 matter and the dominant baryonic component (hot X-ray emitting gas)
-\citep{ForeroRomero2011} has been used to test the CDM paradigm itself
+\citep{ForeroRomero2010} has been used to test the CDM paradigm itself
 by quantifying the substructure velocity requiered to produce such
@@
 
-We use halo catalogs constructed using the BDM algorithm. [...]
+We use halo catalogs constructed using the BDM algorithm. [...] \citep{Riebe2013}.
 
@@
 hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
-baryonic displacement, $d_{2D}^{\prime}$, equal to zero. Second, we
+baryonic displacement, $d_{2D}^{\rm bar}$, equal to zero. Second, we
 consider that all systems with infalling velocities $\mu<-0.9$ and
@@
 distances between the dominant peak and the center of mass of the main
-halo, $d_{2D}^{\prime}=D_{\rm off} R_{\rm vir}$, where $X_{\rm off}$
+halo, $d_{2D}^{\rm bar}=D_{\rm off} R_{\rm vir}$, where $X_{\rm off}$
 is the offset computed for each host halo in the original catalog.
@@
 fraction of halos with $\mu<-0.9$ and $D_{\rm off}<0.6$ for which the
-collision has not started and should have $d_{2D}^{\prime}=0$. A detailed
+collision has not started and should have $d_{2D}^{\rm bar}=0$. A detailed
 modeling of this fraction requires the study of the complete merger
@@
 Letter. Instead we cautio the reader that the derived fraction of
-halos with a displacement $<d_{2D}^{\prime}$ can be considered as an
+halos with a displacement $<d_{2D}^{\rm bar}$ can be considered as an
 upper limit.
 
-The results for the integrated distributions for $>d_{2D}^{\prime}$
+The results for the integrated distributions for $>d_{2D}^{\rm bar}$
 are shown in Figure \ref{fig:baryonic_displacements}.[..]
@@
 
-We selected four snapshot of the simulation for four different
-redshifts (z$=0$, z$=0.25$, z$=0.5$ and z$=1$) based in the
-distribution of redshift in the Figure 1 by \citet{verdugo}, and  for
-each sample in redshift we selected the host halo with circular
-velocities greater than 300 kms$^{-1}$ and was split in two  principal
-groups: The first group correspond to host halo with circular
-velocities between 300 kms$^{-1}$ to 700 kms${^{-1}}$ with mass in the
-range of $10^{12}$ M$_\odot{}$ to $10^{14}$ M$_\odot{}$ in the range
-of mass of the Bullet Groups, and second group correspond to host halo
-with circular velocities greater than 700 kms$^{-1}$ with mass
-$\geq10^{14}$ M$_\odot{}$, in the range of mass of the Bullet
-Clusters, in  the Table \ref{table1} is shown the two groups selected
-in this work. For each group, we  classified the corresponding
-substructures most massive and associated with the corresponding host
-halo.  In  this work,
-we estimate the expected distribution of displacements
-($d_{real,(X,Y)}$) in the projection 2-D that can estimated by
-observations, these displacements correspond to the separation between
-the minimal potential of the host halo and the  minimal potential of
-the substructure, both are dark matter distributions.
+In this Letter we estimate fraction of galaxy groups
+that can present observational features associated to a
+bullet-like event. This is motivated by the recent observational
+results of \citep{Gastaldello} where a system (\bullg) on the mass range
+$1\times 10^{14}$\hMsun and velocity dispersion $650$\kms was reported
+to feature a displacement between its baryonic (hot gas) and dark
+matter components.
 
-\section*{Acknowledgements}
+Our estimate is based on large N-body DM-only cosmological
+simulation. We estimate the distribution of projected displacements
+between the dominant DM clumps in two kinds of systems; groups with circular
+velocities $300\kms<V_{\rm c}<700\kms$ and clusters with $V_{\rm
+  c}>700$\kms. We report these results at four different redshifts
+$z=0.0,0.25,0.5$ and $10$.
+
+We find that a fraction of $XX\pm XX\%$ of the halos in the group
+sample can present a displacement equal or larger than the observed displacement
+for \bullg. We also present these results in terms of the ratio of the
+circular velocities of the sub-halo to the host halo to find that the
+system \bullg is found within the expected parameter space spanned by
+the simulation.
+
+Next we describe the geometry of the collision by the angle between
+the position and velocity vectors of the sub-halo with respect to the
+host. This allows us to separate three different instances: the
+sub-halo crosses the virial radio of the host, the sub-halo goes
+through the center of the host and the secondary
+infall after reaching apogee.
+
+From this analysis we estimate a the integrated distribution of the
+displacements between the DM and the baryonic component. In this case
+we find that a fraction of $XX \pm XX\%$ halos in the group sample
+should present displacements equal or larger than those observed for
+the Bullet-Group \bullg.
+
+The results we present here can be used as a potential test of
+$\Lambda CDM$. (Comments about Gaels results on multimodal groups).
 

### 2014-03-08 paper/ms.tex
Update ms.tex

@@
 to identify multimodal dark matter clumps in the circular velocity
-range $300-1000$\kms.
+range $300-700$\kms.
 
@@
 Section \ref{sec:results} we present our results to finish with a
-discussion and conclusion in Sections \ref{sec:discussion} and
-\ref{sec:conclusions}.
+discussion and conclussion in Sections \ref{sec:discussion} and
+\ref{sec:conclussions}.
 
@@
 For each host halo in the sample we find its most massive
-sub-halo. Each pair host/sub-halo is considererd as a potential Bullet
+sub-halo. Each pair host/sub-halo is considered as a potential Bullet
 Group and is kept for the measurement and analysis described in the
@@
 from observations of these Bullet-like systems. The projected distance
-between two dominand dark matter clumps and the ratio of the
-galaxies' luminosities associated to them. From the simulation point
+between two dominant dark matter clumps and the ratio of the
+galaxies luminosities associated to them. From the simulation point
 of view this can be translated into the 2D projected values of
@@
 All the physical quantities described above can be used to describe
-the tree main stages in a bullet-like encounter. First, the sub-halo
+the three main stages in a bullet-like encounter. First, the sub-halo
 crosses the virial radius of the host halo starting a head on
@@
   right panel the same displacement normalized by the virial radius of
-  the host halo. The continous line corrresponds to the halos in the
+  the host halo. The continuous line corrresponds to the halos in the
   group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the

### 2014-03-08 paper/ms.tex
Update ms.tex

@@
 host's center, the low number of halos with radial infalling velocities
-and displacements $D_{\rm off}>0.6$ sugesst that this the maximum
+and displacements $D_{\rm off}>0.6$ suggest that this the maximum
 range of radii for the apogee.  The third region corresponds to
@@
 speaking, the results we have derived so far, apply to multimodal groups and their
-expected separation betwen the two dominant dark matter clumps but it
+expected separation between the two dominant dark matter clumps but it
 should not be interpreted that all have a corresponding DM-baryon
@@
 equal to zero. Third, for all the other cases we estimate the
-displacement between the baryons and the dominand DM peak by the
+displacement between the baryons and the dominant DM peak by the
 distances between the dominant peak and the center of mass of the main
@@
 
-This simplified modeldoes not take into account that there is a
+This simplified model does not take into account that there is a
 fraction of halos with $\mu<-0.9$ and $D_{\rm off}<0.6$ for which the
@@
 tree of the halo and sub-halo, a study beyond the scope of this
-Letter. Instead we cautio the reader that the derived fraction of
+Letter. Instead we caution the reader that the derived fraction of
 halos with a displacement $<d_{2D}^{\rm bar}$ can be considered as an

### 2014-03-08 paper/ms.tex
new abstract

@@
 \title{The abundance of Bullet Groups in $\Lambda$CDM}
-\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$
-  and T. Verdugo$^3$} 
+\author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
+  T. Verdugo$^3$, G. Foex$^4$ and V. Motta$^4$} 
 \affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
@@
        $^3$ Centro de Investigaciones de Astronom\'ia, AP 264,
-  M\'erida 5101-A, Venezuela}
+  M\'erida 5101-A, Venezuela\\
+  $^4$ Departamento de F\'isica y Astronom\'ia, Universidad de
+  Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
+  2360102, Chile  
+}
 
@@
 dominant dark matter peaks in halos within a mass range corresponding
-to galaxy groups. We find that the probability of finding a system
-similar with displacements of $\sim$400 \hkpc is between 40\%
-for z$=0$ and 60\% for z$=1$ and $\Lambda$CDM standard model, which
-correspond to the observational constraint the object SL2S J08544-0121
-that is  a gravitational lens found in the SL2S and located at
-z$=0.35$. Given the larger abundance of groups with respect to
-clusters, finding multi-modal groups and baryonic-dark matter
-displacements.  
+to galaxy groups. We find that 5\% to 25\% of the dark matter systems
+with circular velocities in the range $300\kms$ to $700\kms$ show
+multimodal morphologies with displacements between the dark matter
+clumps equal or larger to $\sim 400$\hkpc, which corresponds to the
+observational constraint the object SL2S J08544-0121 located at
+$z=0.35$. 
 \end{abstract}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{New_figures/figure_2.eps}
+\includegraphics[width=0.9\textwidth]{Figures_eps/figure_2.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{Figures_eps/figure_4_VcircsubVcirchalo_300kms_700kms.eps} 
+\includegraphics[width=0.9\textwidth]{Figures_eps/figure_5.eps} 
 \end{center}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
+\includegraphics[width=0.9\textwidth]{Figures_eps/figure_3.eps}
 \end{center}
@@
 \label{fig:velocities}
-\end{figure}
+\end{figure*}
 
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{Figures_eps/figure_4_300kms_700kms.eps}
+\includegraphics[width=0.9\textwidth]{Figures_eps/figure_4.eps}
 \end{center}
@@
 \begin{center}
-%\includegraphics[width=0.5\textwidth]{Figures_eps/figure_3.eps}
+\includegraphics[width=0.5\textwidth]{Figures_eps/figure_7.eps}
 \end{center}

### 2014-03-08 paper/ms.tex
updating separation values
abstract

@@
 dominant dark matter peaks in halos within a mass range corresponding
-to galaxy groups. We find that 5\% to 25\% of the dark matter systems
+to galaxy groups. We find that 50\% to 60\% of the dark matter systems
 with circular velocities in the range $300\kms$ to $700\kms$ show
 multimodal morphologies with displacements between the dark matter
-clumps equal or larger to $\sim 400$\hkpc, which corresponds to the
+clumps equal or larger than $133\pm21$\hkpc, which corresponds to the
 observational constraint the object SL2S J08544-0121 located at
-$z=0.35$. 
+$z=0.35$. Using the same data we estimate the DM-baryon separation and
+find that that $0.1\%$ to $1.0\%$ of the same systems should present
+separations equal or larger than $87\pm 14$\hkpc corresponding to the
+same observational benchmark.
+
+$133\pm21$\hkpc DM-DM separation
+$87 \pm 14$\hkpc DM-baryon separation.
+
 \end{abstract}

### 2014-03-09 src/Analysis_8_velocities_all_z_V2.py
Histogram2d

@@ -1,0 +1,309 @@
+#!/usr/bin/python
+
+
+import numpy as np
+import scipy as sc
+import pylab as plt
+from matplotlib.colors import LogNorm
+
+def fun_(var1,var2):
+
+	halo_=sc.genfromtxt(var1)
+	sub_=sc.genfromtxt(var2)
+
+	#Variables
+	
+	Xoff_new_, V_circ_,dist_3d_,dist_2d_XY_, dist_2d_YZ_, dist_2d_XZ_=np.array([]), np.array([]), np.array([]),np.array([]), np.array([]), np.array([])#, Xoff_old_, V_circ_, dist_3d_, dist_2d_XY_, dist_2d_YZ_, dist_2d_XZ_, Rvirial_host_=np.array([]), np.array([]), np.array([]), np.array([]), np.array([]), np.array([]), np.array([]), np.array([])
+	angulo_,dist_bar_,dist_barion,Doff_=np.array([]),np.array([]),np.array([]),np.array([])	
+	#h=1
+	Parameter=0.
+
+	for i in np.arange(len(halo_[:,0])):
+	
+		mask=sub_[:,14]==halo_[i,11]
+		N_=np.size(sub_[mask,14])
+	
+	#	print '['+str(i)+'/'+str(len(halo_[:,0]))+']'
+	
+		if N_==1.:
+	
+	#Parameters
+	
+			V_circ=float(sub_[mask,10][0])/float(halo_[i,10])
+			dist_3d=np.sqrt(((float(sub_[mask,0][0])-float(halo_[i,0]))**2)+((float(sub_[mask,1][0])-float(halo_[i,1]))**2)+((float(sub_[mask,2][0])-float(halo_[i,2]))**2))*1000.
+			dist_2d_XY=np.sqrt(((float(sub_[mask,0][0])-float(halo_[i,0]))**2)+((float(sub_[mask,1][0])-float(halo_[i,1]))**2))*1000.
+			dist_2d_YZ=np.sqrt(((float(sub_[mask,1][0])-float(halo_[i,1]))**2)+((float(sub_[mask,2][0])-float(halo_[i,2]))**2))*1000.
+			dist_2d_XZ=np.sqrt(((float(sub_[mask,0][0])-float(halo_[i,0]))**2)+((float(sub_[mask,2][0])-float(halo_[i,2]))**2))*1000.
[…]

### 2014-03-10 paper/ms.tex
abstract and results

--- 2014-03-08 paper/ms.tex
@@
 We estimate the expected distribution of displacements between the two
-dominant dark matter peaks in halos within a mass range corresponding
-to galaxy groups. We find that 5\% to 25\% of the dark matter systems
-with circular velocities in the range $300\kms$ to $700\kms$ show
-multimodal morphologies with displacements between the dark matter
-clumps equal or larger to $\sim 400$\hkpc, which corresponds to the
-observational constraint the object SL2S J08544-0121 located at
-$z=0.35$. 
+dominant dark matter peaks in two groups of halos corresponding to
+galaxy groups and clusters. We find that 50\% to 60\% of the dark
+matter  with circular velocities in the range $300\kms$ to $700\kms$
+(groups) show multimodal morphologies with displacements between the
+dark matter clumps equal or larger than $133\pm21$\hkpc, which
+corresponds to the observational constraint the object SL2S
+J08544-0121 located at $z=0.35$ which hass a velocity dispersion of
+$644^{+69}_{-102}\kms$. For dark matter halos with circular velocities
+larger than $700\kms$ (clusters) this fraction rises to $80\%$ to
+$85\%$. Using the same simulation we estimate the dark
+matter-to-baryon spatial separation and find that that $0.1\%$ to
+$1.0\%$ of the low mass systems should present separations equal or
+larger than $87\pm 14$\hkpc corresponding to the same observational
+benchmark; for halos with circular velocities larger than $700\kms$
+this fraction is in the range of $4\%$ to $10\%$, consistent with
+previous studies of dark mattter to baryon separations in
+clusters. These results present a weak dependence with redshift. 
 \end{abstract}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{Figures_eps/figure_2.eps}
+\includegraphics[width=0.9\textwidth]{figure_1.eps}
 \end{center}
@@
   Integrated probability distribution for the displacement
-  between the host halo and its dominand sub-halo. The left panel
-  shows the results in terms of the physical displacements and the
-  right panel the same displacement normalized by the virial radius of
+  between the host halo and its largest sub-halo. The left panel
+  shows the results in terms of the physical displacements while
+  the right panel shows the displacements normalized by the virial radius of
   the host halo. The continuous line corrresponds to the halos in the
@@
   sample $V_{\rm circ,host}<700\kms$.
-  The vertical stripe corresponds to the estimate of the separation
+  The vertical lines corresponds to mean estimate separation 
   between the two dark matter clumps in the results reported by
-  \citet{Gastaldello} for the group SL2S J08544-0121. The right panel
-  shows the same results normalized by the virial radius of the host
-  halo.} 
+  \citet{Gastaldello} for the group SL2S J08544-0121. Between $50\%$
+  to $60\%$ of the groups show a displacement equal or larger than
+  this observational benchmark.}
 \label{fig:displacement}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{Figures_eps/figure_5.eps} 
+\includegraphics[width=0.9\textwidth]{figure_2.eps} 
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{Figures_eps/figure_3.eps}
+\includegraphics[width=0.9\textwidth]{figure_3.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{Figures_eps/figure_4.eps}
+\includegraphics[width=0.9\textwidth]{figure_4.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{Figures_eps/figure_7.eps}
+\includegraphics[width=0.5\textwidth]{figure_5.eps}
 \end{center}
@@
 The results for the integrated distributions for $>d_{2D}^{\rm bar}$
-are shown in Figure \ref{fig:baryonic_displacements}.[..]
+are shown in Figure \ref{fig:baryonic_displacements}. The dashed lines
+represented the results for groups and the continous lines correspond
+to clusters. As a test of our approach we compare the cluster results
+against the analytic fit provided by \cite{ForeroRomero2010}. This fit
+reproduces the statistics for the DM-baryon separation found for
+clusters more massive than $>10^{14}$\hMsun in a simulation
+that included a description for gas with $8$ times the volume of the
+Bolshoi Simulation. This fit is valid for separations larger than
+$70$\hkpc, beyond that separation we find that it provides a good
+description within a factor of $\sim 2$ of
 
+\subsection{Reproducibility of our results}
 In order to facilitate the reproducibility and reuse of our results we
@@
 repository. [...]
+
+\section{Observational Implications}
+\label{sec:observations}
 

### 2014-03-10 paper/ms.tex
typos

@@
 corresponds to the observational constraint the object SL2S
-J08544-0121 located at $z=0.35$ which hass a velocity dispersion of
+J08544-0121 located at $z=0.35$ which has a velocity dispersion of
 $644^{+69}_{-102}\kms$. For dark matter halos with circular velocities
@@
 this fraction is in the range of $4\%$ to $10\%$, consistent with
-previous studies of dark mattter to baryon separations in
+previous studies of dark matter to baryon separations in
 clusters. These results present a weak dependence with redshift. 
@@
 The Bullet Cluster provided a new kind of observational evidence of
-the existece of dark matter. Quantifying the displacement between dark
+the existence of dark matter. Quantifying the displacement between dark
 matter and the dominant baryonic component (hot X-ray emitting gas)
 \citep{ForeroRomero2010} has been used to test the CDM paradigm itself
-by quantifying the substructure velocity requiered to produce such
+by quantifying the substructure velocity required to produce such
 displacement \citep{Hayashi2006} to finally estimate the expected
@@
 N-body cosmological simulation with such a resolution that allows us
-to identify multimodal dark matter clumps in the circular velocity
+to identify multi-modal dark matter clumps in the circular velocity
 range $300-700$\kms.
@@
 Section \ref{sec:results} we present our results to finish with a
-discussion and conclussion in Sections \ref{sec:discussion} and
+discussion and conclusion in Sections \ref{sec:discussion} and
 \ref{sec:conclussions}.
@@
 
-We use halo catalogs constructed using the BDM algorithm. [...] \citep{Riebe2013}.
+We use halo catalogs constructed using the BDM algorithm. [...] 
+All the raw data used in this Letter is available through the
+Multidark database \footnote{\texttt{www.multidark.org}}
+\citep{Riebe2013}.
 
 In the snapshots at redshift $z=0.0,0.25, 0.5$ and $1.0$ there are
-$XX, XX, XX, XX$ host halos with circular velocities $V_{\rm c}>
-300$\kms and $XX, XX, XX, XX$ sub-halos with circular velocities
-$V_{\rm c}>75$\kms. These two sets of halos constitute the basis for
-our analysis.
+$10041, 10346, 10554,$ and $10382$ host halos with circular velocities
+$V_{\rm c}\geq 300$\kms; and $157853, 177331, 195072, 225188$
+sub-halos with circular velocities $V_{\rm c}\geq 75$\kms,
+respectively. These two sets of halos constitute the basis for our
+analysis.
 
-For each host halo in the sample we find its most massive
-sub-halo. Each pair host/sub-halo is considered as a potential Bullet
-Group and is kept for the measurement and analysis described in the
-next section.
+For each host halo we find its most massive sub-halo. Each pair
+host/sub-halo is considered as a potential Bullet system and is kept
+got the analysis described in the next section.
 
@@
 the host halo $R_{\rm vir}$; the relative position and velocity of the
-substructre, $\vec{v}$ and $\vec{r}$; and the angle between the
+substructure, $\vec{v}$ and $\vec{r}$; and the angle between the
 position and velocity $\mu$.
@@
 of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. In a higher degree
-of detail, in order to gaint better insight we use
+of detail, in order to gain better insight we use
 the sub-structure velocity as a fraction of the host's circular
-velocity, $||\vec{r}||/V_{\rm c, host}$, as a mesure of the the strenght
+velocity, $||\vec{r}||/V_{\rm c, host}$, as a measure of the the strength
 of the interaction.  Finally, we also measure the geometry of each
@@
 crosses the virial radius of the host halo starting a head on
-collission, $||\vec{r}||/R_{\rm vir}\approx 1$ and
+collision, $||\vec{r}||/R_{\rm vir}\approx 1$ and
 $\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
@@
   the right panel shows the displacements normalized by the virial radius of
-  the host halo. The continuous line corrresponds to the halos in the
+  the host halo. The continuous line corresponds to the halos in the
   group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_2.eps} 
+\includegraphics[width=1.0\textwidth]{figure_2.eps} 
 \end{center}
 \caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
-    c,host}$-$d_{2D}$. The left panel corresponds to groups and the
-  right panel to clusters. The circle with error bars corresponds to
+    c,host}$-$d_{2D}$. The left panel corresponds to clusters and the
+  right panel to groups. The circle with error bars corresponds to
   \bullg data reported from \citet{2013A&A...552A..80M} and
@@
 probability distribution for the displacement between the center of
-the host halo and its dominant sub-halo. The left pannel shows
-the displacement in physical units and the right pannel as a fraction
+the host halo and its dominant sub-halo. The left panel shows
+the displacement in physical units and the right panel as a fraction
 of the virial radius of the host halo.
@@
 groups; right, clusters) at all redshifts. We stack the data because
-we do not observe any strong time evolution, aditionally this allows
+we do not observe any strong time evolution, additionally this allows
 us to increase the signal in each bin. Overplotted there is an circle
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_4.eps}
+\includegraphics[width=1.0\textwidth]{figure_4.eps}
 \end{center}
-\caption{x}
+\caption{2D histograms in the plane $\mu$-$D_{\rm off}$. The left
+  panel corresponds to clusters and the right panel to groups. The data
+  used to construct this histogram includes the halos at all redshifts.}
 \label{fig:geometry}
@@
 \caption{Integrated probability distribution for the estimated
-  baryonic displacements in the group and cluster samples at all redshifts.}
+  baryonic displacements in the group and cluster samples. The
+  continuous line marked as $P_{2D}$ shows the statistics reported by
+  \citet{ForeroRomero2010} for a cosmological simulation including DM
+  and baryons. The vertical lines correspond to the mean value and
+  uncertainty of the displacement measured for \bullg.}
 \label{fig:baryonic_displacements}
@@
 terms of the displacement between dark matter and baryons. Strictly
-speaking, the results we have derived so far, apply to multimodal groups and their
+speaking, the results we have derived so far, apply to multi-modal groups and their
 expected separation between the two dominant dark matter clumps but it
@@
 are shown in Figure \ref{fig:baryonic_displacements}. The dashed lines
-represented the results for groups and the continous lines correspond
+represented the results for groups and the continuous lines correspond
 to clusters. As a test of our approach we compare the cluster results
@@
 have made available all the data and the source code available in a public
-repository. [...]
+repository\footnote{\texttt{https://github.com/Fernandez-Trincado/Bullet\_Groups-2014}.}
 
@@
 
-Our estimate is based on large N-body DM-only cosmological
+Our estimate is based on large N-body dark matter only cosmological
 simulation. We estimate the distribution of projected displacements
-between the dominant DM clumps in two kinds of systems; groups with circular
-velocities $300\kms<V_{\rm c}<700\kms$ and clusters with $V_{\rm
+between the dominant DM clumps in two kinds of systems; groups with
+circular velocities $300\kms<V_{\rm c}<700\kms$ and clusters with $V_{\rm
   c}>700$\kms. We report these results at four different redshifts
@@
 
-We find that a fraction of $XX\pm XX\%$ of the halos in the group
-sample can present a displacement equal or larger than the observed displacement
-for \bullg. We also present these results in terms of the ratio of the
-circular velocities of the sub-halo to the host halo to find that the
-system \bullg is found within the expected parameter space spanned by
-the simulation.
+We find that a fraction of $50\%$-$60\%$ of the halos in the group
+sample present displacement equal or larger than the observed displacement
+for \bullg. For halos in the cluster sample this fraction increases to
+$80\%$-$85\%$.
 
-Next we describe the geometry of the collision by the angle between
+We also describe the collision geometry by the angle between
 the position and velocity vectors of the sub-halo with respect to the
 host. This allows us to separate three different instances: the
-sub-halo crosses the virial radio of the host, the sub-halo goes
-through the center of the host and the secondary
-infall after reaching apogee.
+sub-halo crossing the host virial radius, the sub-halo going
+through the host's center and the secondary infall after reaching
+apogee.
 
-From this analysis we estimate a the integrated distribution of the
-displacements between the DM and the baryonic component. In this case
-we find that a fraction of $XX \pm XX\%$ halos in the group sample
-should present displacements equal or larger than those observed for
-the Bullet-Group \bullg.
+From this analysis we derive an estimate for the displacement between
+the DM and the baryonic component. In the group sample
+$0.1\%$-$1.0\%$ of the halos show a displacement equal or larger than 
+the  measurements of \bullg by \citep{Gastaldello}. In the cluster
+sample this fraction rises to $4\%$-$10\%$.
 
 The results we present here can be used as a potential test of
-$\Lambda CDM$. (Comments about Gaels results on multimodal groups).
+$\Lambda$CDM. [...]
 

### 2014-03-11 paper/ms.tex
figure
new intro with references

@@
 \newcommand{\bulla}{1E0657---56} 
-\newcommand{\bullg}{SL2S J08544-0121}
+\newcommand{\bullg}{SL2S J08544-0121~}
 \shorttitle{Bullet Groups}
@@
 
-\title{The abundance of Bullet Groups in $\Lambda$CDM}
+\title{The abundance of Bullet-Groups in $\Lambda$CDM}
 \author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
@@
 We estimate the expected distribution of displacements between the two
-dominant dark matter peaks in two groups of halos corresponding to
-galaxy groups and clusters. We find that 50\% to 60\% of the dark
-matter  with circular velocities in the range $300\kms$ to $700\kms$
-(groups) show multimodal morphologies with displacements between the
-dark matter clumps equal or larger than $133\pm21$\hkpc, which
-corresponds to the observational constraint the object SL2S
-J08544-0121 located at $z=0.35$ which has a velocity dispersion of
-$644^{+69}_{-102}\kms$. For dark matter halos with circular velocities
-larger than $700\kms$ (clusters) this fraction rises to $80\%$ to
-$85\%$. Using the same simulation we estimate the dark
-matter-to-baryon spatial separation and find that that $0.1\%$ to
+dominant density peaks in dark matter halos simulated in a full
+cosmological context. We use as a benchmark the
+observation of \bullg, which is the lowest mass system observed so far
+featuring a bi-modal dark matter distribution with a dislocated 
+baryonic component. The study extends previous theoretical studies by
+simulating two samples: groups and clusters. We find that 50\% to 60\%
+of the dark matter halos with circular velocities in the range
+$300\kms$ to $700\kms$ (groups) show multimodal morphologies with
+displacements between the dark matter clumps equal or larger than
+$133\pm21$\hkpc observed in \bullg. For dark matter halos with
+circular velocities larger than $700\kms$ (clusters) this fraction
+rises to $80\%$ to $85\%$. Using the same simulation we estimate the
+dark matter-to-baryon spatial separation and find that $0.1\%$ to
 $1.0\%$ of the low mass systems should present separations equal or
-larger than $87\pm 14$\hkpc corresponding to the same observational
+larger than $87\pm 14$\hkpc corresponding to our observational
 benchmark; for halos with circular velocities larger than $700\kms$
 this fraction is in the range of $4\%$ to $10\%$, consistent with
-previous studies of dark matter to baryon separations in
-clusters. These results present a weak dependence with redshift. 
+previous studies of dark matter to baryon separations in clusters. The
+extension of the theoretical predictions and observational results
+towards low mass Bullet-like configurations, i.e. larger abundance of
+systems,  opens up the possibility for a new statistical test of
+$\Lambda$CDM.
+
 \end{abstract}
@@
 
-The Bullet Cluster provided a new kind of observational evidence of
-the existence of dark matter. Quantifying the displacement between dark
-matter and the dominant baryonic component (hot X-ray emitting gas)
-\citep{ForeroRomero2010} has been used to test the CDM paradigm itself
-by quantifying the substructure velocity required to produce such
-displacement \citep{Hayashi2006} to finally estimate the expected
-abundance of such events in the Universe.
+The Bullet Cluster (massive cluster of galaxies \bulla) provided a new
+kind of observational evidence for the existence of dark matter
+\citep{Markevitch2004,Clowe2006}. Quantifying the displacement between
+dark matter and the dominant baryonic component (hot X-ray emitting gas)
+has been used to test the Cold Dark Matter (CDM)
+paradigm itself by quantifying the substructure velocity required to
+produce such displacement \citep{Hayashi2006, Springel2007,
+  Thompson2012}, the displacemeent between the dominant dark matter
+and baryonic component \citep{ForeroRomero2010} to estimate the
+expected abundance of such events in a $\Lambda$CDM Universe and even
+explore possible extensions to the concordance cosmological model
+\citep{Farrar2007,Lee2010,Lee2012}.
 
-Since that time there are other observations of other Bullet-like
-systems [...].
+Since then, other examples of Bullet-like systems have been found; 
+MACS J0025.4-1222 \citep{Bradac2008}, Abell 2744 \citep{Merten2011},
+DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
+\citep{Dahle2013}. Recently \citep{Gastaldello} observed baryonic-DM
+displacement if $124\pm 20$ kpc in a group-like system with a total
+mass $2.4\pm 0.6 \times 10^{14}$\Msun. Systems of this mass are
+$\sim10$ times more abundant than cluster systems in the mass range of
+the Bullet Cluster $>10^{15}$\hMsun, this opens up the possibility of
+observationally finding bullet groups in a fair amount to impose
+constraints on $\Lambda$CDM.
 
-Recently \citep{Gastaldello} observed baryonic-DM displacement if
-$124\pm 20$ kpc in a group-like system with a total mass $2.4\pm 0.6
-\times 10^{14}$\Msun. Systems of this mass are $\sim 10$ times more massive
-than cluster systems in the mass range $>10^{15}$\hMsun, this opens
-up the possibility of observationally finding bullet groups in a fair
-amount to impose constraints on $\Lambda$CDM. This greater abundance
-has to be weighted by the fraction of systems that present large
-displacements. Such study has been performed for clusters but not for
-lower mass systems.
+However, a greater abundance of small mass systems has to be weighted
+by the probability of having a merger and 
+presenting a large displacement between the DM and baryonic
+components. These two conditions (merger rates, maximum possible
+displacement) are a funcion of halo mass in $\Lambda$CDM
+cosmologies.  Such study has been performed for clusters but not for
+lower mass systems \citep{ForeroRomero2010}. The existence of objects
+like \bullg and observational campaigns like the Strong Lensing Legacy
+Survey (SL2S) open up the possibility of finding multi-modal dark
+matter distributions in the group mass range.
 
-In this Letter we present prediction for the abundance of group-like
-systems that might show a DM-baryon displacement. To this end we use a
-N-body cosmological simulation with such a resolution that allows us
-to identify multi-modal dark matter clumps in the circular velocity
-range $300-700$\kms.
+In this Letter we compute the abundance of group-like dark
+matter halos with a multi-modal morphology that also might present a
+DM-baryon displacement. To this end we use a N-body cosmological
+simulation with such a resolution that allows us to identify
+multi-modal dark matter distributions in hosts with circular velocities
+larger than $300$\kms.
 
@@
 geometry of the problem at hand and the measurements setup. Next in
-Section \ref{sec:results} we present our results to finish with a
-discussion and conclusion in Sections \ref{sec:discussion} and
-\ref{sec:conclussions}.
+Section \ref{sec:results} we present our results and observational
+perspectives to finally conclude in Sections \ref{sec:conclusions}.
 
@@
 follow the evolution of  a dark matter density field sampled with
-$2024^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds
+$2048^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds
 to  the spatially flat concordance model with the following
@@
 
-Figure \ref{fig:} presents the geometry of the bullet groups using the 
+Figure \ref{fig:geometry} presents the geometry of the bullet groups using the 
 variables $\mu$ and $D_{\rm off}$. The first evident feature is that

### 2014-03-11 paper/ms.tex
finished description of the simulation

@@
 \newcommand{\bulla}{1E0657---56} 
-\newcommand{\bullg}{SL2S J08544-0121~}
+\newcommand{\bullg}{SL2S J08544-0121}
 \shorttitle{Bullet Groups}
@@
 We estimate the expected distribution of displacements between the two
-dominant density peaks in dark matter halos simulated in a full
-cosmological context. We use as a benchmark the
+dominant dark matter density peaks and between baryons and dark matter
+in halos simulated within a full cosmological context. We use as a benchmark the
 observation of \bullg, which is the lowest mass system observed so far
 featuring a bi-modal dark matter distribution with a dislocated 
-baryonic component. The study extends previous theoretical studies by
-simulating two samples: groups and clusters. We find that 50\% to 60\%
+baryonic component. We extend previous results by
+studying two halo samples: groups and clusters. We find that 50\% to 60\%
 of the dark matter halos with circular velocities in the range
@@
 displacements between the dark matter clumps equal or larger than
-$133\pm21$\hkpc observed in \bullg. For dark matter halos with
+$133\pm21$\hkpc as observed in \bullg. For dark matter halos with
 circular velocities larger than $700\kms$ (clusters) this fraction
@@
 dark matter-to-baryon spatial separation and find that $0.1\%$ to
-$1.0\%$ of the low mass systems should present separations equal or
+$1.0\%$ of the groups should present separations equal or
 larger than $87\pm 14$\hkpc corresponding to our observational
-benchmark; for halos with circular velocities larger than $700\kms$
-this fraction is in the range of $4\%$ to $10\%$, consistent with
-previous studies of dark matter to baryon separations in clusters. The
-extension of the theoretical predictions and observational results
-towards low mass Bullet-like configurations, i.e. larger abundance of
-systems,  opens up the possibility for a new statistical test of
-$\Lambda$CDM.
-
+benchmark; for clusters this fraction is in the range of $4\%$ to
+$10\%$, consistent with previous studies of dark matter to baryon
+separations. The extension of the theoretical predictions and
+observational results towards low mass Bullet-like configurations,
+i.e. larger abundance of systems,  opens up the possibility for a new
+statistical test of  $\Lambda$CDM.  
 \end{abstract}
@@
 
-This paper is organized as the follows. In Section
+This Letter is organized as the follows. In Section
 \ref{sec:simulation} we present the simulation and the halo catalogs
@@
 We use the Bolshoi Run, a cosmological DM only simulation over a cubic
-volume of 250 comoving \hMpc on a side. The simulation uses the ART code to
+volume of 250\hMpc comoving on a side. The simulation uses the ART code to
 follow the evolution of a dark matter density field sampled with
-$2048^3$ from $z=80$ to $z=0$ [...]. The cosmology used  corresponds
+$2048^3$ from $z=80$ to $z=0$. The cosmology used  corresponds
 to  the spatially flat concordance model with the following
-parameters:  the density parameter for matter (dark matter$+$baryons)
+parameters:  the density parameter for matter (dark matter and baryons)
 $\Omega_m=0.27$, the density parameter for baryonic matter
@@
 normalization of the Power spectrum $n=0.95$ and the amplitude of mass
-density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  The number
-of particles used for each of the DM component was $2048^3$, resulting
-in a mass resolution of $1.35 \times 10^8$
-M$_{\odot}$h$^{-1}$. \citet{2011ApJ...740..102K}.
+density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  These
+cosmological parameters are consistent with the nine-year Wilikinson
+Microwave Anisotropy Probe (WMAP) results \citep{hinshaw_etal13}. A
+detailed presentation of the simulation can be found in
+\citet{2011ApJ...740..102K}.
 
-We use halo catalogs constructed using the BDM algorithm. [...] 
-All the raw data used in this Letter is available through the
-Multidark database \footnote{\texttt{www.multidark.org}}
-\citep{Riebe2013}.
+The number of particles used for each of the DM component was
+$2048^3$, resulting in a mass resolution of $1.35 \times 10^8$
+M$_{\odot}$h$^{-1}$. The completeness limit in this simulation is set
+for halos with $100$ particles corresponding to a mass of
+$1.35\times10^{10}$\hMsun or a maximum circular velocity $V_{c}$ of
+$50$\kms.
 
-In the snapshots at redshift $z=0.0,0.25, 0.5$ and $1.0$ there are
-$10041, 10346, 10554,$ and $10382$ host halos with circular velocities
-$V_{\rm c}\geq 300$\kms; and $157853, 177331, 195072, 225188$
-sub-halos with circular velocities $V_{\rm c}\geq 75$\kms,
-respectively. These two sets of halos constitute the basis for our
-analysis.
+We use halo catalogs constructed using the Bound Density Maxima (BDM)
+algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
+density threshold of 360 times the mean density of the Universe, for 
+different redshifts we use the overdensity criterion by
+\cite{Bryan1998}. An important feature of BDM is that it allows us to
+detect sub-halos inside larger virialized structures.
 
-For each host halo we find its most massive sub-halo. Each pair
-host/sub-halo is considered as a potential Bullet system and is kept
-got the analysis described in the next section.
+All the raw data used in this Letter is
+available through the Multidark database \footnote{\texttt{www.multidark.org}}
+\citep{Riebe2013}.  Furthermore, in order to facilitate the
+reproducibility and reuse of our results we have made available all
+the data and the source code available in a public
+repository \footnote{\texttt{https://github.com/Fernandez-Trincado/Bullet\_Groups-2014}}.
+
+In this Letter we make a study at four different redhifts $z=0.0,0.25,
+0.5$ and $1.0$. First, we select all the host halos (i.e. halos that
+are not inside a larger halo) with circular velocities $V_{\rm c}\geq
+300$\kms. Then, we select the sub-halos with circular velocities
+$V_{\rm c}\geq 75$\kms. The objective is to use this sub-halos as the
+tracer of the sub-dominant dark matter clump in the merging cluster,
+i.e. the bullets.
+
+For the redshifts $z=0.0,0.25,
+0.5$ and $1.0$ we find $10041, 10346, 10554$ and $10382$ host halos
+and $157853, 177331, 195072, 225188$ sub-halos, respectively. These
+two sets (host halos and sub-halos) constitute the basis for our
+analysis. We find now for each host halo we its most massive sub-halo. Each pair
+host halo/sub-halo is considered as a potential Bullet system and is
+kept for the analysis described in the next Section.
 
@@
 
-\subsection{Reproducibility of our results}
-In order to facilitate the reproducibility and reuse of our results we
-have made available all the data and the source code available in a public
-repository\footnote{\texttt{https://github.com/Fernandez-Trincado/Bullet\_Groups-2014}.}
-
 \section{Observational Implications}

### 2014-03-11 paper/ms.tex
section 3

@@
 DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
-\citep{Dahle2013}. Recently \citep{Gastaldello} observed baryonic-DM
-displacement if $124\pm 20$ kpc in a group-like system with a total
+\citep{Dahle2013}. Recently \citep{Gastaldello} observed a baryonic-DM
+displacement if $124\pm 20$ kpc in \bullg, a group-like system with a total
 mass $2.4\pm 0.6 \times 10^{14}$\Msun. Systems of this mass are
@@
 
-For the redshifts $z=0.0,0.25,
-0.5$ and $1.0$ we find $10041, 10346, 10554$ and $10382$ host halos
-and $157853, 177331, 195072, 225188$ sub-halos, respectively. These
-two sets (host halos and sub-halos) constitute the basis for our
-analysis. We find now for each host halo we its most massive sub-halo. Each pair
-host halo/sub-halo is considered as a potential Bullet system and is
-kept for the analysis described in the next Section.
+For the redshifts $z=0.0,0.25, 0.5$ and $1.0$ we find $10041, 10346,
+10554$ and $10382$ host halos and $157853, 177331, 195072, 225188$
+sub-halos, respectively. These two sets (host halos and sub-halos)
+constitute the basis for our analysis. We find now for each host halo
+we its most massive sub-halo. Each pair host halo/sub-halo is
+considered as a potential Bullet system and is kept for the analysis
+described in the next Section.
 
@@
 
-The Bullet groups is composed by two halos. the host halo and the sub
-halo. This configuration is described by the position and velocity of
-the sub-halo in a frame of reference where the main halo is at rest;
-thus  $\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and 
+The Bullet-like configurations are composed by two dark matter
+structures: the host halo and the dominant sub-halo. We describe the
+kinematics of this configuration by the 
+position and velocity vectors of the sub-halo in a frame of reference
+where the main halo is at rest; thus
+$\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
 $\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, where the subscripts $host$
@@
 
-The angle between these two vectors characterized by, 
+The angle between these two vectors can be characterized by, 
 \begin{equation}
@@
   \cos(\theta)=\frac{\vec{v{}}\cdotp{}\vec{r}}{\left\|\vec{v}{}\right\|
-    \left\|\vec{r}\right\|} 
+    \left\|\vec{r}\right\|} .
  \end{equation} 
 %
-encodes the geometry of the collision, i.e. cases of $|\mu|\approx 1$
-can be considered as head-on collisions while $|\mu|\approx 0$
-describe a grazing trajectory.
+This encodes relevant information to describe the collision,
+i.e. cases of $|\mu|\approx 1$ can be considered as head-on collisions
+while $|\mu|\approx 0$ describes a grazing trajectory.
 
-The bullet-like encounter can be instantaneously described by
-quantities the following quantities the circular velocity of the host
-and the sub-halo, $V_{\rm c,host}$ and $V_{\rm c,  sub}$; the size of
-the host halo $R_{\rm vir}$; the relative position and velocity of the
-substructure, $\vec{v}$ and $\vec{r}$; and the angle between the
-position and velocity $\mu$.
+The geometrical configuration can be further described by the
+following quantities. The circular velocity of each component, $V_{\rm
+  c,host}$ for the host and $V_{\rm c, sub}$ for the sub-halo and the
+size of the host halo $R_{\rm vir}$.
 
-As a first approximation there are two quantities that are available
-from observations of these Bullet-like systems. The projected distance
-between two dominant dark matter clumps and the ratio of the
-galaxies luminosities associated to them. From the simulation point
-of view this can be translated into the 2D projected values of
-$||\vec{r}||$, its value relative to the virial radius $D_{\rm off}=
-||\vec{r}||_{\rm 2D}/R_{\rm vir}$ and the ratio of the circular velocities
-of the two clumps $V_{\rm c,sub}/V_{\rm c,host}$. In a higher degree
-of detail, in order to gain better insight we use
-the sub-structure velocity as a fraction of the host's circular
-velocity, $||\vec{r}||/V_{\rm c, host}$, as a measure of the the strength
-of the interaction.  Finally, we also measure the geometry of each
-interaction through the values for $\mu$.
+As a zero-th order approximation, in this paper we work with three
+quantities that are available from observations of Bullet-like
+systems. The projected distance between two dominant DM clumps, the
+projected distance between the DM-baryonic clumps and the ratio of the galaxies
+luminosities associated to the DM clumps.
 
-All the physical quantities described above can be used to describe
+From the simulation point of view, the first quantity can be
+translated into the 2D projected values of $||\vec{r}||$ and its value
+relative to the virial radius $D_{\rm   off}= ||\vec{r}||_{\rm
+  2D}/R_{\rm vir}$. The last quantity can be approximated by ratio of
+the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm
+  c,host}$ which under conditions of constant mass-to-light ratios
+should be equal to the square root of the luminosity ratio. The second
+quantity is not directly available from a DM-only simulation but, as we
+show in the Results section, can be  inferred from the available
+information.
+
+In order to gain better insight, we use two
+quantities that are not readily available from observations but can be
+measured in the simulation. The first one is the sub-structure
+velocity as a fraction of the host's circular velocity, $||\vec{v}||/V_{\rm c, host}$, as a measure of the the strength of the
+merger.  The second is $\mu$ to measure the geometry (head-on
+vs. grazing) of each collision.
+
+The physical quantities described above can be used to describe
 the three main stages in a bullet-like encounter. First, the sub-halo
@@
 center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
-this quantities in Section XXX to fully characterize the different
-kind of interactions observed in the Bolshoi simulation.
+this quantities in the enxt section to fully characterize the different
+kind of interactions observed in the Bolshoi Run,
 

### 2014-03-11 paper/ms.tex
subsection 4.1

@@
 
-The Bullet Cluster (massive cluster of galaxies \bulla) provided a new
+The Bullet Cluster (\bulla) provided a new
 kind of observational evidence for the existence of dark matter
@@
 $\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, where the subscripts $host$
-and $sub$ refer to the host and sub-halo in the frame of reference of
-the simulation, respectively.
+and $sub$ refer to the position of the minium of potential for the
+host and sub-halo in the frame of reference of the simulation,
+respectively.
 
@@
   c,host}$ for the host and $V_{\rm c, sub}$ for the sub-halo and the
-size of the host halo $R_{\rm vir}$.
+size of the host halo $R_{\rm vir}$. Another useful quantity computed
+in the simulation is the distance between the minium of potential for
+the host halo and its center of mass, $X_{\rm
+  off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$ which serves as a
+measurement of how perturbed is the host halo.
 
@@
   Integrated probability distribution for the displacement
-  between the host halo and its largest sub-halo. The left panel
+  between the center of the host halo and its dominant sub-halo. The left panel
   shows the results in terms of the physical displacements while
   the right panel shows the displacements normalized by the virial radius of
-  the host halo. The continuous line corresponds to the halos in the
-  group sample $V_{\rm circ,host}>700\kms$ and the dashed lines to the
-  sample $V_{\rm circ,host}<700\kms$.
-  The vertical lines corresponds to mean estimate separation 
-  between the two dark matter clumps in the results reported by
-  \citet{Gastaldello} for the group SL2S J08544-0121. Between $50\%$
+  the host halo. The continuous (dashed) line corresponds to the halos in the
+  cluster (group).
+  The vertical lines shows the mean and uncertainties in the estimated
+  separation  between the two dark matter clumps in the results reported by
+  \citet{Gastaldello} for the \bullg. Between $50\%$
   to $60\%$ of the groups show a displacement equal or larger than
@@
     c,host}$-$d_{2D}$. The left panel corresponds to clusters and the
-  right panel to groups. The circle with error bars corresponds to
+  right panel to groups. The star with error bars corresponds to
   \bullg data reported from \citet{2013A&A...552A..80M} and
@@
 
-The panel with the physical displacements also shows a vertical stripe
-with the estimated displacement for the Bullet-group reported by
-\cite{Gastaldello}. Considering this system as consistent withe the
-groups sample we see that a fraction of $\sim 15\pm 2\%$ of the groups
-should present a displacement equal or larger than the one estimated
-for \bullg, this fraction is close to $45\pm2\% $. The panel with the
-normalized displacements shows a  distribution that can be considered
-close to universal in the sense that the two samples (groups and
-clusters) at all redshifts present a similar trend.[...]
+The panel with the projected 2D physical displacements also shows a
+vertical stripe with the estimated displacement for the Bullet-group reported by
+\cite{Gastaldello}. In the group sample we see that a fraction of
+$50\%$ to $60\%$  should present a displacement equal than the
+estimate for \bullg; in the cluster sample this fraction increases to
+$80\%$-$85\%$. This fraction is naturally higher in more massive
+systems because they are larger in size. Normalizing the displacements
+by the virial radius, right panel Figure \ref{fig:displacement}, we
+see that the distribution is the same regardless of the sample and the
+redshift.
 
 Figure \ref{fig:mass_displacement} shows 2D histograms in a plane
-composed by the ratio of the two circular velocities $V_{\rm c,
-  sub}/V_{\rm c, host}$ and the physical displacements. This is
-revealing because these two quantities can be constrained by
-observations. The displacement is a direct observable, while the ratio
-of the circular velocities can be estimated from lensing studies or
-approximated by the ratio of the total galaxy luminosity associated
-with the galaxy peaks.
+defined by the ratio of the two circular velocities $V_{\rm c,
+  sub}/V_{\rm c, host}$ and the projected 2D physical displacements;
+quantities that can be constrained by observations. The displacement
+is a direct observable, while the ratio of the circular velocities can
+be estimated from lensing studies or approximated by the ratio of the
+total galaxy luminosity associated with the galaxy peaks or by a
+lensing reconstruction.
 
 To construct this figure we co-add all the halos in the sample (left,
-groups; right, clusters) at all redshifts. We stack the data because
-we do not observe any strong time evolution, additionally this allows
-us to increase the signal in each bin. Overplotted there is an circle
-with error bars that represents the observational estimates for the
-system \bullg using the fraction in velocity dispersion in
-the line-of-sigth of the group SL2S SJ08544-0121
-($\sigma_{host}=341^{+43}_{-109}$\kms and
+clusters; right, groups) at all redshifts. We stack the data because
+we do not observe any strong redshift dependence, additionally this allows
+us to increase the signal in each bin. We overplot a star with error
+bars that represents the observational estimates for the system
+\bullg\ using the fraction in velocity dispersion in the line-of-sigth
+of the group SL2S SJ08544-0121 ($\sigma_{host}=341^{+43}_{-109}$\kms and
 $\sigma_{sub}=185^{+30}_{-62}$\kms) reported by

### 2014-03-11 paper/ms.tex
conclusions

@@
 systems. The projected distance between two dominant DM clumps, the
-projected distance between the DM-baryonic clumps and the ratio of the galaxies
-luminosities associated to the DM clumps.
+projected distance between the DM-baryonic clumps and the ratio of the
+mass associated to the DM clumps.
 
@@
 relative to the virial radius $D_{\rm   off}= ||\vec{r}||_{\rm
-  2D}/R_{\rm vir}$. The last quantity can be approximated by ratio of
-the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm
-  c,host}$ which under conditions of constant mass-to-light ratios
-should be equal to the square root of the luminosity ratio. The second
-quantity is not directly available from a DM-only simulation but, as we
-show in the Results section, can be  inferred from the available
-information.
+  2D}/R_{\rm vir}$. The last quantity, the mass ratio, can be
+approximated by ratio of the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm  c,host}$ which should be equal to the square root of the mass
+ratio. The second quantity, the projected DM-baryon distance, is not
+directly available from a DM-only simulation but, as we show in the
+Results section, can be inferred from the available information.
 
@@
 in physical units while the right panel show the same values
-normalized by the circular velocity of the host halo. The line coding
+normalized by the circular velocity of the host halo. The line encoding
 follows the same structure as Figure \ref{fig:displacement}}
 \label{fig:velocities}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{figure_4.eps}
+\end{center}
+\caption{2D histograms in the plane $\mu$-$D_{\rm off}$. The left
+  panel corresponds to clusters and the right panel to groups. The data
+  used to construct this histogram includes the halos at all redshifts.}
+\label{fig:geometry}
 \end{figure*}
@@
 the host halo. The left panel presents this velocity in physical units
-while the left panel presents them as a fraction of the circular
+while the right panel presents them as a fraction of the circular
 velocity of the host halo.
@@
 of the host halo and the redshift the integrated distributions lie
-very close to each other.
+very close to each other.  The universality of this profile extends to
+the group mass range the findings of \citep{Hayashi2006} for clusters.
 
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{figure_4.eps}
-\end{center}
-\caption{2D histograms in the plane $\mu$-$D_{\rm off}$. The left
-  panel corresponds to clusters and the right panel to groups. The data
-  used to construct this histogram includes the halos at all redshifts.}
-\label{fig:geometry}
-\end{figure*}
-
 Figure \ref{fig:geometry} presents the geometry of the bullet groups using the 
@@
 most of the configurations have $|mu|>0.9$ ($\theta\leq 30^{\circ}$),
-meaning that most of the collisions can be described as a head-on while
-only a minority with $|mu|<0.9$ have more tangential trajectories. For
-the pairs on radial trajectories there are three regions of interest
-in this plane that describe different stages in the collision,
-assuming that the sub-halo merges or falls below the detection
-threshold after the first pass through the center of the host halo.
+meaning that most of the collisions can be described as a head-on
+encounter while only a minority with $|mu|<0.9$ have grazing
+trajectories. For the pairs on radial trajectories there are three
+regions of interest in this plane that describe different stages in
+the collision, assuming that the sub-halo merges (or falls below the
+BDM detection threshold) right at its second pass through the center
+of the host halo \citep{Poole2006}.
 
@@
 $\mu\approx-1$ and $D_{\rm off}<0.6$ which corresponds to the
-secondary infall after apogee.
+secondary infall after apogee. We use this sequence in the next
+subsection to estimate the expected displacement between baryons and
+the dominant DM clump.
 
@@
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.5\textwidth]{figure_5.eps}
-\end{center}
-\caption{Integrated probability distribution for the estimated
-  baryonic displacements in the group and cluster samples. The
-  continuous line marked as $P_{2D}$ shows the statistics reported by
-  \citet{ForeroRomero2010} for a cosmological simulation including DM
-  and baryons. The vertical lines correspond to the mean value and
-  uncertainty of the displacement measured for \bullg.}
-\label{fig:baryonic_displacements}
-\end{figure}
+Strictly speaking, the results we have derived so far, apply to multi-modal
+groups and their expected separation between the two dominant dark
+matter clumps. These displacements cannot be interpreted that all have a
+corresponding DM-baryon displacement.
 
-These different collision geometries will produce different results in
-terms of the displacement between dark matter and baryons. Strictly
-speaking, the results we have derived so far, apply to multi-modal groups and their
-expected separation between the two dominant dark matter clumps but it
-should not be interpreted that all have a corresponding DM-baryon
-displacement. The systems where the halo is starting to fall into the
-host ($\mu\approx-1$, $D_{\rm off}>0.6$) should not present a
-detectable DM-baryon displacement.
+However, these different stages for a collision, that we describe at
+the end of the previous sub-section, can produce different results in
+terms of the displacement between dark matter and baryons. For
+instance, the systems where the halo is starting to fall into the host
+($\mu\approx-1$, $D_{\rm off}>0.6$) should not present a detectable
+DM-baryon displacement.  We do expect such displacements when the
+sub-structure has already passed through the center of the host halo,
+i.e. cases where $\mu\approx 1$.
 
-We clearly expect such displacement in the case where the
-sub-structure has already passed through the center of the host
-halo. In this section we attempt an estimation for the DM-baryon
-displacement statistics. We work under the following
-hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
-baryonic displacement, $d_{2D}^{\rm bar}$, equal to zero. Second, we
-consider that all systems with infalling velocities $\mu<-0.9$ and
-large displacements $D_{\rm off}>0.6$ also have baryonic displacements
-equal to zero. Third, for all the other cases we estimate the
-displacement between the baryons and the dominant DM peak by the
-distances between the dominant peak and the center of mass of the main
-halo, $d_{2D}^{\rm bar}=D_{\rm off} R_{\rm vir}$, where $X_{\rm off}$
-is the offset computed for each host halo in the original catalog.
+In this sub- section we estimate DM-baryon displacement statistics. We
+work under the following hypothesis. First, we consider that systems
+with $|\mu|<0.9$ have a baryonic displacement, $d_{2D}^{\rm bar}$,
+equal to zero. This means that only head-on encounter produce a
+displacement. Second, we consider that all systems with infalling
+velocities $\mu<-0.9$ and large displacements $D_{\rm off}>0.6$ also
+have baryonic displacements equal to zero. Third, for all the other
+cases we estimate the displacement between the baryons and the
+dominant DM peak by the distances between the dominant peak and the
+center of mass of the main halo, $d_{2D}^{\rm bar} = X_{\rm off} R_{\rm
+  vir}$, where $X_{\rm off}$ is the offset computed between the minium
+of potential and the center of mass for each host halo.
 
@@
 that included a description for gas with $8$ times the volume of the
-Bolshoi Simulation. This fit is valid for separations larger than
-$70$\hkpc, beyond that separation we find that it provides a good
-description within a factor of $\sim 2$ of
+Bolshoi Simulation. The fit is valid for separations larger than
+$70$\hkpc, beyond which we find that it provides a remarkably good
+description within a factor of $\sim 2$ of our results. This gives us
+confidence in our approach to estimate the expected fraction of
+groups with a DM-baryon displacement.
+
+From Figure \ref{fig:baryonic_displacements} we see that only a
+fraction of $0.1\%$ to $1\%$ of the groups are expected to have a
+DM-baryon displacement equal or larger than $87\pm 14$\hkpc as
+observed in \bullg. This fraction rises to $4\%$ to $10\%$ in the case
+of clusters, consistent with the results reported by
+\cite{ForeroRomero2010}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{figure_5.eps}
+\end{center}
+\caption{Integrated probability distribution for the estimated
+  baryonic displacements in the group and cluster samples. Continous (dashed)
+  lines correspond to clusters (groups). The continuous black line
+  marked as $P_{2D}$ shows the statistics reported by
+  \citet{ForeroRomero2010} for a cosmological simulation including DM
+  and baryons. The vertical lines correspond to the mean value and
+  uncertainty of the displacement measured for \bullg.} 
+\label{fig:baryonic_displacements}
+\end{figure}
 
@@
 
-In this Letter we estimate fraction of galaxy groups
-that can present observational features associated to a
-bullet-like event. This is motivated by the recent observational
-results of \citep{Gastaldello} where a system (\bullg) on the mass range
-$1\times 10^{14}$\hMsun and velocity dispersion $650$\kms was reported
-to feature a displacement between its baryonic (hot gas) and dark
-matter components.
+In this Letter we estimate fraction of galaxy groups and clusters that
+can present observational features associated to a bullet-like
+event. This is motivated by the recent observational results of
+\citep{Gastaldello} where a system (\bullg) on the mass range $1\times
+10^{14}$\hMsun and velocity dispersion $650$\kms was reported to
+feature a displacement between its baryonic (hot gas) and dark matter
+components.
 
-Our estimate is based on large N-body dark matter only cosmological
-simulation. We estimate the distribution of projected displacements
+We estimate the distribution of projected displacements
 between the dominant DM clumps in two kinds of systems; groups with
@@
   c}>700$\kms. We report these results at four different redshifts
-$z=0.0,0.25,0.5$ and $10$.
+$z=0.0,0.25,0.5$ and $10$. Our results based on large N-body dark
+matter only cosmological simulation with such a resolution that allows
+to study the group mass range for the first time in the context of
+Bullet-like configurations.
 
-We find that a fraction of $50\%$-$60\%$ of the halos in the group
-sample present displacement equal or larger than the observed displacement
-for \bullg. For halos in the cluster sample this fraction increases to
-$80\%$-$85\%$.
+Our main results is that that a fraction of $50\%$-$60\%$ of the halos
+in the group sample present displacement equal or larger than the
+observed displacement for \bullg. For halos in the cluster sample this
+fraction increases to $80\%$-$85\%$. We also derive an
+estimate for the displacement between the DM and the baryonic
+component. In the group sample $0.1\%$-$1.0\%$ of the halos show a
+displacement equal or larger than  the  measurements of \bullg by
+\citep{Gastaldello}. In the cluster sample this fraction rises to
+$4\%$-$10\%$.
 
-We also describe the collision geometry by the angle between
-the position and velocity vectors of the sub-halo with respect to the
-host. This allows us to separate three different instances: the
-sub-halo crossing the host virial radius, the sub-halo going
-through the host's center and the secondary infall after reaching
-apogee.
+We also find distributions for the DM separation and the velocity of
+the bullet through its host. If these quantities are normalized by the
+virial radius and the circular velocity, respectively, we arrive at
+distributions close to universal that are similar for the two halo
+samples at all redshifts.
 
-From this analysis we derive an estimate for the displacement between
-the DM and the baryonic component. In the group sample
-$0.1\%$-$1.0\%$ of the halos show a displacement equal or larger than 
-the  measurements of \bullg by \citep{Gastaldello}. In the cluster
-sample this fraction rises to $4\%$-$10\%$.
+For the case of \bullg the fair comparison is achieved in the cluster
+sample, which have statistics dominated by objects of similar mass. In
+this case we conclude that the existence of such configuration is
+highly probable in $\Lambda$CDM (4$\%$ to $10\%$ abundance). In turn,
+for the same separation the fraction for groups is lower (0.1$\%$ to
+$1\%$). Taking into account that the difference in spatial abundance between
+these two samples is on the order of a factor of $10$, one can
+conclude that the absolute number of groups and clusters presenting a DM-baryon
+displacement larger or equal to \bullg should be of the same order.
 
-The results we present here can be used as a potential test of
-$\Lambda$CDM. [...]
+However, an interesting observational possibility opens up with
+surveys such as SL2S that can target a large number of groups and
+estimate its multi-modal nature from lensing analysis that can be used
+as a potential test of $\Lambda$CDM. In this case the absolute number
+of groups with a displacement of the same order of \bullg is larger by
+a factor of $\sim 8$ than the number of clusters with the same
+displacement.
 

### 2014-03-11 paper/ms.tex
first version for the coauthors

@@
 separations. The extension of the theoretical predictions and
-observational results towards low mass Bullet-like configurations,
-i.e. larger abundance of systems,  opens up the possibility for a new
-statistical test of  $\Lambda$CDM.  
+observational results towards low mass bi-modal dark matter
+configurations opens up the possibility for a new statistical test of
+$\Lambda$CDM.   
 \end{abstract}
@@
 
-This Letter is organized as the follows. In Section
+This Letter is organized as follows. In Section
 \ref{sec:simulation} we present the simulation and the halo catalogs
@@
 
-\section{Observational Implications}
-\label{sec:observations}
-
 \section{Conclusions}

### 2014-03-17 paper/ms.tex
minor

@@
 
+J.E. Forero-Romero acknowledges support from Vicerrector\'ia de
+Investigaciones through a FAPA starting grant.
+
+T. Verdugo acknowledges support from CONACYT through grant 165365 and
+203489 through the program Estancias posdoctorales y sab\'aticas al
+extranjero para la consolidaci\'on de grupos de investigaci\'on.
+
 \bibliographystyle{apj}

### 2014-03-18 paper/ms.tex
almost all comments are included

--- 2014-03-11 paper/ms.tex
@@
   M\'erida 5101-A, Venezuela\\
-  $^4$ Departamento de F\'isica y Astronom\'ia, Universidad de
+  $^4$ Instituto de F\'isica y Astronom\'ia, Universidad de
   Valpara\'iso, Avda. Gran Breta\~na 1111, Playa Ancha, Valpara\'iso
@@
 baryonic component. We extend previous results by
-studying two halo samples: groups and clusters. We find that 50\% to 60\%
+studying two halo samples: groups and clusters. We find that $(55\pm 5)\%$
 of the dark matter halos with circular velocities in the range
@@
 circular velocities larger than $700\kms$ (clusters) this fraction
-rises to $80\%$ to $85\%$. Using the same simulation we estimate the
-dark matter-to-baryon spatial separation and find that $0.1\%$ to
+rises to $(82\pm 3)\%$. Using the same simulation we estimate the
+dark matter-to-baryon spatial separation and find that $0.1$ to
 $1.0\%$ of the groups should present separations equal or
 larger than $87\pm 14$\hkpc corresponding to our observational
-benchmark; for clusters this fraction is in the range of $4\%$ to
-$10\%$, consistent with previous studies of dark matter to baryon
-separations. The extension of the theoretical predictions and
-observational results towards low mass bi-modal dark matter
-configurations opens up the possibility for a new statistical test of
-$\Lambda$CDM.   
+benchmark; for clusters this fraction rises to $(7\pm 3)\%$, consistent
+with previous studies of dark matter to baryon separations. The
+extension of the theoretical predictions and observational results
+towards low mass bi-modal dark matter configurations opens up the
+possibility for a new statistical test of  $\Lambda$CDM.
 \end{abstract}
@@
 
-The Bullet Cluster (\bulla) provided a new
-kind of observational evidence for the existence of dark matter
+The Bullet Cluster (\bulla) provided a new kind of observational
+evidence for the existence of dark matter
 \citep{Markevitch2004,Clowe2006}. Quantifying the displacement between
@@
 and baryonic component \citep{ForeroRomero2010} to estimate the
-expected abundance of such events in a $\Lambda$CDM Universe and even
-explore possible extensions to the concordance cosmological model
+expected abundance of such events in a $\Lambda$CDM Universe, putting
+constraints on the dark matter particle self-interaction cross section
+and even explore possible extensions to the concordance cosmological model
 \citep{Farrar2007,Lee2010,Lee2012}.
@@
 components. These two conditions (merger rates, maximum possible
-displacement) are a funcion of halo mass in $\Lambda$CDM
+displacement) are a funcion of DM halo mass in $\Lambda$CDM
 cosmologies.  Such study has been performed for clusters but not for
 lower mass systems \citep{ForeroRomero2010}. The existence of objects
-like \bullg and observational campaigns like the Strong Lensing Legacy
-Survey (SL2S) open up the possibility of finding multi-modal dark
-matter distributions in the group mass range.
+like \bullg\ and observational campaigns like the Strong Lensing Legacy
+Survey (SL2S) \citep{Cabanac2007,More2012} open up the possibility of finding
+multi-modal dark matter distributions in the group mass range.
 
@@
 Section \ref{sec:results} we present our results and observational
-perspectives to finally conclude in Sections \ref{sec:conclusions}.
+perspectives to finally conclude in Section \ref{sec:conclusions}.
 
@@
 We use the Bolshoi Run, a cosmological DM only simulation over a cubic
-volume of 250\hMpc comoving on a side. The simulation uses the ART code to
-follow the evolution of a dark matter density field sampled with
-$2048^3$ from $z=80$ to $z=0$. The cosmology used  corresponds
-to  the spatially flat concordance model with the following
-parameters:  the density parameter for matter (dark matter and baryons)
-$\Omega_m=0.27$, the density parameter for baryonic matter
+volume of 250\hMpc comoving on a side. The simulation uses the ART
+code \citep{Kravtsov1997} to follow the evolution of a dark matter
+density field sampled with $2048^3$ from $z=80$ to $z=0$. The
+cosmology used  corresponds to  the spatially flat concordance model
+with the following parameters:  the density parameter for matter (dark
+matter and baryons) $\Omega_m=0.27$, the density parameter for baryonic matter
 $\Omega_b=0.0469$, the density parameter for dark energy
@@
 for halos with $100$ particles corresponding to a mass of
-$1.35\times10^{10}$\hMsun or a maximum circular velocity $V_{c}$ of
+$1.35\times10^{10}$\hMsun\ or a maximum circular velocity $V_{c}$ of
 $50$\kms.
@@
 algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
-density threshold of 360 times the mean density of the Universe, for 
-different redshifts we use the overdensity criterion by
-\cite{Bryan1998}. An important feature of BDM is that it allows us to
-detect sub-halos inside larger virialized structures.
+density threshold of 360 times the mean density of the Universe (or
+200 times the critical density), for different redshifts we use the
+overdensity criterion by \cite{Bryan1998}. An important feature of BDM
+is that it allows us to detect sub-halos inside larger virialized
+structures.
 
-All the raw data used in this Letter is
-available through the Multidark database \footnote{\texttt{www.multidark.org}}
+All the raw data used in this Letter is available through the
+Multidark database \footnote{\texttt{www.multidark.org}}
 \citep{Riebe2013}.  Furthermore, in order to facilitate the
@@
 
-In this Letter we make a study at four different redhifts $z=0.0,0.25,
+In this Letter we make a study at four different redshifts $z=0.0,0.25,
 0.5$ and $1.0$. First, we select all the host halos (i.e. halos that
 are not inside a larger halo) with circular velocities $V_{\rm c}\geq
-300$\kms. Then, we select the sub-halos with circular velocities
-$V_{\rm c}\geq 75$\kms. The objective is to use this sub-halos as the
-tracer of the sub-dominant dark matter clump in the merging cluster,
-i.e. the bullets.
+300$\kms ($\geq 1\times 10^{13}\\hMsun$). Then, we select the sub-halos with
+circular velocities $V_{\rm c}\geq 75$\kms ($\geq 5\times
+10^{10}\hMsun$). The objective is to use this sub-halos as the tracer
+of the sub-dominant dark matter clump in the merging cluster, i.e. the
+bullets.
 
@@
 sub-halos, respectively. These two sets (host halos and sub-halos)
-constitute the basis for our analysis. We find now for each host halo
-we its most massive sub-halo. Each pair host halo/sub-halo is
-considered as a potential Bullet system and is kept for the analysis
-described in the next Section.
+constitute the basis for our analysis. We associate each host halo
+to its most massive sub-halo, each one of these pairs (host \& sub-halo)
+is considered as a potential Bullet system and is kept for the
+analysis described in the next Section.
 
@@
   off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$ which serves as a
-measurement of how perturbed is the host halo.
+measurement of how much the host halo is perturbed.
 
 As a zero-th order approximation, in this paper we work with three
-quantities that are available from observations of Bullet-like
-systems. The projected distance between two dominant DM clumps, the
-projected distance between the DM-baryonic clumps and the ratio of the
-mass associated to the DM clumps.
+observed quantities for Bullet-like systems. The projected distance
+between two dominant DM clumps, the projected distance between the
+DM-baryonic clumps and the ratio of the mass associated to the DM
+clumps.
 
@@
 
-In order to gain better insight, we use two
-quantities that are not readily available from observations but can be
-measured in the simulation. The first one is the sub-structure
-velocity as a fraction of the host's circular velocity, $||\vec{v}||/V_{\rm c, host}$, as a measure of the the strength of the
-merger.  The second is $\mu$ to measure the geometry (head-on
-vs. grazing) of each collision.
+%In order to gain better insight, we use two
+%quantities that can be infered from the simulation. The first one is
+%the sub-structure velocity as a fraction of the host's circular
+%velocity, $||\vec{v}||/V_{\rm c, host}$, as a measure of the the
+%strength of the merger.  The second onw is $\mu$, which measures the geometry
+%(head-on vs. grazing) of each interaction.
 
@@
 collision, $||\vec{r}||/R_{\rm vir}\approx 1$ and
-$\mu\approx<0.0$. Second, as the sub-halo crosses for the first time
+$\mu\lessapprox<0.0$. Second, as the sub-halo crosses for the first time
 the center of the host halo $||\vec{r}||/R_{\rm vir} < 1.0$ and
@@
 center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
-this quantities in the enxt section to fully characterize the different
+these quantities in the next section to fully characterize the different
 kind of interactions observed in the Bolshoi Run,
@@
 \caption{
-  Integrated probability distribution for the displacement
-  between the center of the host halo and its dominant sub-halo. The left panel
-  shows the results in terms of the physical displacements while
-  the right panel shows the displacements normalized by the virial radius of
-  the host halo. The continuous (dashed) line corresponds to the halos in the
+  Integrated probability distribution for the displacement between the
+  center of the host halo and its dominant sub-halo. The left panel
+  shows the results in terms of the physical displacements while the
+  right panel shows the displacements normalized by the virial radius
+  of the host halo. The continuous (dashed) line corresponds to the halos in the
   cluster (group).
-  The vertical lines shows the mean and uncertainties in the estimated
-  separation  between the two dark matter clumps in the results reported by
-  \citet{Gastaldello} for the \bullg. Between $50\%$
+  The vertical lines show the mean value and uncertainties ($133\pm
+  21$\hkpc) in the  separation between the two dark matter clumps
+  estimated in \citet{Gastaldello} for the \bullg. Between $50\%$
   to $60\%$ of the groups show a displacement equal or larger than
@@
   right panel to groups. The star with error bars corresponds to
-  \bullg data reported from \citet{2013A&A...552A..80M} and
+  \bullg\ data reported from \citet{2013A&A...552A..80M} and
   \citet{Gastaldello}. The data used to construct the histograms
@@
 estimate for \bullg; in the cluster sample this fraction increases to
-$80\%$-$85\%$. This fraction is naturally higher in more massive
-systems because they are larger in size. Normalizing the displacements
-by the virial radius, right panel Figure \ref{fig:displacement}, we
-see that the distribution is the same regardless of the sample and the
-redshift.
+$80\%$-$85\%$. The uncertainties in this estimates are derived from
+the uncertainties in the displacement measurement for \bullg.This
+fraction is naturally higher in more massive systems because they are
+larger in size. Normalizing the displacements by the virial radius,
+right panel Figure \ref{fig:displacement}, we see that the
+distribution is the same regardless of the sample and the redshift.
 
@@
   sub}/V_{\rm c, host}$ and the projected 2D physical displacements;
-quantities that can be constrained by observations. The displacement
-is a direct observable, while the ratio of the circular velocities can
-be estimated from lensing studies or approximated by the ratio of the
-total galaxy luminosity associated with the galaxy peaks or by a
-lensing reconstruction.
+quantities that can be constrained by observations.
 
@@
 clusters; right, groups) at all redshifts. We stack the data because
-we do not observe any strong redshift dependence, additionally this allows
+we do not observe any strong redshift dependence. This allows
 us to increase the signal in each bin. We overplot a star with error
-bars that represents the observational estimates for the system
+bars that represents the observational constraints for the system
 \bullg\ using the fraction in velocity dispersion in the line-of-sigth
@@
 
-\subsection{Relative Velocities}
-\label{sec:velocities}
+%\subsection{Relative Velocities}
+%\label{sec:velocities}
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.9\textwidth]{figure_3.eps}
-\end{center}
-\caption{Integrated probability distribution for the relative velocity of the
-sub-halo with respect to its host. The left panel shows the results
-in physical units while the right panel show the same values
-normalized by the circular velocity of the host halo. The line encoding
-follows the same structure as Figure \ref{fig:displacement}}
-\label{fig:velocities}
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%\includegraphics[width=0.9\textwidth]{figure_3.eps}
+%\end{center}
+%\caption{Integrated probability distribution for the relative velocity of the
+%sub-halo with respect to its host. The left panel shows the results
+%in physical units while the right panel show the same values
+%normalized by the circular velocity of the host halo. The line encoding
+%follows the same structure as Figure \ref{fig:displacement}}
+%\label{fig:velocities}
+%\end{figure*}
 
@@
 
-In Figure \ref{fig:velocities} we present the integrated probability
-of the relative peculiar velocities of the sub-halos with respect to
-the host halo. The left panel presents this velocity in physical units
-while the right panel presents them as a fraction of the circular
-velocity of the host halo.
+%In Figure \ref{fig:velocities} we present the integrated probability
+%of the relative peculiar velocities of the sub-halos with respect to
+%the host halo. This velocity is presented in the left panel in
+%physical units and in the right panel as a fraction of the circular
+%velocity of the host halo.
 
-The panel with the normalized velocities shows that the distribution
-of sub-halo velocities is close to universal. Regardless of the mass
-of the host halo and the redshift the integrated distributions lie
-very close to each other.  The universality of this profile extends to
-the group mass range the findings of \citep{Hayashi2006} for clusters.
+%The panel with the normalized velocities shows that the distribution
+%of sub-halo velocities is close to universal. Regardless of the mass
+%of the host halo and the redshift the integrated distributions lie
+%very close to each other.  The universality of this profile also holds
+%for the group mass range. extending the result found by
+%\citep{Hayashi2006} for cluster mass halos.
 
-The median of this distribution is located at $v/V_{\rm
-  c,host}=1.1$. We also note the strong break at $v/V_{\rm
-  c,host}=3.0$ that is present in the data from the group sample that
-allows us to probe fractions on the order of $10^{-4}$.  This break is
-located close the escape velocity of $v/V_{\rm c,host}$ for dark
-matter halos following a NFW profile with a concentration value
-$c\approx 6$ \citep{Hayashi2006}.
+%The median of this distribution is located at $v/V_{\rm
+%  c,host}=1.1$. We also note the strong break at $v/V_{\rm
+%  c,host}=3.0$ present in the data from the group sample, which
+%allows us to probe fractions on the order of $10^{-4}$.  This break is
+%located close the escape velocity of $v/V_{\rm c,host}$ for dark
+%matter halos following a NFW profile with a concentration value
+%$c\approx 6$ \citep{Hayashi2006}.
 
 \subsection{Collision Geometries}
-\label{fig:geometry}
+\label{sec:geometry}
 
@@
 variables $\mu$ and $D_{\rm off}$. The first evident feature is that
-most of the configurations have $|mu|>0.9$ ($\theta\leq 30^{\circ}$),
+most of the configurations have $|\mu|>0.9$ ($\theta\leq 30^{\circ}$),
 meaning that most of the collisions can be described as a head-on
-encounter while only a minority with $|mu|<0.9$ have grazing
+encounter while only a minority with $|\mu|<0.9$ have grazing
 trajectories. For the pairs on radial trajectories there are three
@@
 range of radii for the apogee.  The third region corresponds to
-$\mu\approx-1$ and $D_{\rm off}<0.6$ which corresponds to the
+$\mu\approx-1$ and $D_{\rm off}<0.6$ that is the the
 secondary infall after apogee. We use this sequence in the next
@@
 
-Strictly speaking, the results we have derived so far, apply to multi-modal
+Strictly speaking, the results we have derived so far apply to multi-modal
 groups and their expected separation between the two dominant dark
-matter clumps. These displacements cannot be interpreted that all have a
-corresponding DM-baryon displacement.
+matter clumps. However, a non-zero DM-DM displacement cannot be
+interpreted as having a corresponding non-zero DM-baryon
+displacement. Given that we use a DM only simulation, we have to find
+a way to estimate DM-baryon displacements from the available information.
 
-However, these different stages for a collision, that we describe at
-the end of the previous sub-section, can produce different results in
-terms of the displacement between dark matter and baryons. For
-instance, the systems where the halo is starting to fall into the host
-($\mu\approx-1$, $D_{\rm off}>0.6$) should not present a detectable
-DM-baryon displacement.  We do expect such displacements when the
-sub-structure has already passed through the center of the host halo,
-i.e. cases where $\mu\approx 1$.
+This estimate is based on the different collision stages described at
+the end of the previous sub-section.  For instance, in systems where
+the halo is starting to fall into the host ($\mu\approx-1$, $D_{\rm
+  off}>0.6$) the DM-baryon displacement should be equal to
+zero. However, when the  sub-structure has already passed through the
+center of the host halo, i.e. cases where $\mu\approx 1$, the
+DM-baryon displacement should be different from zero.
 
-In this sub- section we estimate DM-baryon displacement statistics. We
-work under the following hypothesis. First, we consider that systems
-with $|\mu|<0.9$ have a baryonic displacement, $d_{2D}^{\rm bar}$,
-equal to zero. This means that only head-on encounter produce a
-displacement. Second, we consider that all systems with infalling
-velocities $\mu<-0.9$ and large displacements $D_{\rm off}>0.6$ also
-have baryonic displacements equal to zero. Third, for all the other
-cases we estimate the displacement between the baryons and the
-dominant DM peak by the distances between the dominant peak and the
-center of mass of the main halo, $d_{2D}^{\rm bar} = X_{\rm off} R_{\rm
-  vir}$, where $X_{\rm off}$ is the offset computed between the minium
-of potential and the center of mass for each host halo.
+To estimate the DM-baryon displacement we  work under the following
+hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
+baryonic displacement, $d_{2D}^{\rm bar}$, equal to zero. This means
+that only head-on encounters produce a displacement. Second, we
+consider that all systems with infalling velocities $\mu<-0.9$ and
+large displacements $D_{\rm off}>0.6$ also have baryonic displacements
+equal to zero. Third, for all the other cases we estimate the
+displacement between the baryons and the dominant DM peak by
+$d_{2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$
+is the offset computed between the minium of potential and the center
+of mass for each host halo computed from all the matter inside the
+virial radius.
 
@@
 represented the results for groups and the continuous lines correspond
-to clusters. As a test of our approach we compare the cluster results
+to clusters. As a test of our model we compare the cluster results
 against the analytic fit provided by \cite{ForeroRomero2010}. This fit
 reproduces the statistics for the DM-baryon separation found for
-clusters more massive than $>10^{14}$\hMsun in a simulation
-that included a description for gas with $8$ times the volume of the
+clusters more massive than $>10^{14}$\hMsun\ in a simulation
+which included a description for DM and gas with $8$ times the volume of the
 Bolshoi Simulation. The fit is valid for separations larger than
@@
 
+\subsection{Possible Observational Statistical Tests}
+
+Recently \citep{Foex2013} presented an analysis of $80$ galaxy groups
+from the SL2S sample. From the light distribution, only $34$ objects
+($\approx 42\%$) have regular isophotes, $33$ had ellongated
+isophotes (hints of merging system), and $13$ ($\approx 16\%$) had a
+clear bi-modal light distribution.
+
+The bi-modal objects are defined to have at least a clear second
+luminosity peak within $350$\hkpc from the main halo, as traced by the
+strong lensing system.  The lowest separation in those systems is
+$64$ \hkpc and the average is $145\pm 52$\hkpc. Comparing this average
+displacement against the integratied distribution for the group sample (left
+panel, Figure \ref{fig:displacement}) one would expects between $40\%$
+to $80\%$ of DM halos to present those displacements. This fraction is
+certainly larger than the $\approx 16\%$ inferred from the
+observational sample.
+
+We have taken the results from the simulation and selected all the
+objects in the group sample with a DM-DM displacement less than
+$350$\hkpc but larger than $64$\hkpc to find XXX objects in
+total. From this subsample we find that XXX have a DM-baryon
+displacement larger than $87$\hkpc.
+
+This rough comparison hints that it is possible to find a large fraction
+of multi-modal groups with a DM-baryon displacement in a $\Lambda$CDM
+cosmology. A proper comparison must take into account all the
+observational uncertainties and biases to derive a stronger prediction from the
+simulation, something that is beyond the scope of this Letter.
+
 \section{Conclusions}
@@
 \citep{Gastaldello} where a system (\bullg) on the mass range $1\times
-10^{14}$\hMsun and velocity dispersion $650$\kms was reported to
+10^{14}$\hMsun\ and velocity dispersion $650$\kms was reported to
 feature a displacement between its baryonic (hot gas) and dark matter
@@
 between the dominant DM clumps in two kinds of systems; groups with
-circular velocities $300\kms<V_{\rm c}<700\kms$ and clusters with $V_{\rm
-  c}>700$\kms. We report these results at four different redshifts
-$z=0.0,0.25,0.5$ and $10$. Our results based on large N-body dark
-matter only cosmological simulation with such a resolution that allows
-to study the group mass range for the first time in the context of
-Bullet-like configurations.
+circular velocities $300\kms<V_{\rm c}<700\kms$ ($1.0\times
+10^{13}\hMsun < M_{\rm vir}<1.0\times 10^{14}\hMsun$) and clusters with $V_{\rm
+  c}>700$\kms ($M_{\rm vir}>1.0\times 10^{14}\hMsun$). We report these
+results at four different redshifts $z=0.0,0.25,0.5$ and $10$. Our
+results are based on large DM-only N-body cosmological simulation with
+a resolution that allows to study for the first time Bullet-like
+configurations in the mass range of galaxy groups.
 
@@
 component. In the group sample $0.1\%$-$1.0\%$ of the halos show a
-displacement equal or larger than  the  measurements of \bullg by
+displacement equal or larger than  the  measurements of \bullg\ by
 \citep{Gastaldello}. In the cluster sample this fraction rises to
@@
 
-For the case of \bullg the fair comparison is achieved in the cluster
-sample, which have statistics dominated by objects of similar mass. In
+For the case of \bullg\ a fair comparison is achieved against cluster
+sample, which has statistics dominated by objects of similar mass. In
 this case we conclude that the existence of such configuration is
@@
 for the same separation the fraction for groups is lower (0.1$\%$ to
-$1\%$). Taking into account that the difference in spatial abundance between
-these two samples is on the order of a factor of $10$, one can
-conclude that the absolute number of groups and clusters presenting a DM-baryon
-displacement larger or equal to \bullg should be of the same order.
+$1\%$). Taking into account that the difference in spatial abundance
+between these two samples is on the order of a factor of $10$, one can
+conclude that the absolute number of groups and clusters presenting a
+DM-baryon displacement larger or equal to \bullg\ should be of the
+same order.
 
-However, an interesting observational possibility opens up with
-surveys such as SL2S that can target a large number of groups and
-estimate its multi-modal nature from lensing analysis that can be used
-as a potential test of $\Lambda$CDM. In this case the absolute number
-of groups with a displacement of the same order of \bullg is larger by
-a factor of $\sim 8$ than the number of clusters with the same
-displacement.
+An observational possibility opens up with surveys such as SL2S that
+targetted a large number of groups and estimate its multi-modal nature
+from lensing analysis \citep{Foex2013}, an approach that can be
+exploited with upcoming lensing surveys (e.g. with the {\it Euclid}
+satellite).
 
 The CosmoSim database used in this paper is a service by the
-Leibniz-Institute for Astrophysics Potsdam (AIP). The  BolshoiP
+Leibniz-Institute for Astrophysics Potsdam (AIP). The  Bolshoi
 simulation was performed within the Bolshoi project of the University
@@
 was run at the NASA Ames Research Center.
+
+J.E.F-R acknowledges support from Vicerrector\'ia de
+Investigaciones through a FAPA starting grant.
+
+T.V. acknowledges support from CONACYT through grant 165365 and
+203489 through the program Estancias posdoctorales y sab\'aticas al
+extranjero para la consolidaci\'on de grupos de investigaci\'on.
+
+V.M. gratefully acknowledges FONDECYT support through grant 1120741
+and ECOS/CONICYT through grant C12U02.
 

### 2014-03-18 paper/ms.tex
removed relative velocity subsection

@@
 possibility for a new statistical test of  $\Lambda$CDM.
+
+NOTA: tomar $186\pm30$ para el DM-DM displacement.
+
 \end{abstract}
@@
 
-%In order to gain better insight, we use two
-%quantities that can be infered from the simulation. The first one is
-%the sub-structure velocity as a fraction of the host's circular
-%velocity, $||\vec{v}||/V_{\rm c, host}$, as a measure of the the
-%strength of the merger.  The second onw is $\mu$, which measures the geometry
-%(head-on vs. grazing) of each interaction.
-
 The physical quantities described above can be used to describe
@@
 data presented by \cite{Gastaldello}.
-
-%\subsection{Relative Velocities}
-%\label{sec:velocities}
-
-%\begin{figure*}
-%\begin{center}
-%\includegraphics[width=0.9\textwidth]{figure_3.eps}
-%\end{center}
-%\caption{Integrated probability distribution for the relative velocity of the
-%sub-halo with respect to its host. The left panel shows the results
-%in physical units while the right panel show the same values
-%normalized by the circular velocity of the host halo. The line encoding
-%follows the same structure as Figure \ref{fig:displacement}}
-%\label{fig:velocities}
-%\end{figure*}
 
@@
 from the SL2S sample. From the light distribution, only $34$ objects
-($\approx 42\%$) have regular isophotes, $33$ had ellongated
-isophotes (hints of merging system), and $13$ ($\approx 16\%$) had a
+($\sim 42\%$) have regular isophotes, $33$ had ellongated
+isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
 clear bi-modal light distribution.

### 2014-03-20 paper/ms.tex
removed velocity section
new darft with new figures
new numbers

@@
 featuring a bi-modal dark matter distribution with a dislocated 
-baryonic component. We extend previous results by
-studying two halo samples: groups and clusters. We find that $(55\pm 5)\%$
+baryonic component. We extend previous computational results by
+studying two halo samples: groups and clusters. We find that $(50 \pm 10)\%$
 of the dark matter halos with circular velocities in the range
@@
 displacements between the dark matter clumps equal or larger than
-$133\pm21$\hkpc as observed in \bullg. For dark matter halos with
+$186 \pm 30$\hkpc as observed in \bullg. For dark matter halos with
 circular velocities larger than $700\kms$ (clusters) this fraction
-rises to $(82\pm 3)\%$. Using the same simulation we estimate the
+rises to $(70 \pm 10)\%$. Using the same simulation we estimate the
 dark matter-to-baryon spatial separation and find that $0.1$ to
@@
 benchmark; for clusters this fraction rises to $(7\pm 3)\%$, consistent
-with previous studies of dark matter to baryon separations. The
-extension of the theoretical predictions and observational results
-towards low mass bi-modal dark matter configurations opens up the
-possibility for a new statistical test of  $\Lambda$CDM.
-
-NOTA: tomar $186\pm30$ para el DM-DM displacement.
-
+with previous studies of dark matter to baryon separations. In terms
+of absolute numbers densities we find that the expected value for
+bullet groups is tree times larger than the expected value for bullet
+groups. The extension of the theoretical predictions and observational
+results towards low mass bi-modal dark matter configurations opens up
+the possibility for a new statistical test of  $\Lambda$CDM.  
 \end{abstract}
@@
 are not inside a larger halo) with circular velocities $V_{\rm c}\geq
-300$\kms ($\geq 1\times 10^{13}\\hMsun$). Then, we select the sub-halos with
+300$\kms ($\geq 1\times 10^{13} \hMsun$). Then, we select the sub-halos with
 circular velocities $V_{\rm c}\geq 75$\kms ($\geq 5\times
@@
 
-For the redshifts $z=0.0,0.25, 0.5$ and $1.0$ we find $10041, 10346,
-10554$ and $10382$ host halos and $157853, 177331, 195072, 225188$
-sub-halos, respectively. These two sets (host halos and sub-halos)
+These two sets (host halos and sub-halos)
 constitute the basis for our analysis. We associate each host halo
@@
 is considered as a potential Bullet system and is kept for the
-analysis described in the next Section.
+analysis described in the next Section. The number of systems at each
+redshift is listed on the first arrow of Table \ref{table:numbers}.
 
@@
   cluster (group).
-  The vertical lines show the mean value and uncertainties ($133\pm
-  21$\hkpc) in the  separation between the two dark matter clumps
-  estimated in \citet{Gastaldello} for the \bullg. Between $50\%$
+  The vertical lines show the mean value and uncertainties ($186\pm
+  30$\hkpc) in the  separation between the two dark matter clumps
+  estimated in \citet{Gastaldello} for the \bullg. Between $40\%$
   to $60\%$ of the groups show a displacement equal or larger than
-  this observational benchmark.}
+  this observational benchmark. This fraction rises to $60\%$ and
+  $80\%$ in clusters.}
 \label{fig:displacement}
@@
 \cite{Gastaldello}. In the group sample we see that a fraction of
-$50\%$ to $60\%$  should present a displacement equal than the
+$40\%$ to $60\%$  should present a displacement equal than the
 estimate for \bullg; in the cluster sample this fraction increases to
-$80\%$-$85\%$. The uncertainties in this estimates are derived from
+$70\%$-$80\%$. The uncertainties in this estimates are derived from
 the uncertainties in the displacement measurement for \bullg.This
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_4.eps}
+\includegraphics[width=1.0\textwidth]{figure_3.eps}
 \end{center}
@@
 \end{figure*}
-
-%In Figure \ref{fig:velocities} we present the integrated probability
-%of the relative peculiar velocities of the sub-halos with respect to
-%the host halo. This velocity is presented in the left panel in
-%physical units and in the right panel as a fraction of the circular
-%velocity of the host halo.
-
-%The panel with the normalized velocities shows that the distribution
-%of sub-halo velocities is close to universal. Regardless of the mass
-%of the host halo and the redshift the integrated distributions lie
-%very close to each other.  The universality of this profile also holds
-%for the group mass range. extending the result found by
-%\citep{Hayashi2006} for cluster mass halos.
-
-%The median of this distribution is located at $v/V_{\rm
-%  c,host}=1.1$. We also note the strong break at $v/V_{\rm
-%  c,host}=3.0$ present in the data from the group sample, which
-%allows us to probe fractions on the order of $10^{-4}$.  This break is
-%located close the escape velocity of $v/V_{\rm c,host}$ for dark
-%matter halos following a NFW profile with a concentration value
-%$c\approx 6$ \citep{Hayashi2006}.
 
@@
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figure_5.eps}
+\includegraphics[width=0.5\textwidth]{figure_4.eps}
 \end{center}
@@
 Recently \citep{Foex2013} presented an analysis of $80$ galaxy groups
-from the SL2S sample. From the light distribution, only $34$ objects
+in the SL2S sample. From the light distribution, only $34$ objects
 ($\sim 42\%$) have regular isophotes, $33$ had ellongated
 isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
-clear bi-modal light distribution.
+clear bi-modal light distribution.  The system \bullg\ is one of these
+$13$ systems.
 
@@
 strong lensing system.  The lowest separation in those systems is
-$64$ \hkpc and the average is $145\pm 52$\hkpc. Comparing this average
-displacement against the integratied distribution for the group sample (left
-panel, Figure \ref{fig:displacement}) one would expects between $40\%$
-to $80\%$ of DM halos to present those displacements. This fraction is
-certainly larger than the $\approx 16\%$ inferred from the
+$64$ \hkpc and the average is $145\pm 52$\hkpc.
+
+We now make a comparison of these fractions against the results of our
+simulations. The results are summarized in Table
+\ref{table:numbers}. The first row indicate the total number of halos
+in each sample, at each redshift. The second row shows the number of
+objects with DM-DM displacement $46\hkpc< d_{\rm 2D}< 350$\hkpc. The
+last row indicates the number of objects in the previous sub-sample
+with a  $d_{\rm 2D}^{\rm bar}>87$\hkpc.
+
+Considering that the statistics for the cluster sample are dominated
+by objects in the mass range of the \bullg we make a comparison
+against this sample. The table shows that $\sim 40\%$ of the 
+clusters are expected to have large DM-DM displacements, this is a
+factor of $\sim 2$ larger than the observational estimate by
+\citep{Foex2013}. However, roughly $\sim 7\%$ of these systems present a
+displacement equal or larger than the observed in the \bullg, a
+fraction that is compatible with the $1/13\sim 0.07$ fraction in the
 observational sample.
-
-We have taken the results from the simulation and selected all the
-objects in the group sample with a DM-DM displacement less than
-$350$\hkpc but larger than $64$\hkpc to find XXX objects in
-total. From this subsample we find that XXX have a DM-baryon
-displacement larger than $87$\hkpc.
 
@@
 of multi-modal groups with a DM-baryon displacement in a $\Lambda$CDM
-cosmology. A proper comparison must take into account all the
-observational uncertainties and biases to derive a stronger prediction from the
-simulation, something that is beyond the scope of this Letter.
+cosmology and that our estimates for the relative number of bullet
+systems with respect to multi-modal systems is compatible with
+observations.
+
+A proper comparison must take into account all the observational
+uncertainties, biases, mixes between our two populations (groups \&
+clusters at different redshifts) to derive a stronger prediction from
+the simulation, something that is beyond the scope of this Letter.
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{ccccccccc}\hline\hline
+        & Groups & Groups & Groups & Groups & Clusters & Clusters & Clusters & Clusters\\
+  & $z=0$   & $z=0.25$   & $z=0.5$   & $z=1.0$   & $z=0$   & $z=0.25$   & $z=0.5$   & $z=1.0$ \\
+  & ($\# $)    & ($\# $)    & ($\# $)    & ($\# $)    & ($\# $)    & ($\# $)    & ($\# $)    & ($\# $)  \\\hline
+Full Sample & 9641 & 9984 & 10244 & 10190 & 400  & 363 & 310 & 192 \\
+$64 <d_{\rm 2D}/\hkpc< 350$ & 6188 & 6422 & 6635 & 6933 & 151 &
+141 & 120 & 99\\
+($64 <d_{\rm 2D}/\hkpc< 350 $) \& ($d_{\rm 2D}^{\rm bar}/\hkpc >87$) & 14 & 25 & 44 & 35 & 8 & 9 & 13 & 8 \\\hline\hline
+\end{tabular}
+\caption{Absolute number of objects in the groups and clusters sample
+  at all redshifts for different selection criteria. }
+\label{table:numbers}
+\end{center}
+\end{table*}
 
@@
 
-In this Letter we estimate fraction of galaxy groups and clusters that
+In this Letter we estimate the fraction of galaxy groups and clusters that
 can present observational features associated to a bullet-like
@@
 
-Our main results is that that a fraction of $50\%$-$60\%$ of the halos
+Our main results is that that a fraction of $40\%$-$60\%$ of the halos
 in the group sample present displacement equal or larger than the
 observed displacement for \bullg. For halos in the cluster sample this
-fraction increases to $80\%$-$85\%$. We also derive an
+fraction increases to $60\%$-$80\%$. We also derive an
 estimate for the displacement between the DM and the baryonic
@@
 
-We also find distributions for the DM separation and the velocity of
-the bullet through its host. If these quantities are normalized by the
-virial radius and the circular velocity, respectively, we arrive at
-distributions close to universal that are similar for the two halo
-samples at all redshifts.
-
 For the case of \bullg\ a fair comparison is achieved against cluster
 sample, which has statistics dominated by objects of similar mass. In
-this case we conclude that the existence of such configuration is
-highly probable in $\Lambda$CDM (4$\%$ to $10\%$ abundance). In turn,
-for the same separation the fraction for groups is lower (0.1$\%$ to
-$1\%$). Taking into account that the difference in spatial abundance
-between these two samples is on the order of a factor of $10$, one can
-conclude that the absolute number of groups and clusters presenting a
-DM-baryon displacement larger or equal to \bullg\ should be of the
-same order.
+a rough comparison using the selection criteria by \citep{Gael2013,
+  Gastaldello} we find that the relative number of bullet groups and
+systems with large DM-DM displacements is consistent with
+observations; both are in the range $\sim 7\%$. In terms of absolute
+numer densities, we expect $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ Bullet
+groups similar to \bullg; three times the expected value for Bullet
+clusters.
 
-An observational possibility opens up with surveys such as SL2S that
-targetted a large number of groups and estimate its multi-modal nature
-from lensing analysis \citep{Foex2013}, an approach that can be
-exploited with upcoming lensing surveys (e.g. with the {\it Euclid}
-satellite).
+We conclude that a new observational possibility opens up with surveys
+such as SL2S that targett a large number of groups and estimate its
+multi-modal nature from lensing analysis \citep{Foex2013}, an approach
+that can be exploited with upcoming lensing surveys (e.g. with the
+{\it Euclid} satellite).
 

### 2014-03-20 paper/ms.tex
abstract

@@
 }
-
+\email{jfernandezt87@gmail.com}
+\email{je.forero@uniandes.edu.co}
 \begin{abstract}
@@
 dominant dark matter density peaks and between baryons and dark matter
-in halos simulated within a full cosmological context. We use as a benchmark the
-observation of \bullg, which is the lowest mass system observed so far
+in halos simulated within a full cosmological context in $\Lambda$CDM.
+We use as a benchmark the observation of \bullg, which is the lowest mass system observed so far
 featuring a bi-modal dark matter distribution with a dislocated
-baryonic component. We extend previous computational results by
-studying two halo samples: groups and clusters. We find that $(50 \pm 10)\%$
-of the dark matter halos with circular velocities in the range
+baryonic component. We extend to lower masses previous computational results by
+studying two halo samples: groups and clusters. We find that $(50 \pm
+10)\%$ of the dark matter halos with circular velocities in the range
 $300\kms$ to $700\kms$ (groups) show multimodal morphologies with
@@
 with previous studies of dark matter to baryon separations. In terms
-of absolute numbers densities we find that the expected value for
-bullet groups is tree times larger than the expected value for bullet
-groups. The extension of the theoretical predictions and observational
-results towards low mass bi-modal dark matter configurations opens up
-the possibility for a new statistical test of  $\Lambda$CDM.  
+of absolute number densities we find that the expected value for
+groups similar to \bullg\ is tree times larger than the expected value
+for clusters. This extension of the theoretical predictions and
+observational results towards low mass bi-modal dark matter
+configurations opens up the possibility for a new statistical test of
+$\Lambda$CDM.   
 \end{abstract}
 
-\begin{keywords}
-{cosmology: theory -- dark matter} 
-\end{keywords}
+\keywords{dark matter, galaxies: clusters: individual (SL2S
+  J08544-0121), galaxies: interactions, methods: numerical}
 
@@
 evidence for the existence of dark matter
-\citep{Markevitch2004,Clowe2006}. Quantifying the displacement between
-dark matter and the dominant baryonic component (hot X-ray emitting gas)
-has been used to test the Cold Dark Matter (CDM)
-paradigm itself by quantifying the substructure velocity required to
-produce such displacement \citep{Hayashi2006, Springel2007,
-  Thompson2012}, the displacemeent between the dominant dark matter
-and baryonic component \citep{ForeroRomero2010} to estimate the
-expected abundance of such events in a $\Lambda$CDM Universe, putting
-constraints on the dark matter particle self-interaction cross section
-and even explore possible extensions to the concordance cosmological model
+\citep{Markevitch2004,Clowe2006}. Since then it has been used to test the Cold
+Dark Matter (CDM) paradigm itself by quantifying different aspects
+such as the expected displacement between the dominant dark matter and
+baryonic component in a $\Lambda$CDM Universe \citep{ForeroRomero2010}
+or the substructure velocity required to produce such displacement \citep{Hayashi2006, Springel2007,
+  Thompson2012}. It has also been used to constrain the dark matter
+particle self-interaction cross section and to explore possible
+extensions to the concordance cosmological model
 \citep{Farrar2007,Lee2010,Lee2012}.
@@
 by objects in the mass range of the \bullg we make a comparison
-against this sample. The table shows that $\sim 40\%$ of the 
+against this sample. Table \ref{table:numbers} shows that $\sim 40\%$ of the 
 clusters are expected to have large DM-DM displacements, this is a
@@
 
-This rough comparison hints that it is possible to find a large fraction
-of multi-modal groups with a DM-baryon displacement in a $\Lambda$CDM
-cosmology and that our estimates for the relative number of bullet
-systems with respect to multi-modal systems is compatible with
-observations.
-
-A proper comparison must take into account all the observational
+This rough comparison  that our estimates for the relative number of
+bullet systems with respect to multi-modal systems is compatible with
+observations. A proper comparison must take into account all the observational
 uncertainties, biases, mixes between our two populations (groups \&
@@
 the simulation, something that is beyond the scope of this Letter.
+
+Neverthless, comparing the group and cluster samples we expect to have
+a number density of bullets similar to \bullg that is three times
+larger for groups than for clusters.
 

### 2014-03-20 paper/ms.tex
conclusions

@@
 
-In this Letter we estimate the fraction of galaxy groups and clusters that
-can present observational features associated to a bullet-like
-event. This is motivated by the recent observational results of
-\citep{Gastaldello} where a system (\bullg) on the mass range $1\times
-10^{14}$\hMsun\ and velocity dispersion $650$\kms was reported to
-feature a displacement between its baryonic (hot gas) and dark matter
-components.
+In this Letter we estimate the fraction of galaxy groups and clusters
+in a $\Lambda$CDM cosmology that could present observational features
+associated to a bullet-like event. This is motivated by the recent
+observational results of \citep{Gastaldello} where a system (\bullg)
+on the mass range $1\times 10^{14}$\hMsun\ and velocity dispersion
+$650$\kms was reported to feature a displacement between its baryonic
+(hot gas) and dark matter components.
 
@@
 
-Our main results is that that a fraction of $40\%$-$60\%$ of the halos
-in the group sample present displacement equal or larger than the
+Our main result is that a fraction of $40\%$-$60\%$ of the halos
+in the group sample present DM-DM displacement equal or larger than the
 observed displacement for \bullg. For halos in the cluster sample this
 fraction increases to $60\%$-$80\%$. We also derive an
-estimate for the displacement between the DM and the baryonic
-component. In the group sample $0.1\%$-$1.0\%$ of the halos show a
-displacement equal or larger than  the  measurements of \bullg\ by
-\citep{Gastaldello}. In the cluster sample this fraction rises to
-$4\%$-$10\%$.
+estimate for the DM-baryon displacement In the group sample
+$0.1\%$-$1.0\%$ of the halos show a displacement equal or larger than
+the  measurements of \bullg\ by \citep{Gastaldello}; in the cluster
+sample this fraction rises to $4\%$-$10\%$.
 
-For the case of \bullg\ a fair comparison is achieved against cluster
-sample, which has statistics dominated by objects of similar mass. In
-a rough comparison using the selection criteria by \citep{Gael2013,
-  Gastaldello} we find that the relative number of bullet groups and
-systems with large DM-DM displacements is consistent with
-observations; both are in the range $\sim 7\%$. In terms of absolute
-numer densities, we expect $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ Bullet
-groups similar to \bullg; three times the expected value for Bullet
-clusters.
+For the case of \bullg\ a fair comparison is achieved against our cluster
+sample which has statistics dominated by objects of similar mass. In
+a rough comparison using the selection criteria in \citep{Foex2013,
+  Gastaldello} we find that the relative number of bullet groups
+(large DM-baryon displacement) with respect to a general sample of
+multi-modal systems (large DM-DM displacements) is consistent with
+observations; both are in the range $\sim 7\%$.
 
-We conclude that a new observational possibility opens up with surveys
-such as SL2S that targett a large number of groups and estimate its
-multi-modal nature from lensing analysis \citep{Foex2013}, an approach
-that can be exploited with upcoming lensing surveys (e.g. with the
-{\it Euclid} satellite).
+In terms of absolute numer densities, we expect to have $\sim 6.0\times
+10^{-7}$ Mpc$^{-3}$ groups similar to \bullg; three times the expected
+value for clusters. This opens up a new observational possibility with surveys
+such as SL2S that target a large number of groups and estimate its
+multi-modal nature from lensing analysis \citep{Foex2013}. An approach
+that can be further exploited with upcoming lensing surveys (e.g. with
+the {\it Euclid} satellite).
 

### 2014-03-20 paper/ms.tex
captions

@@
   Integrated probability distribution for the displacement between the
-  center of the host halo and its dominant sub-halo. The left panel
+  center of the host halo and its dominant sub-halo at all redshifts
+  $z=0$, $0.25$, $0.5$ and $1.0$. The left panel
   shows the results in terms of the physical displacements while the
@@
   of the host halo. The continuous (dashed) line corresponds to the halos in the
-  cluster (group).
+  cluster (group) sample.
   The vertical lines show the mean value and uncertainties ($186\pm
-  30$\hkpc) in the  separation between the two dark matter clumps
+  30\hkpc$) in the  separation between the two dark matter clumps
   estimated in \citet{Gastaldello} for the \bullg. Between $40\%$
@@
 
-We estimate the distribution of projected displacements
+We compute the distribution of projected displacements
 between the dominant DM clumps in two kinds of systems; groups with
@@
 sample which has statistics dominated by objects of similar mass. In
-a rough comparison using the selection criteria in \citep{Foex2013,
-  Gastaldello} we find that the relative number of bullet groups
+a rough comparison using the observational criteria \citep{Foex2013,
+  Gastaldello} we find that the relative number of bullets
 (large DM-baryon displacement) with respect to a general sample of

### 2014-03-20 paper/ms.tex
introduction

@@
 evidence for the existence of dark matter
-\citep{Markevitch2004,Clowe2006}. Since then it has been used to test the Cold
-Dark Matter (CDM) paradigm itself by quantifying different aspects
-such as the expected displacement between the dominant dark matter and
-baryonic component in a $\Lambda$CDM Universe \citep{ForeroRomero2010}
-or the substructure velocity required to produce such displacement \citep{Hayashi2006, Springel2007,
+\citep{Markevitch2004,Clowe2006}. Since then it has been used to test
+the Cold Dark Matter (CDM) paradigm itself by quantifying different
+aspects such as the expected displacement between the dominant dark
+matter and baryonic component in a $\Lambda$CDM Universe
+\citep{ForeroRomero2010} or the substructure velocity required to
+produce such displacement \citep{Hayashi2006, Springel2007,
   Thompson2012}. It has also been used to constrain the dark matter
@@
 DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
-\citep{Dahle2013}. Recently \citep{Gastaldello} observed a baryonic-DM
-displacement if $124\pm 20$ kpc in \bullg, a group-like system with a total
-mass $2.4\pm 0.6 \times 10^{14}$\Msun. Systems of this mass are
-$\sim10$ times more abundant than cluster systems in the mass range of
-the Bullet Cluster $>10^{15}$\hMsun, this opens up the possibility of
-observationally finding bullet groups in a fair amount to impose
-constraints on $\Lambda$CDM.
+\citep{Dahle2013}. Recently \citep{Gastaldello} observed a DM-baryon
+displacement of $87\pm 14$\hkpc and a DM-DM separation of $186\pm
+30$\hkpc in \bullg, a group-like system with a total
+mass $2.4\pm 0.6 \times 10^{14}$\Msun found in the the Strong Lensing
+Legacy Survey (SL2S) sample \citep{Cabanac2007,More2012}.
 
-However, a greater abundance of small mass systems has to be weighted
-by the probability of having a merger and 
-presenting a large displacement between the DM and baryonic
-components. These two conditions (merger rates, maximum possible
-displacement) are a funcion of DM halo mass in $\Lambda$CDM
-cosmologies.  Such study has been performed for clusters but not for
-lower mass systems \citep{ForeroRomero2010}. The existence of objects
-like \bullg\ and observational campaigns like the Strong Lensing Legacy
-Survey (SL2S) \citep{Cabanac2007,More2012} open up the possibility of finding
-multi-modal dark matter distributions in the group mass range.
+Groups around this mass are $\sim10$ times more abundant than clusters
+in the mass range of the Bullet Cluster $>10^{15}$\hMsun. This 
+should open up the possibility of finding Bullet Groups in large
+numbers to test $\Lambda$CDM. However, a larger abundance of small
+mass systems has to be weighted by the probability of being in a
+merger and  presenting a large displacement between the DM and
+baryonic components.  These two conditions (merger rates, maximum
+possible displacement) are a funcion of DM halo mass in $\Lambda$CDM
+cosmologies.  A detailed statistical study to estimate the abundance
+of Bullets has been performed for clusters but not for lower mass
+systems \citep{ForeroRomero2010}.
 
-In this Letter we compute the abundance of group-like dark
-matter halos with a multi-modal morphology that also might present a
-DM-baryon displacement. To this end we use a N-body cosmological
-simulation with such a resolution that allows us to identify
-multi-modal dark matter distributions in hosts with circular velocities
-larger than $300$\kms.
+In this Letter we extend such study for systems in the group mass
+scale. We measure the abundance of DM systems with with a multi-modal
+morphology (large DM-DM displacements) and estimate the amount of
+systems with a Bullet configuration  (large DM-baryon
+displacements). To this end we use a high resolution N-body
+cosmological simulation (Bolshoi) that allows us to find  multi-modal
+dark matter distributions in hosts with circular velocities larger
+than $300$\kms ($\sim 1.0\times 10^{13}\hMsun$).
 
@@
 used in this work. We continue in Section \ref{sec:setup} with the
-geometry of the problem at hand and the measurements setup. Next in
+geometry of the problem at hand and the measurement setup. Next in
 Section \ref{sec:results} we present our results and observational

### 2014-03-20 paper/ms.tex
geometry and measurement

@@
 code \citep{Kravtsov1997} to follow the evolution of a dark matter
-density field sampled with $2048^3$ from $z=80$ to $z=0$. The
+density field from $z=80$ to $z=0$ sampled with $2048^3$  particles. The
 cosmology used  corresponds to  the spatially flat concordance model
@@
 Microwave Anisotropy Probe (WMAP) results \citep{hinshaw_etal13}. A
-detailed presentation of the simulation can be found in
-\citet{2011ApJ...740..102K}.
+detailed presentation of the simulation can be found in \citet{2011ApJ...740..102K}.
 
-The number of particles used for each of the DM component was
-$2048^3$, resulting in a mass resolution of $1.35 \times 10^8$
-M$_{\odot}$h$^{-1}$. The completeness limit in this simulation is set
-for halos with $100$ particles corresponding to a mass of
-$1.35\times10^{10}$\hMsun\ or a maximum circular velocity $V_{c}$ of
-$50$\kms.
+This results in a mass resolution of $1.35 \times 10^8$
+M$_{\odot}$h$^{-1}$ for each computational particle. The completeness
+limit in this simulation is set for halos with $100$ particles
+corresponding to a mass of $1.35\times10^{10}$\hMsun\ or a maximum
+circular velocity $V_{c}$ of $50$\kms.
 
-We use halo catalogs constructed using the Bound Density Maxima (BDM)
+We use DM halo catalogs constructed using the Bound Density Maxima (BDM)
 algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
-density threshold of 360 times the mean density of the Universe (or
+density threshold of 360 times the mean density of the Universe (
 200 times the critical density), for different redshifts we use the
@@
 
-All the raw data used in this Letter is available through the
-Multidark database \footnote{\texttt{www.multidark.org}}
+All the raw data used in this Letter is available through the Multidark database \footnote{\texttt{www.multidark.org}}
 \citep{Riebe2013}.  Furthermore, in order to facilitate the
@@
 
-In this Letter we make a study at four different redshifts $z=0.0,0.25,
-0.5$ and $1.0$. First, we select all the host halos (i.e. halos that
-are not inside a larger halo) with circular velocities $V_{\rm c}\geq
-300$\kms ($\geq 1\times 10^{13} \hMsun$). Then, we select the sub-halos with
+To construct our main halo sample we follow three
+steps. Firstly, we select all the host halos (i.e. halos that are not
+inside a larger halo) with circular velocities $V_{\rm c}\geq 300$\kms
+($\geq 1\times 10^{13} \hMsun$). Secondly, we select the sub-halos with
 circular velocities $V_{\rm c}\geq 75$\kms ($\geq 5\times
-10^{10}\hMsun$). The objective is to use this sub-halos as the tracer
-of the sub-dominant dark matter clump in the merging cluster, i.e. the
-bullets.
+10^{10}\hMsun$). Thirdly, we associate each host halo to its most
+massive sub-halo.
 
-These two sets (host halos and sub-halos)
-constitute the basis for our analysis. We associate each host halo
-to its most massive sub-halo, each one of these pairs (host \& sub-halo)
-is considered as a potential Bullet system and is kept for the
-analysis described in the next Section. The number of systems at each
-redshift is listed on the first arrow of Table \ref{table:numbers}.
+Each one of the pairs (host \& sub-halo) is considered as a
+potential Bullet system and is kept for the analysis described in the
+next Section. We use the sub-halos as the tracer of the sub-dominant
+dark matter clump in the merging cluster, i.e. the bullets.
+
+Finally, we split the sample into two  populations; groups with
+$300\kms < V_{\rm c, host}<700\kms$ and clusters with $V_{\rm
+  c,host}>700\kms$. These two samples are constructed at four redshifts:
+$z=0.0, 0.25, 0.5$ and $1.0$.  The number of pairs at each redshift in
+each population is listed on the first arrow of Table
+\ref{table:numbers}.
+
+\ref{table:numbers}.
 
@@
 
-The Bullet-like configurations are composed by two dark matter
-structures: the host halo and the dominant sub-halo. We describe the
-kinematics of this configuration by the 
+Bullet-like configurations have two dominand dark matter structures:
+the host halo and the dominant sub-halo. We describe the kinematics of this configuration by the 
 position and velocity vectors of the sub-halo in a frame of reference
 where the main halo is at rest; thus
-$\vec{v{}}=\vec{v}_{sub}-\vec{v}_{halo}$ and
-$\vec{r}=\vec{r}_{sub}-\vec{r}_{halo}$, where the subscripts $host$
+$\vec{v{}}=\vec{v}_{\rm sub}-\vec{v}_{\rm host}$ and
+$\vec{r{}}=\vec{r}_{\rm sub}-\vec{r}_{\rm host}$, where the subscripts $host$
 and $sub$ refer to the position of the minium of potential for the
-host and sub-halo in the frame of reference of the simulation,
-respectively.
+host and sub-halo in the frame of reference of the simulation, respectively.
 
-The angle between these two vectors can be characterized by, 
+The angle between these two vectors can be quantified by, 
 \begin{equation}
@@
 %
-This encodes relevant information to describe the collision,
-i.e. cases of $|\mu|\approx 1$ can be considered as head-on collisions
-while $|\mu|\approx 0$ describes a grazing trajectory.
+This encondes information about the collision, i.e. cases of
+$|\mu|\approx 1$ can be considered as head-on collisions while
+$|\mu|\approx 0$ describes a grazing trajectory.
 
@@
 size of the host halo $R_{\rm vir}$. Another useful quantity computed
-in the simulation is the distance between the minium of potential for
-the host halo and its center of mass, $X_{\rm
-  off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$ which serves as a
+in the simulation is the distance between the minimum of potential for
+the host halo and its center of mass (computed from all the particles
+inside the $R_{\rm vir}$), $X_{\rm off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$, which serves as a
 measurement of how much the host halo is perturbed.
 
-As a zero-th order approximation, in this paper we work with three
-observed quantities for Bullet-like systems. The projected distance
-between two dominant DM clumps, the projected distance between the
-DM-baryonic clumps and the ratio of the mass associated to the DM
-clumps.
+In this letter we work with three quantities that could be inferred
+from observations of Bullet-like systems. The projected distance
+between two dominant DM clumps, $d_{\rm 2D}$; the projected distance
+between the DM-baryonic clumps, $d_{\rm 2D}^{\rm bar}$; and the mass
+ration associated to the two dominant DM clumps.
 
@@
 relative to the virial radius $D_{\rm   off}= ||\vec{r}||_{\rm
-  2D}/R_{\rm vir}$. The last quantity, the mass ratio, can be
-approximated by ratio of the circular velocities of the two clumps $V_{\rm c,sub}/V_{\rm  c,host}$ which should be equal to the square root of the mass
-ratio. The second quantity, the projected DM-baryon distance, is not
-directly available from a DM-only simulation but, as we show in the
-Results section, can be inferred from the available information.
+  2D}/R_{\rm vir}$. The second quantity, the projected DM-baryon
+distance, is not directly available from a DM-only simulation but can
+be estimated from the data.  The last quantity, the mass ratio, can be
+approximated by ratio of the circular velocities of the two clumps
+$V_{\rm c,sub}/V_{\rm  c,host}$ which should be equal to the square
+root of the mass ratio.
 
-The physical quantities described above can be used to describe
-the three main stages in a bullet-like encounter. First, the sub-halo
-crosses the virial radius of the host halo starting a head on
-collision, $||\vec{r}||/R_{\rm vir}\approx 1$ and
-$\mu\lessapprox<0.0$. Second, as the sub-halo crosses for the first time
-the center of the host halo $||\vec{r}||/R_{\rm vir} < 1.0$ and
-$\mu>0.0$. Third, as the sub-halo reaches apogee and comes back to the
-center of the halo $||\vec{r}||/R_{\rm vir} < 1.0$ and $\mu<0.0$. We use
-these quantities in the next section to fully characterize the different
-kind of interactions observed in the Bolshoi Run,
+We also use the physical quantities described above to discriminate
+between grazing trajectories, $|\mu|<0.9$, and Bullet-like collissions
+with $|\mu|\approx 1$. In the latter case we can also distinguish three
+main stages in a such encounter. First, when the sub-halo crosses the
+virial radius of the host halo starting a head on collision, $D_{\rm
+  off} \approx 1$ and $\mu\approx -1$. Second, as the sub-halo crosses
+for the first time the center of the host halo $D_{\rm off}<1.0$ and
+$\mu\approx 1$. Third, as the sub-halo reaches apogee and comes back
+to the center of the halo $D_{\rm off} < 1.0$ and $\mu< -1$.
 
@@
 Figure \ref{fig:displacement} shows the results for two different
-populations; groups with $300\kms < V_{\rm c, host}<700\kms$ and
-clusters with $V_{\rm c,host}>700\kms$. Additionally, this is
-presented for all redshifts $z=0.0, 0.25, 0.5$ and $1.0$.
-
-The panel with the projected 2D physical displacements also shows a
+populations at all redshifts. The panel with the projected 2D physical displacements also shows a
 vertical stripe with the estimated displacement for the Bullet-group reported by

### 2014-03-20 paper/ms.tex
new version

@@
 of absolute number densities we find that the expected value for
-groups similar to \bullg\ is tree times larger than the expected value
+groups similar to \bullg\ is three times larger than the expected value
 for clusters. This extension of the theoretical predictions and
@@
 
-In this letter we work with three quantities that could be inferred
+In this letter we work with two quantities that could be inferred
 from observations of Bullet-like systems. The projected distance
-between two dominant DM clumps, $d_{\rm 2D}$; the projected distance
-between the DM-baryonic clumps, $d_{\rm 2D}^{\rm bar}$; and the mass
-ration associated to the two dominant DM clumps.
+between two dominant DM clumps, $d_{\rm 2D}$ and the projected distance
+between the DM-baryonic clumps, $d_{\rm 2D}^{\rm bar}$.
 
@@
 distance, is not directly available from a DM-only simulation but can
-be estimated from the data.  The last quantity, the mass ratio, can be
-approximated by ratio of the circular velocities of the two clumps
-$V_{\rm c,sub}/V_{\rm  c,host}$ which should be equal to the square
-root of the mass ratio.
+be estimated from the data.
 
@@
 
-\subsection{Displacements and Relative Circular Velocities}
+\subsection{DM-DM Displacements}
 \label{fig:displacement}
@@
 
+Figure \ref{fig:displacement} presents the integrated
+probability distribution for the DM-DM displacements, $d_{\rm 2D}$ The
+left panel shows the displacement in physical units and the right
+panel as a fraction of the virial radius of the host halo.  The panel
+with the projected 2D physical displacements also shows a vertical
+stripe with the estimated displacement for the Bullet-group reported
+by \cite{Gastaldello}.
+
+In the group sample we see that a fraction of
+$40\%$ to $60\%$  should present a displacement equal than the
+estimate for \bullg; in the cluster sample this fraction increases to
+$70\%$-$80\%$. The uncertainties in this estimates are derived from
+the uncertainties in the displacement measurement for \bullg. This
+fraction is naturally higher in more massive systems because they are
+larger in size. Normalizing the displacements by the virial radius,
+right panel Figure \ref{fig:displacement}, we see that the
+distributions are similar for the two samples at all redshifts.
+
+\subsection{Collision Geometries}
+\label{sec:geometry}
+
 \begin{figure*}
@@
 \includegraphics[width=1.0\textwidth]{figure_2.eps}
-\end{center}
-\caption{2D histogram in the plane $V_{\rm c,sub}/V_{\rm
-    c,host}$-$d_{2D}$. The left panel corresponds to clusters and the
-  right panel to groups. The star with error bars corresponds to
-  \bullg\ data reported from \citet{2013A&A...552A..80M} and
-  \citet{Gastaldello}. The data used to construct the histograms
-  integrates the objects at all redshifts. }
-\label{fig:mass_displacement}
-\end{figure*}
-
-The main result of this paper is summarized in Figure
-\ref{fig:displacement}, it presents the integrated
-probability distribution for the displacement between the center of
-the host halo and its dominant sub-halo. The left panel shows
-the displacement in physical units and the right panel as a fraction
-of the virial radius of the host halo.
-
-Figure \ref{fig:displacement} shows the results for two different
-populations at all redshifts. The panel with the projected 2D physical displacements also shows a
-vertical stripe with the estimated displacement for the Bullet-group reported by
-\cite{Gastaldello}. In the group sample we see that a fraction of
-$40\%$ to $60\%$  should present a displacement equal than the
-estimate for \bullg; in the cluster sample this fraction increases to
-$70\%$-$80\%$. The uncertainties in this estimates are derived from
-the uncertainties in the displacement measurement for \bullg.This
-fraction is naturally higher in more massive systems because they are
-larger in size. Normalizing the displacements by the virial radius,
-right panel Figure \ref{fig:displacement}, we see that the
-distribution is the same regardless of the sample and the redshift.
-
-Figure \ref{fig:mass_displacement} shows 2D histograms in a plane
-defined by the ratio of the two circular velocities $V_{\rm c,
-  sub}/V_{\rm c, host}$ and the projected 2D physical displacements;
-quantities that can be constrained by observations.
-
-To construct this figure we co-add all the halos in the sample (left,
-clusters; right, groups) at all redshifts. We stack the data because
-we do not observe any strong redshift dependence. This allows
-us to increase the signal in each bin. We overplot a star with error
-bars that represents the observational constraints for the system
-\bullg\ using the fraction in velocity dispersion in the line-of-sigth
-of the group SL2S SJ08544-0121 ($\sigma_{host}=341^{+43}_{-109}$\kms and
-$\sigma_{sub}=185^{+30}_{-62}$\kms) reported by
-\citet{2013A&A...552A..80M} and the DM displacement inferred from the
-data presented by \cite{Gastaldello}.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{figure_3.eps}
 \end{center}
@@
 
-\subsection{Collision Geometries}
-\label{sec:geometry}
+Figure \ref{fig:geometry} presents the geometry of the intereactions using the 
+variables $\mu$ and $D_{\rm off}$. The first evident feature is that
+most of the configurations have head-on encouters, $|\mu|>0.9$
+($\theta\leq 30^{\circ}$), while only a minority with $|\mu|<0.9$ can
+be described as having  grazing trajectories.
 
-Figure \ref{fig:geometry} presents the geometry of the bullet groups using the 
-variables $\mu$ and $D_{\rm off}$. The first evident feature is that
-most of the configurations have $|\mu|>0.9$ ($\theta\leq 30^{\circ}$),
-meaning that most of the collisions can be described as a head-on
-encounter while only a minority with $|\mu|<0.9$ have grazing
-trajectories. For the pairs on radial trajectories there are three
-regions of interest in this plane that describe different stages in
-the collision, assuming that the sub-halo merges (or falls below the
-BDM detection threshold) right at its second pass through the center
-of the host halo \citep{Poole2006}.
+For pairs on radial trajectories there are three regions of interest
+in this plane that correspond to the three merging stages described
+at the end of Section \ref{sec:geometry} assuming that the sub-halo
+merges (or falls below the BDM detection threshold) right at its
+second pass through the center of the host halo \citep{Poole2006}.
 
@@
 locates the systems where a head-on collision has just started. The
-sub-halo is close to the boundary of the host halo and is
-infalling. The second region has $\mu\approx 1$ and $D_{\rm off}<0.6$;
-at this stage the collision continues after the first crossing of the
-host's center, the low number of halos with radial infalling velocities
-and displacements $D_{\rm off}>0.6$ suggest that this the maximum
-range of radii for the apogee.  The third region corresponds to
-$\mu\approx-1$ and $D_{\rm off}<0.6$ that is the the
-secondary infall after apogee. We use this sequence in the next
-subsection to estimate the expected displacement between baryons and
-the dominant DM clump.
+second region has $\mu\approx 1$ and $D_{\rm off}<0.6$; at this stage
+the collision continues after the first crossing of the host's center,
+the low number of halos with radial infalling velocities and
+displacements $D_{\rm off}>0.6$ suggest that this the maximum range of
+radii for the apogee.  The third region corresponds to $\mu\approx-1$
+and $D_{\rm off}<0.6$ that is the the secondary infall after apogee.
 
-\subsection{Displacement between Dark Matter and Baryons}
+In the next subsection we use the information in this sequence to
+estimate the expected DM-baryon displacement.
+
+\subsection{DM-baryon Displacement}
 \label{sec:baryonic_displacements}
 
-Strictly speaking, the results we have derived so far apply to multi-modal
-groups and their expected separation between the two dominant dark
-matter clumps. However, a non-zero DM-DM displacement cannot be
-interpreted as having a corresponding non-zero DM-baryon
-displacement. Given that we use a DM only simulation, we have to find
-a way to estimate DM-baryon displacements from the available information.
+The results we have derived so far apply to multi-modal systems and
+the expected separation between the two dominant dark matter
+clumps. However, a non-zero DM-DM displacement does not imply 
+a non-zero DM-baryon displacement. Given that we use a DM only
+simulation, we have to find a way to estimate a DM-baryon displacement
+from the available information.
 
-This estimate is based on the different collision stages described at
-the end of the previous sub-section.  For instance, in systems where
-the halo is starting to fall into the host ($\mu\approx-1$, $D_{\rm
-  off}>0.6$) the DM-baryon displacement should be equal to
-zero. However, when the  sub-structure has already passed through the
-center of the host halo, i.e. cases where $\mu\approx 1$, the
-DM-baryon displacement should be different from zero.
-
-To estimate the DM-baryon displacement we  work under the following
-hypothesis. First, we consider that systems with $|\mu|<0.9$ have a
-baryonic displacement, $d_{2D}^{\rm bar}$, equal to zero. This means
-that only head-on encounters produce a displacement. Second, we
-consider that all systems with infalling velocities $\mu<-0.9$ and
-large displacements $D_{\rm off}>0.6$ also have baryonic displacements
-equal to zero. Third, for all the other cases we estimate the
-displacement between the baryons and the dominant DM peak by
-$d_{2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$
-is the offset computed between the minium of potential and the center
-of mass for each host halo computed from all the matter inside the
-virial radius.
+This estimate is based on the different kinds of trajectories and
+collision stages described in previous sections. To start with, we
+consider that systems with $|\mu|<0.9$, describing grazing
+trajectories, have a baryonic displacement equal to zero.  In systems
+with head-on collissions, $|\mu|>0.9$, we distinguish two different
+cases. The first one, systems with  $\mu<-0.9$ and large displacements $D_{\rm
+  off}>0.6$ most probably describe the beginning of the interaction
+and should have baryonic displacements equal to zero.
+equal to zero. In all the other cases, the DM-baryon displacement
+should be equal to zero. We approximate this displacement by  $d_{\rm
+  2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
+the offset computed between the minium of potential and the center of
+mass for each host halo computed from all the matter inside the virial
+radius.
 
@@
 Letter. Instead we caution the reader that the derived fraction of
-halos with a displacement $<d_{2D}^{\rm bar}$ can be considered as an
+halos with a displacement $<d_{2D}^{\rm bar}$ must be considered as an
 upper limit.
 
-The results for the integrated distributions for $>d_{2D}^{\rm bar}$
+The results for the integrated distributions for $>d_{\rm 2D}^{\rm bar}$
 are shown in Figure \ref{fig:baryonic_displacements}. The dashed lines
@@
 clusters more massive than $>10^{14}$\hMsun\ in a simulation
-which included a description for DM and gas with $8$ times the volume of the
-Bolshoi Simulation. The fit is valid for separations larger than
-$70$\hkpc, beyond which we find that it provides a remarkably good
-description within a factor of $\sim 2$ of our results. This gives us
-confidence in our approach to estimate the expected fraction of
-groups with a DM-baryon displacement.
+which included a description for DM and gas with $8$ times more volume
+and $8$ times less mass resolution than the Bolshoi Simulation. The
+fit is valid for separations larger than $70$\hkpc, beyond which we
+find that it provides a remarkably good description within a factor of
+$\sim 2$ of our results. This gives us confidence in our approach to
+estimate the expected fraction of groups with a DM-baryon
+displacement.
 
-From Figure \ref{fig:baryonic_displacements} we see that only a
+Finally, from Figure \ref{fig:baryonic_displacements} we see that only a
 fraction of $0.1\%$ to $1\%$ of the groups are expected to have a
@@
 
-\begin{figure}
+\subsection{Towards a Statistical Comparison Against Observations}
+
+Recently \cite{Foex2013} presented an analysis of $80$ galaxy groups
+in the SL2S sample. From the light distribution, only $34$ objects
+($\sim 42\%$) have regular isophotes, $33$ had ellongated
+isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
+clear bi-modal light distribution; \bullg\ is one of these
+$13$ systems.
+
+The bi-modal objects are defined to have at least a clear second
+luminosity peak within $350$\hkpc from the main halo, as traced by the
+strong lensing system.  The lowest separation in those systems is
+$64$ \hkpc and the average is $145\pm 52$\hkpc.
+
+We now make a comparison of these fractions against the results of our
+simulations. The results are summarized in Table
+\ref{table:numbers}. The first row indicates the total number of halos
+in each sample at each redshift. The second row shows the number of
+objects with DM-DM displacements $46\hkpc< d_{\rm 2D}< 350$\hkpc. The
+last row indicates the number of objects in the previous sub-sample
+with DM-baryon displacements $d_{\rm 2D}^{\rm bar}>87$\hkpc.
+
+Considering that the statistics for the cluster sample are dominated
+by objects in the mass range of the \bullg we make a comparison
+against this sample. Table \ref{table:numbers} shows that $\sim 40\%$ of the 
+clusters are expected to have large DM-DM displacements, this is a
+factor of $\sim 2$ larger than the observational estimate by
+\cite{Foex2013}. However, roughly $\sim 7\%$ of these systems present a
+displacement equal or larger than the observed in the \bullg, a
+fraction that is compatible with the $1/13\sim 0.07$ fraction in the
+SL2S sample from which \bullg\ was drawn.
+
+This rough comparison  shows that our estimates for the relative number of
+bullet systems (large DM-baryon displacements) with respect to
+multi-modal systems (large DM-DM displacements) is compatible with
+observations. A proper comparison must take into account all the observational
+uncertainties, biases, mixes between our two populations (groups \&
+clusters at different redshifts) to derive a stronger bound from
+the simulation, something that is beyond the scope of this Letter.
+
+Neverthless, comparing the number for group and cluster samples in the
+last row of Table \ref{table:numbers} we can already predict that a
+fixed redshift the number density of bullets similar to \bullg that
+three times larger for groups than for clusters.
+
+\begin{figure*}
 \begin{center}
-\includegraphics[width=0.5\textwidth]{figure_4.eps}
+\includegraphics[width=0.9\textwidth]{figure_3.eps}
 \end{center}
@@
 \label{fig:baryonic_displacements}
-\end{figure}
-
-\subsection{Possible Observational Statistical Tests}
-
-Recently \citep{Foex2013} presented an analysis of $80$ galaxy groups
-in the SL2S sample. From the light distribution, only $34$ objects
-($\sim 42\%$) have regular isophotes, $33$ had ellongated
-isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
-clear bi-modal light distribution.  The system \bullg\ is one of these
-$13$ systems.
-
-The bi-modal objects are defined to have at least a clear second
-luminosity peak within $350$\hkpc from the main halo, as traced by the
-strong lensing system.  The lowest separation in those systems is
-$64$ \hkpc and the average is $145\pm 52$\hkpc.
-
-We now make a comparison of these fractions against the results of our
-simulations. The results are summarized in Table
-\ref{table:numbers}. The first row indicate the total number of halos
-in each sample, at each redshift. The second row shows the number of
-objects with DM-DM displacement $46\hkpc< d_{\rm 2D}< 350$\hkpc. The
-last row indicates the number of objects in the previous sub-sample
-with a  $d_{\rm 2D}^{\rm bar}>87$\hkpc.
-
-Considering that the statistics for the cluster sample are dominated
-by objects in the mass range of the \bullg we make a comparison
-against this sample. Table \ref{table:numbers} shows that $\sim 40\%$ of the 
-clusters are expected to have large DM-DM displacements, this is a
-factor of $\sim 2$ larger than the observational estimate by
-\citep{Foex2013}. However, roughly $\sim 7\%$ of these systems present a
-displacement equal or larger than the observed in the \bullg, a
-fraction that is compatible with the $1/13\sim 0.07$ fraction in the
-observational sample.
-
-This rough comparison  that our estimates for the relative number of
-bullet systems with respect to multi-modal systems is compatible with
-observations. A proper comparison must take into account all the observational
-uncertainties, biases, mixes between our two populations (groups \&
-clusters at different redshifts) to derive a stronger prediction from
-the simulation, something that is beyond the scope of this Letter.
-
-Neverthless, comparing the group and cluster samples we expect to have
-a number density of bullets similar to \bullg that is three times
-larger for groups than for clusters.
+\end{figure*}
 

### 2014-03-20 paper/ms.tex
keywords
goes for a second round of comments

@@
 \submitted{{\it Submitted for publication in ApJL}}
-\usepackage{multirow,color,wrapfig,ulem}
 \usepackage {graphicx}
@@
 We estimate the expected distribution of displacements between the two
-dominant dark matter density peaks and between baryons and dark matter
-in halos simulated within a full cosmological context in $\Lambda$CDM.
-We use as a benchmark the observation of \bullg, which is the lowest mass system observed so far
+dominant dark matter (DM) density peaks (DM-DM displacements) and between
+gaseous baryons and dark matter (DM-baryon displacements) in DM halos 
+with masses larger than $10^{13}$\hMsun. We use as a benchmark the
+observation of \bullg, which is the lowest mass system ($1.0\times
+10^{14}$\hMsun) observed so far
 featuring a bi-modal dark matter distribution with a dislocated
-baryonic component. We extend to lower masses previous computational results by
-studying two halo samples: groups and clusters. We find that $(50 \pm
-10)\%$ of the dark matter halos with circular velocities in the range
-$300\kms$ to $700\kms$ (groups) show multimodal morphologies with
-displacements between the dark matter clumps equal or larger than
-$186 \pm 30$\hkpc as observed in \bullg. For dark matter halos with
-circular velocities larger than $700\kms$ (clusters) this fraction
-rises to $(70 \pm 10)\%$. Using the same simulation we estimate the
-dark matter-to-baryon spatial separation and find that $0.1$ to
-$1.0\%$ of the groups should present separations equal or
-larger than $87\pm 14$\hkpc corresponding to our observational
-benchmark; for clusters this fraction rises to $(7\pm 3)\%$, consistent
-with previous studies of dark matter to baryon separations. In terms
-of absolute number densities we find that the expected value for
-groups similar to \bullg\ is three times larger than the expected value
-for clusters. This extension of the theoretical predictions and
-observational results towards low mass bi-modal dark matter
-configurations opens up the possibility for a new statistical test of
-$\Lambda$CDM.   
+baryonic component. We find that $(50 \pm 10)\%$ of the dark matter
+halos with circular velocities in the range $300\kms$ to $700\kms$
+(groups) show DM-DM displacements equal or larger than $186 \pm
+30$\hkpc as observed in \bullg. For dark matter halos with circular
+velocities larger than $700\kms$ (clusters) this fraction rises to
+$(70 \pm 10)\%$. Using the same simulation we estimate the DM-baryon
+displacements and find that $0.1$ to $1.0\%$ of the groups should
+present separations equal or larger than $87\pm 14$\hkpc corresponding
+to our observational benchmark; for clusters this fraction rises to
+$(7\pm 3)\%$, consistent with previous studies of dark matter to
+baryon separations. Considering both constraints on the DM-DM and
+DM-baryon displacements we find that the number density of groups
+similar to \bullg\ is $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times
+larger than the estimated value forclusters. These results open up
+the possibility for a new statistical test of $\Lambda$CDM.     
 \end{abstract}
 
-\keywords{dark matter, galaxies: clusters: individual (SL2S
-  J08544-0121), galaxies: interactions, methods: numerical}
+\keywords{dark matter --- galaxies: clusters: individual (SL2S
+  J08544-0121) --- galaxies: interactions --- methods: numerical}
 
@@
 possible displacement) are a funcion of DM halo mass in $\Lambda$CDM
-cosmologies.  A detailed statistical study to estimate the abundance
-of Bullets has been performed for clusters but not for lower mass
-systems \citep{ForeroRomero2010}.
+cosmologies.  A detailed statistical study to estimate the DM-gas
+displacements of Bullets has been performed for clusters
+\citep{ForeroRomero2010} but not for lower mass systems.
 
@@
 This encondes information about the collision, i.e. cases of
-$|\mu|\approx 1$ can be considered as head-on collisions while
-$|\mu|\approx 0$ describes a grazing trajectory.
+$|\mu|\sim 1$ can be considered as head-on collisions while
+$|\mu|< 0.9$ describes a grazing trajectory.
 
@@
 We also use the physical quantities described above to discriminate
-between grazing trajectories, $|\mu|<0.9$, and Bullet-like collissions
-with $|\mu|\approx 1$. In the latter case we can also distinguish three
-main stages in a such encounter. First, when the sub-halo crosses the
-virial radius of the host halo starting a head on collision, $D_{\rm
-  off} \approx 1$ and $\mu\approx -1$. Second, as the sub-halo crosses
-for the first time the center of the host halo $D_{\rm off}<1.0$ and
-$\mu\approx 1$. Third, as the sub-halo reaches apogee and comes back
-to the center of the halo $D_{\rm off} < 1.0$ and $\mu< -1$.
+three main stages in a Bullet-like encounter with $|\mu|\sim
+1$. First, when the sub-halo crosses the virial radius of the host
+halo starting a head on collision, $D_{\rm   off} \sim 1$ and $\mu\sim
+-1$. Second, as the sub-halo crosses for the first time the center of
+the host halo $D_{\rm off}<1.0$ and $\mu\sim 1$. Third, as the
+sub-halo reaches apogee and comes back to the center of the halo
+$D_{\rm off} < 1.0$ and $\mu\sim -1$.
 
@@
 Figure \ref{fig:displacement} presents the integrated
-probability distribution for the DM-DM displacements, $d_{\rm 2D}$ The
+probability distribution for the DM-DM displacements, $d_{\rm 2D}$. The
 left panel shows the displacement in physical units and the right
@@
 
-\subsection{DM-baryon Displacement}
+\subsection{DM-baryon Displacements}
 \label{sec:baryonic_displacements}
@@
 $\sim 2$ of our results. This gives us confidence in our approach to
-estimate the expected fraction of groups with a DM-baryon
+correctly estimate the expected fraction of groups with a DM-baryon
 displacement.

### 2014-03-20 paper/ms.tex
goes for a second round of comments

@@
 last row of Table \ref{table:numbers} we can already predict that a
-fixed redshift the number density of bullets similar to \bullg that
-three times larger for groups than for clusters.
+fixed redshift the number density of halos in the groups sample similar to \bullg is
+$\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times larger than the
+estimate for halos in the group sample.
 

### 2014-03-20 paper/ms.tex
minor fix

@@
 We estimate the expected distribution of displacements between the two
-dominant dark matter (DM) density peaks (DM-DM displacements) and between
-gaseous baryons and dark matter (DM-baryon displacements) in DM halos 
+dominant dark matter (DM) peaks (DM-DM displacements) and between
+DM and gaseous baryon peak (DM-baryon displacements) in DM halos 
 with masses larger than $10^{13}$\hMsun. We use as a benchmark the
@@
 and should have baryonic displacements equal to zero.
-equal to zero. In all the other cases, the DM-baryon displacement
+In all the other cases, the DM-baryon displacement
 should be equal to zero. We approximate this displacement by  $d_{\rm

### 2014-03-25 paper/ms.tex
overdensity criterion

@@
 algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
-density threshold of 360 times the mean density of the Universe (
-200 times the critical density), for different redshifts we use the
-overdensity criterion by \cite{Bryan1998}. An important feature of BDM
-is that it allows us to detect sub-halos inside larger virialized
+density threshold of 360 times the mean density of the Universe. An important feature of BDM is that it allows us to detect sub-halos inside larger virialized
 structures.
@@
 each population is listed on the first arrow of Table
-\ref{table:numbers}.
-
 \ref{table:numbers}.

### 2014-03-29 paper/ms.tex
comentarios Tomas

@@
 \author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
-  T. Verdugo$^3$, G. Foex$^4$ and V. Motta$^4$} 
+  G.Foex$^4$, T. Verdugo$^3$ and V. Motta$^4$} 
 \affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
@@
 30$\hkpc in \bullg, a group-like system with a total
-mass $2.4\pm 0.6 \times 10^{14}$\Msun found in the the Strong Lensing
+mass $2.4\pm 0.6 \times 10^{14}\Msun$ found in the the Strong Lensing
 Legacy Survey (SL2S) sample \citep{Cabanac2007,More2012}.
@@
 In this Letter we extend such study for systems in the group mass
-scale. We measure the abundance of DM systems with with a multi-modal
+scale. We measure the abundance of DM systems with a multi-modal
 morphology (large DM-DM displacements) and estimate the amount of
@@
 algorithm \citep{BDM,BDMb}. To define the radius of a halo we use a
-density threshold of 360 times the mean density of the Universe. An important feature of BDM is that it allows us to detect sub-halos inside larger virialized
-structures.
+density threshold of 360 times the mean density of the Universe. An
+important feature of BDM is that it allows us to detect sub-halos
+inside larger virialized structures.
 
@@
 $z=0.0, 0.25, 0.5$ and $1.0$.  The number of pairs at each redshift in
-each population is listed on the first arrow of Table
-\ref{table:numbers}.
+each population is listed on the first row of Table \ref{table:numbers}.
 
@@
 
-The first region has $\mu\approx-1$ and $D_{\rm off}>0.6$, which
+The first region has $\mu\sim-1$ and $D_{\rm off}>0.6$, which
 locates the systems where a head-on collision has just started. The
-second region has $\mu\approx 1$ and $D_{\rm off}<0.6$; at this stage
+second region has $\mu\sim 1$ and $D_{\rm off}<0.6$; at this stage
 the collision continues after the first crossing of the host's center,
@@
 displacements $D_{\rm off}>0.6$ suggest that this the maximum range of
-radii for the apogee.  The third region corresponds to $\mu\approx-1$
+radii for the apogee.  The third region corresponds to $\mu\sim-1$
 and $D_{\rm off}<0.6$ that is the the secondary infall after apogee.
@@
 trajectories, have a baryonic displacement equal to zero.  In systems
-with head-on collissions, $|\mu|>0.9$, we distinguish two different
-cases. The first one, systems with  $\mu<-0.9$ and large displacements $D_{\rm
-  off}>0.6$ most probably describe the beginning of the interaction
-and should have baryonic displacements equal to zero.
-In all the other cases, the DM-baryon displacement
-should be equal to zero. We approximate this displacement by  $d_{\rm
+with head-on collissions, $|\mu|>0.9$, we distinguish ystems with
+$\mu<-0.9$ and large displacements $D_{\rm   off}>0.6$ most probably
+describe the beginning of the interaction and should have baryonic
+displacements equal to zero. In all the other cases, the DM-baryon displacement
+should be different from zero. We approximate this displacement by  $d_{\rm
   2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
@@
 Considering that the statistics for the cluster sample are dominated
-by objects in the mass range of the \bullg we make a comparison
+by objects in the mass range of the \bullg\ we make a comparison
 against this sample. Table \ref{table:numbers} shows that $\sim 40\%$ of the 
@@
 observations. A proper comparison must take into account all the observational
-uncertainties, biases, mixes between our two populations (groups \&
+uncertainties, biases and mixes between our two populations (groups \&
 clusters at different redshifts) to derive a stronger bound from
@@
 
-Neverthless, comparing the number for group and cluster samples in the
-last row of Table \ref{table:numbers} we can already predict that a
-fixed redshift the number density of halos in the groups sample similar to \bullg is
-$\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times larger than the
-estimate for halos in the group sample.
+Nevertheless, comparing the absolute number of systems with
+characteristics similar to \bullg\ in the group sample
+(last row of Table \ref{table:numbers}) we predict that its number
+density is $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times larger
+than the expected number density of \bullg\ systems in the cluster
+sample.
 

### 2014-03-29 paper/ms.tex
comments from Gael

@@
 similar to \bullg\ is $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times
-larger than the estimated value forclusters. These results open up
+larger than the estimated value for clusters. These results open up
 the possibility for a new statistical test of $\Lambda$CDM.
@@
 morphology (large DM-DM displacements) and estimate the amount of
-systems with a Bullet configuration  (large DM-baryon
+systems with a Bullet-like configuration  (large DM-baryon
 displacements). To this end we use a high resolution N-body
@@
 
-All the raw data used in this Letter is available through the Multidark database \footnote{\texttt{www.multidark.org}}
+All the raw data used in this Letter are available through the Multidark database \footnote{\texttt{www.multidark.org}}
 \citep{Riebe2013}.  Furthermore, in order to facilitate the
@@
 $300\kms < V_{\rm c, host}<700\kms$ and clusters with $V_{\rm
-  c,host}>700\kms$. These two samples are constructed at four redshifts:
-$z=0.0, 0.25, 0.5$ and $1.0$.  The number of pairs at each redshift in
-each population is listed on the first row of Table \ref{table:numbers}.
+  c,host}>700\kms$ ($\geq 8.0\times 10^{13}$\hMsun). These two samples
+are constructed at four redshifts: $z=0.0, 0.25, 0.5$ and $1.0$.  The
+number of pairs at each redshift in each population is listed on the
+first row of Table \ref{table:numbers}.
 
@@
 The geometrical configuration can be further described by the
-following quantities. The circular velocity of each component, $V_{\rm
-  c,host}$ for the host and $V_{\rm c, sub}$ for the sub-halo and the
+following quantities. The circular velocity of each component and the
 size of the host halo $R_{\rm vir}$. Another useful quantity computed
@@
 the host halo and its center of mass (computed from all the particles
-inside the $R_{\rm vir}$), $X_{\rm off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$, which serves as a
-measurement of how much the host halo is perturbed.
+inside the $R_{\rm vir}$), $X_{\rm
+  off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$, which serves as a measurement of how much the host halo is perturbed.
 
@@
 between two dominant DM clumps, $d_{\rm 2D}$ and the projected distance
-between the DM-baryonic clumps, $d_{\rm 2D}^{\rm bar}$.
+between the DM and the dominand baryonic clumps (in the case of
+clusters this corresponds to the gas), $d_{\rm 2D}^{\rm bar}$.
 
@@
 collision stages described in previous sections. To start with, we
-consider that systems with $|\mu|<0.9$, describing grazing
-trajectories, have a baryonic displacement equal to zero.  In systems
-with head-on collissions, $|\mu|>0.9$, we distinguish ystems with
-$\mu<-0.9$ and large displacements $D_{\rm   off}>0.6$ most probably
-describe the beginning of the interaction and should have baryonic
-displacements equal to zero. In all the other cases, the DM-baryon displacement
-should be different from zero. We approximate this displacement by  $d_{\rm
-  2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
+consider that systems with $|\mu|<0.9$ describing grazing
+trajectories have a baryonic displacement equal to zero.  In systems
+with head-on collissions, $|\mu|>0.9$ the systems with $\mu<-0.9$ and
+large displacements $D_{\rm   off}>0.6$ most probably describe the
+beginning of the interaction and should have baryonic displacements
+equal to zero. In all other cases the DM-baryon displacement
+should be different from zero. We approximate this displacement by
+$d_{\rm   2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
 the offset computed between the minium of potential and the center of
@@
 
-The results for the integrated distributions for $>d_{\rm 2D}^{\rm bar}$
+The results for the integrated distributions for $d_{\rm 2D}^{\rm bar}$
 are shown in Figure \ref{fig:baryonic_displacements}. The dashed lines
@@
 
-In this Letter we estimate the fraction of galaxy groups and clusters
+In this Letter we estimated the fraction of galaxy groups and clusters
 in a $\Lambda$CDM cosmology that could present observational features
@@
 $650$\kms was reported to feature a displacement between its baryonic
-(hot gas) and dark matter components.
+(gas) and dark matter components.
 
-We compute the distribution of projected displacements
+We computed the distribution of projected displacements
 between the dominant DM clumps in two kinds of systems; groups with
 circular velocities $300\kms<V_{\rm c}<700\kms$ ($1.0\times
-10^{13}\hMsun < M_{\rm vir}<1.0\times 10^{14}\hMsun$) and clusters with $V_{\rm
-  c}>700$\kms ($M_{\rm vir}>1.0\times 10^{14}\hMsun$). We report these
-results at four different redshifts $z=0.0,0.25,0.5$ and $10$. Our
+10^{13}\hMsun < M_{\rm vir}<8.0\times 10^{13}\hMsun$) and clusters with $V_{\rm
+  c}>700$\kms ($M_{\rm vir}>8.0\times 10^{13}\hMsun$). We reported these
+results at four different redshifts $z=0.0,0.25,0.5$ and $1$. Our
 results are based on large DM-only N-body cosmological simulation with
-a resolution that allows to study for the first time Bullet-like
+a resolution that allows us to study for the first time Bullet-like
 configurations in the mass range of galaxy groups.
@@
 Our main result is that a fraction of $40\%$-$60\%$ of the halos
-in the group sample present DM-DM displacement equal or larger than the
+in the group sample presents DM-DM displacement equal or larger than the
 observed displacement for \bullg. For halos in the cluster sample this
-fraction increases to $60\%$-$80\%$. We also derive an
-estimate for the DM-baryon displacement In the group sample
+fraction increases to $60\%$-$80\%$. We also derived an
+estimate for the DM-baryon displacement. In the group sample
 $0.1\%$-$1.0\%$ of the halos show a displacement equal or larger than
@@
 
-In terms of absolute numer densities, we expect to have $\sim 6.0\times
+In terms of absolute number densities, we expect to have $\sim 6.0\times
 10^{-7}$ Mpc$^{-3}$ groups similar to \bullg; three times the expected
@@
 that can be further exploited with upcoming lensing surveys (e.g. with
-the {\it Euclid} satellite).
+the {\it Euclid} satellite) and pushes for X-ray surveys with higher
+sensibility: chances are larger to find bullets in systems with lower
+X-ray luminosities.
 
@@
 Investigaciones through a FAPA starting grant.
+
+G.F. acknowledges support from FONDECYT through grant 3120160.
 

### 2014-03-31 paper/ms.tex
abstract update
Update ms.tex

@@
 dominant dark matter (DM) peaks (DM-DM displacements) and between
-DM and gaseous baryon peak (DM-baryon displacements) in DM halos 
+DM and gaseous baryon peak (DM-gas displacements) in dark matter halos 
 with masses larger than $10^{13}$\hMsun. We use as a benchmark the
@@
 featuring a bi-modal dark matter distribution with a dislocated
-baryonic component. We find that $(50 \pm 10)\%$ of the dark matter
+gas component. We find that $(50 \pm 10)\%$ of the dark matter
 halos with circular velocities in the range $300\kms$ to $700\kms$
@@
 velocities larger than $700\kms$ (clusters) this fraction rises to
-$(70 \pm 10)\%$. Using the same simulation we estimate the DM-baryon
+$(70 \pm 10)\%$. Using the same simulation we estimate the DM-gas
 displacements and find that $0.1$ to $1.0\%$ of the groups should
@@
 baryon separations. Considering both constraints on the DM-DM and
-DM-baryon displacements we find that the number density of groups
+DM-gas displacements we find that the number density of groups
 similar to \bullg\ is $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$, three times
 larger than the estimated value for clusters. These results open up
-the possibility for a new statistical test of $\Lambda$CDM.
+the possibility for a new statistical test of $\Lambda$CDM by looking
+for DM-gas displacements in low mass clusters and groups. 
 \end{abstract}
@@
 DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
-\citep{Dahle2013}. Recently \citep{Gastaldello} observed a DM-baryon
+\citep{Dahle2013}. Recently \citep{Gastaldello} observed a DM-gas
 displacement of $87\pm 14$\hkpc and a DM-DM separation of $186\pm
@@
 merger and  presenting a large displacement between the DM and
-baryonic components.  These two conditions (merger rates, maximum
+gaseous components.  These two conditions (merger rates, maximum
 possible displacement) are a funcion of DM halo mass in $\Lambda$CDM
@@
 morphology (large DM-DM displacements) and estimate the amount of
-systems with a Bullet-like configuration  (large DM-baryon
+systems with a Bullet-like configuration  (large DM-gas
 displacements). To this end we use a high resolution N-body
@@
 This Letter is organized as follows. In Section
-\ref{sec:simulation} we present the simulation and the halo catalogs
-used in this work. We continue in Section \ref{sec:setup} with the
-geometry of the problem at hand and the measurement setup. Next in
-Section \ref{sec:results} we present our results and observational
+\ref{sec:simulation} we present the simulation and the halo
+catalogs. We continue in Section \ref{sec:setup} with the  geometry of
+the problem at hand and the measurement setup. Next in   Section
+\ref{sec:results} we present our results and observational
 perspectives to finally conclude in Section \ref{sec:conclusions}.
@@
 $\Omega_{\Lambda}=0.73$, the Hubble parameter $h=0.7$, the
-normalization of the Power spectrum $n=0.95$ and the amplitude of mass
-density fluctuation (at redshift z$=$0) $\sigma_8=0.82$.  These
+slope of the primordial power spectrum $n=0.95$ and the amplitude of mass
+density fluctuations (at redshift z$=$0) $\sigma_8=0.82$.  These
 cosmological parameters are consistent with the nine-year Wilikinson
 Microwave Anisotropy Probe (WMAP) results \citep{hinshaw_etal13}. A
-detailed presentation of the simulation can be found in \citet{2011ApJ...740..102K}.
+detailed presentation of the simulation can be found in
+\citet{2011ApJ...740..102K}.
 
@@
 
-All the raw data used in this Letter are available through the Multidark database \footnote{\texttt{www.multidark.org}}
+All the raw data used in this Letter are available through the
+Multidark database \footnote{\texttt{www.multidark.org}}
 \citep{Riebe2013}.  Furthermore, in order to facilitate the
@@
 
-To construct our main halo sample we follow three
-steps. Firstly, we select all the host halos (i.e. halos that are not
-inside a larger halo) with circular velocities $V_{\rm c}\geq 300$\kms
-($\geq 1\times 10^{13} \hMsun$). Secondly, we select the sub-halos with
-circular velocities $V_{\rm c}\geq 75$\kms ($\geq 5\times
+To construct our main halo sample we follow three steps. Firstly, we
+select all the host halos (i.e. halos that are not inside a larger
+halo) with circular velocities $V_{\rm c}\geq 300$\kms ($\geq 1\times
+10^{13} \hMsun$). Secondly, we select the sub-halos with circular
+velocities $V_{\rm c}\geq 75$\kms ($\geq 5\times
 10^{10}\hMsun$). Thirdly, we associate each host halo to its most
@@
 potential Bullet system and is kept for the analysis described in the
-next Section. We use the sub-halos as the tracer of the sub-dominant
+next Section  by using the sub-halos as the tracer of the sub-dominant
 dark matter clump in the merging cluster, i.e. the bullets.
 
-Finally, we split the sample into two  populations; groups with
-$300\kms < V_{\rm c, host}<700\kms$ and clusters with $V_{\rm
+Finally, we split the sample into two  populations; groups, with
+$300\kms < V_{\rm c, host}<700\kms$; and clusters, with $V_{\rm
   c,host}>700\kms$ ($\geq 8.0\times 10^{13}$\hMsun). These two samples
@@
 Bullet-like configurations have two dominand dark matter structures:
-the host halo and the dominant sub-halo. We describe the kinematics of this configuration by the 
-position and velocity vectors of the sub-halo in a frame of reference
-where the main halo is at rest; thus
+the host halo and the dominant sub-halo. We describe the kinematics of
+this configuration by the  position and velocity vectors of the
+sub-halo in a frame of reference where the main halo is at rest; thus
 $\vec{v{}}=\vec{v}_{\rm sub}-\vec{v}_{\rm host}$ and
@@
 and $sub$ refer to the position of the minium of potential for the
-host and sub-halo in the frame of reference of the simulation, respectively.
+host and sub-halo in the frame of reference of the simulation,
+respectively.
 
@@
 The geometrical configuration can be further described by the
-following quantities. The circular velocity of each component and the
+the circular velocity of each component and the
 size of the host halo $R_{\rm vir}$. Another useful quantity computed
@@
 inside the $R_{\rm vir}$), $X_{\rm
-  off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$, which serves as a measurement of how much the host halo is perturbed.
+  off}=||\vec{r}_{min}-\vec{r}_{cm}||/R_{\rm vir}$, which serves as a
+measurement of how much the host halo is perturbed.
 
-In this letter we work with two quantities that could be inferred
+In this Letter we work with two quantities that could be inferred
 from observations of Bullet-like systems. The projected distance
-between two dominant DM clumps, $d_{\rm 2D}$ and the projected distance
-between the DM and the dominand baryonic clumps (in the case of
-clusters this corresponds to the gas), $d_{\rm 2D}^{\rm bar}$.
+between two dominant DM clumps, $d_{\rm 2D}$, and the projected distance
+between the DM and the gas clumps, $d_{\rm 2D}^{\rm bar}$.
 
@@
 relative to the virial radius $D_{\rm   off}= ||\vec{r}||_{\rm
-  2D}/R_{\rm vir}$. The second quantity, the projected DM-baryon
+  2D}/R_{\rm vir}$. The second quantity, the projected DM-gas
 distance, is not directly available from a DM-only simulation but can
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_1.eps}
+\includegraphics[width=0.9\textwidth]{figure_1_V3.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_2.eps}
+\includegraphics[width=1.0\textwidth]{figure_3_V3.eps}
 \end{center}
@@
   panel corresponds to clusters and the right panel to groups. The data
-  used to construct this histogram includes the halos at all redshifts.}
+  used to construct this histogram includes halos at all redshifts.}
 \label{fig:geometry}
@@
 second region has $\mu\sim 1$ and $D_{\rm off}<0.6$; at this stage
-the collision continues after the first crossing of the host's center,
-the low number of halos with radial infalling velocities and
-displacements $D_{\rm off}>0.6$ suggest that this the maximum range of
+the collision continues after the first crossing of the host's
+center. The low number of halos with radial infalling velocities and
+displacements $D_{\rm off}>0.6$ suggests that this the maximum range of
 radii for the apogee.  The third region corresponds to $\mu\sim-1$
@@
 
-In the next subsection we use the information in this sequence to
-estimate the expected DM-baryon displacement.
+In the next subsection we use the information in this collision
+sequence to estimate the expected DM-gas displacement.
 
-\subsection{DM-baryon Displacements}
+\subsection{DM-gas Displacements}
 \label{sec:baryonic_displacements}
@@
 The results we have derived so far apply to multi-modal systems and
-the expected separation between the two dominant dark matter
+their expected separation between the two dominant dark matter
 clumps. However, a non-zero DM-DM displacement does not imply 
-a non-zero DM-baryon displacement. Given that we use a DM only
-simulation, we have to find a way to estimate a DM-baryon displacement
-from the available information.
+a non-zero DM-gas displacement. We now estimate these displacements
+from the available information in our DM only simulation.
 
-This estimate is based on the different kinds of trajectories and
+Our estimates are based on the different kinds of trajectories and
 collision stages described in previous sections. To start with, we
 consider that systems with $|\mu|<0.9$ describing grazing
-trajectories have a baryonic displacement equal to zero.  In systems
+trajectories have a DM-gas displacement equal to zero.  In systems
 with head-on collissions, $|\mu|>0.9$ the systems with $\mu<-0.9$ and
 large displacements $D_{\rm   off}>0.6$ most probably describe the
-beginning of the interaction and should have baryonic displacements
-equal to zero. In all other cases the DM-baryon displacement
-should be different from zero. We approximate this displacement by
+beginning of the interaction and should have DM-gas displacements
+equal to zero as well. In all other cases the DM-gas displacement
+should be different from zero with the approximated value
 $d_{\rm   2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
@@
 collision has not started and should have $d_{2D}^{\rm bar}=0$. A detailed
-modeling of this fraction requires the study of the complete merger
-tree of the halo and sub-halo, a study beyond the scope of this
+modeling of this fraction requires the study of the complete merging
+history  of the halo and sub-halo, a study beyond the scope of this
 Letter. Instead we caution the reader that the derived fraction of
@@
 $\sim 2$ of our results. This gives us confidence in our approach to
-correctly estimate the expected fraction of groups with a DM-baryon
+correctly estimate the expected fraction of groups with a DM-gas
 displacement.
@@
 fraction of $0.1\%$ to $1\%$ of the groups are expected to have a
-DM-baryon displacement equal or larger than $87\pm 14$\hkpc as
+DM-gas displacement equal or larger than $87\pm 14$\hkpc as
 observed in \bullg. This fraction rises to $4\%$ to $10\%$ in the case
@@
 last row indicates the number of objects in the previous sub-sample
-with DM-baryon displacements $d_{\rm 2D}^{\rm bar}>87$\hkpc.
+with DM-gas displacements $d_{\rm 2D}^{\rm bar}>87$\hkpc.
 
@@
 against this sample. Table \ref{table:numbers} shows that $\sim 40\%$ of the 
-clusters are expected to have large DM-DM displacements, this is a
+clusters are expected to have large DM-DM displacements, which is a
 factor of $\sim 2$ larger than the observational estimate by
@@
 This rough comparison  shows that our estimates for the relative number of
-bullet systems (large DM-baryon displacements) with respect to
+bullet systems (large DM-gas displacements) with respect to
 multi-modal systems (large DM-DM displacements) is compatible with
@@
 \caption{Integrated probability distribution for the estimated
-  baryonic displacements in the group and cluster samples. Continous (dashed)
+  DM-gas displacements in the group and cluster samples. Continous (dashed)
   lines correspond to clusters (groups). The continuous black line
@@
   \citet{ForeroRomero2010} for a cosmological simulation including DM
-  and baryons. The vertical lines correspond to the mean value and
+  and gas. The vertical lines correspond to the mean value and
   uncertainty of the displacement measured for \bullg.} 
@@
   Gastaldello} we find that the relative number of bullets
-(large DM-baryon displacement) with respect to a general sample of
+(large DM-gas displacement) with respect to a general sample of
 multi-modal systems (large DM-DM displacements) is consistent with
@@
 
-In terms of absolute number densities, we expect to have $\sim 6.0\times
-10^{-7}$ Mpc$^{-3}$ groups similar to \bullg; three times the expected
-value for clusters. This opens up a new observational possibility with surveys
+Using the same criteria we find that in the simulation there there are
+$\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ groups similar to \bullg. This
+number density is three times larger than the computed value for
+clusters. This opens up a new observational possibility with surveys
 such as SL2S that target a large number of groups and estimate its
@@
 that can be further exploited with upcoming lensing surveys (e.g. with
-the {\it Euclid} satellite) and pushes for X-ray surveys with higher
+ he {\it Euclid} satellite) and pushes for X-ray surveys with higher
 sensibility: chances are larger to find bullets in systems with lower

### 2014-04-01 paper/ms.tex
new version for the co-authors
updated text
typo
submitted version

@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_1_V3.eps}
+\includegraphics[width=0.9\textwidth]{figure_1.eps}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_3_V3.eps}
+\includegraphics[width=1.0\textwidth]{figure_2.eps}
 \end{center}
@@
 and $8$ times less mass resolution than the Bolshoi Simulation. The
-fit is valid for separations larger than $70$\hkpc, beyond which we
+fit is valid for separations larger than $70\hkpc$, beyond which we
 find that it provides a remarkably good description within a factor of
@@
 associated to a bullet-like event. This is motivated by the recent
-observational results of \citep{Gastaldello} where a system (\bullg)
+observational results of \cite{Gastaldello} where a system (\bullg)
 on the mass range $1\times 10^{14}$\hMsun\ and velocity dispersion
@@
 $0.1\%$-$1.0\%$ of the halos show a displacement equal or larger than
-the  measurements of \bullg\ by \citep{Gastaldello}; in the cluster
+the  measurements of \bullg\ by \cite{Gastaldello}; in the cluster
 sample this fraction rises to $4\%$-$10\%$.
@@
 
-Using the same criteria we find that in the simulation there there are
+Using the same criteria we find that in the simulation there are
 $\sim 6.0\times 10^{-7}$ Mpc$^{-3}$ groups similar to \bullg. This
@@
 
-G.F. acknowledges support from FONDECYT through grant 3120160.
+J.G.F-T acknowledges support from Universidad de los Andes de Bogot\'a
+- Colombia and Centro de Investigaciones de Astronom\'ia (CIDA) -
+Venezuela.
+
+G.F. acknowledges support from FONDECYT through grant 3120160 and
+ECOS/CONICYT through grant C12U02.
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references} 
+\begin{thebibliography}{24}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Brada{\v c}} {et~al.}(2008){Brada{\v c}}, {Allen}, {Treu},
+  {Ebeling}, {Massey}, {Morris}, {von der Linden}, \& {Applegate}}]{Bradac2008}
+{Brada{\v c}}, M., {Allen}, S.~W., {Treu}, T., {Ebeling}, H., {Massey}, R.,
+  {Morris}, R.~G., {von der Linden}, A., \& {Applegate}, D. 2008, \apj, 687,
+  959
+
+\bibitem[{{Cabanac} {et~al.}(2007){Cabanac}, {Alard}, {Dantel-Fort}, {Fort},
+  {Gavazzi}, {Gomez}, {Kneib}, {Le F{\`e}vre}, {Mellier}, {Pello}, {Soucail},
+  {Sygnet}, \& {Valls-Gabaud}}]{Cabanac2007}
+{Cabanac}, R.~A., {Alard}, C., {Dantel-Fort}, M., {Fort}, B., {Gavazzi}, R.,
+  {Gomez}, P., {Kneib}, J.~P., {Le F{\`e}vre}, O., {Mellier}, Y., {Pello}, R.,
+  {Soucail}, G., {Sygnet}, J.~F., \& {Valls-Gabaud}, D. 2007, \aap, 461, 813
+
+\bibitem[{{Clowe} {et~al.}(2006){Clowe}, {Brada{\v c}}, {Gonzalez},
+  {Markevitch}, {Randall}, {Jones}, \& {Zaritsky}}]{Clowe2006}
+{Clowe}, D., {Brada{\v c}}, M., {Gonzalez}, A.~H., {Markevitch}, M., {Randall},
+  S.~W., {Jones}, C., \& {Zaritsky}, D. 2006, \apjl, 648, L109
+
+\bibitem[{{Dahle} {et~al.}(2013){Dahle}, {Sarazin}, {Lopez}, {Kouveliotou},
+  {Patel}, {Rol}, {van der Horst}, {Fynbo}, {Wijers}, {Burrows}, {Gehrels},
+  {Grupe}, {Ramirez-Ruiz}, \& {Micha{\l}owski}}]{Dahle2013}
+{Dahle}, H., {Sarazin}, C.~L., {Lopez}, L.~A., {Kouveliotou}, C., {Patel},
+  S.~K., {Rol}, E., {van der Horst}, A.~J., {Fynbo}, J., {Wijers}, R.~A.~M.~J.,
+  {Burrows}, D.~N., {Gehrels}, N., {Grupe}, D., {Ramirez-Ruiz}, E., \&
+  {Micha{\l}owski}, M.~J. 2013, \apj, 772, 23
+
+\bibitem[{{Dawson} {et~al.}(2012){Dawson}, {Wittman}, {Jee}, {Gee}, {Hughes},
+  {Tyson}, {Schmidt}, {Thorman}, {Brada{\v c}}, {Miyazaki}, {Lemaux}, {Utsumi},
+  \& {Margoniner}}]{Dawson2012}
+{Dawson}, W.~A., {Wittman}, D., {Jee}, M.~J., {Gee}, P., {Hughes}, J.~P.,
+  {Tyson}, J.~A., {Schmidt}, S., {Thorman}, P., {Brada{\v c}}, M., {Miyazaki},
+  S., {Lemaux}, B., {Utsumi}, Y., \& {Margoniner}, V.~E. 2012, \apjl, 747, L42
+
+\bibitem[{{Farrar} \& {Rosen}(2007)}]{Farrar2007}
+{Farrar}, G.~R., \& {Rosen}, R.~A. 2007, Physical Review Letters, 98, 171302
+
+\bibitem[{{Fo{\"e}x} {et~al.}(2013){Fo{\"e}x}, {Motta}, {Limousin}, {Verdugo},
+  {More}, {Cabanac}, {Gavazzi}, \& {Mu{\~n}oz}}]{Foex2013}
+{Fo{\"e}x}, G., {Motta}, V., {Limousin}, M., {Verdugo}, T., {More}, A.,
+  {Cabanac}, R., {Gavazzi}, R., \& {Mu{\~n}oz}, R.~P. 2013, \aap, 559, A105
+
+\bibitem[{{Forero-Romero} {et~al.}(2010){Forero-Romero}, {Gottl{\"o}ber}, \&
+  {Yepes}}]{ForeroRomero2010}
+{Forero-Romero}, J.~E., {Gottl{\"o}ber}, S., \& {Yepes}, G. 2010, \apj, 725,
+  598
+
+\bibitem[{{Gastaldello} {et~al.}(2014){Gastaldello}, {Limousin}, {Foex},
+  {Mu\~noz}, {Verdugo}, {Motta}, {More}, {Cabanac}, {Buote}, {Eckert},
+  {Ettori}, {Fritz}, {Ghizzardi}, {Humphrey}, {Meneghetti}, \&
+  M.}]{Gastaldello}
+{Gastaldello}, F., {Limousin}, M., {Foex}, G., {Mu\~noz}, R., {Verdugo}, T.,
+  {Motta}, V., {More}, A., {Cabanac}, R., {Buote}, D., {Eckert}, D., {Ettori},
+  S., {Fritz}, A., {Ghizzardi}, S., {Humphrey}, P., {Meneghetti}, M., \& M., R.
+  2014, \mnras\ accepted
+
+\bibitem[{{Hayashi} \& {White}(2006)}]{Hayashi2006}
+{Hayashi}, E., \& {White}, S.~D.~M. 2006, \mnras, 370, L38
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{hinshaw_etal13}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
+  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
+  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
+  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
+  {Wright}, E.~L. 2013, \apjs, 208, 19
+
+\bibitem[{{Klypin} {et~al.}(1999){Klypin}, {Gottl{\"o}ber}, {Kravtsov}, \&
+  {Khokhlov}}]{BDMb}
+{Klypin}, A., {Gottl{\"o}ber}, S., {Kravtsov}, A.~V., \& {Khokhlov}, A.~M.
+  1999, \apj, 516, 530
+
+\bibitem[{{Klypin} \& {Holtzman}(1997)}]{BDM}
+{Klypin}, A., \& {Holtzman}, J. 1997, ArXiv Astrophysics e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{2011ApJ...740..102K}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Kravtsov} {et~al.}(1997){Kravtsov}, {Klypin}, \&
+  {Khokhlov}}]{Kravtsov1997}
+{Kravtsov}, A.~V., {Klypin}, A.~A., \& {Khokhlov}, A.~M. 1997, \apjs, 111, 73
+
+\bibitem[{{Lee} \& {Baldi}(2012)}]{Lee2012}
+{Lee}, J., \& {Baldi}, M. 2012, \apj, 747, 45
+
+\bibitem[{{Lee} \& {Komatsu}(2010)}]{Lee2010}
+{Lee}, J., \& {Komatsu}, E. 2010, \apj, 718, 60
+
+\bibitem[{{Markevitch} {et~al.}(2004){Markevitch}, {Gonzalez}, {Clowe},
+  {Vikhlinin}, {Forman}, {Jones}, {Murray}, \& {Tucker}}]{Markevitch2004}
+{Markevitch}, M., {Gonzalez}, A.~H., {Clowe}, D., {Vikhlinin}, A., {Forman},
+  W., {Jones}, C., {Murray}, S., \& {Tucker}, W. 2004, \apj, 606, 819
+
+\bibitem[{{Merten} {et~al.}(2011){Merten}, {Coe}, {Dupke}, {Massey}, {Zitrin},
+  {Cypriano}, {Okabe}, {Frye}, {Braglia}, {Jim{\'e}nez-Teja}, {Ben{\'{\i}}tez},
+  {Broadhurst}, {Rhodes}, {Meneghetti}, {Moustakas}, {Sodr{\'e}}, {Krick}, \&
+  {Bregman}}]{Merten2011}
+{Merten}, J., {Coe}, D., {Dupke}, R., {Massey}, R., {Zitrin}, A., {Cypriano},
+  E.~S., {Okabe}, N., {Frye}, B., {Braglia}, F.~G., {Jim{\'e}nez-Teja}, Y.,
+  {Ben{\'{\i}}tez}, N., {Broadhurst}, T., {Rhodes}, J., {Meneghetti}, M.,
+  {Moustakas}, L.~A., {Sodr{\'e}}, Jr., L., {Krick}, J., \& {Bregman}, J.~N.
+  2011, \mnras, 417, 333
+
+\bibitem[{{More} {et~al.}(2012){More}, {Cabanac}, {More}, {Alard}, {Limousin},
+  {Kneib}, {Gavazzi}, \& {Motta}}]{More2012}
+{More}, A., {Cabanac}, R., {More}, S., {Alard}, C., {Limousin}, M., {Kneib},
+  J.-P., {Gavazzi}, R., \& {Motta}, V. 2012, \apj, 749, 38
+
+\bibitem[{{Poole} {et~al.}(2006){Poole}, {Fardal}, {Babul}, {McCarthy},
+  {Quinn}, \& {Wadsley}}]{Poole2006}
+{Poole}, G.~B., {Fardal}, M.~A., {Babul}, A., {McCarthy}, I.~G., {Quinn}, T.,
+  \& {Wadsley}, J. 2006, \mnras, 373, 881
+
+\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
+  {Turchaninov}}]{Riebe2013}
+{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
+  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
+  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Springel} \& {Farrar}(2007)}]{Springel2007}
+{Springel}, V., \& {Farrar}, G.~R. 2007, \mnras, 380, 911
+
+\bibitem[{{Thompson} \& {Nagamine}(2012)}]{Thompson2012}
+{Thompson}, R., \& {Nagamine}, K. 2012, \mnras, 419, 3560
+
+\end{thebibliography}
 

### 2014-04-15 paper/ms.tex
submitted version (figures in pdf)
updates for the referee

--- 2014-03-31 paper/ms.tex
@@
 \usepackage {graphicx}
-
+\usepackage{hyperref}
 \usepackage{amsmath} 
@@
 \newcommand{\bullg}{SL2S J08544-0121}
-\shorttitle{Bullet Groups}
+\shorttitle{Bullet groups}
 \shortauthors{Fern\'andez-Trincado et al.}
@@
 
-\title{The abundance of Bullet-Groups in $\Lambda$CDM}
+\title{The Abundance of Bullet-like Groups in $\Lambda$CDM}
 \author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
@@
 matter and baryonic component in a $\Lambda$CDM Universe
-\citep{ForeroRomero2010} or the substructure velocity required to
-produce such displacement \citep{Hayashi2006, Springel2007,
-  Thompson2012}. It has also been used to constrain the dark matter
-particle self-interaction cross section and to explore possible
-extensions to the concordance cosmological model
-\citep{Farrar2007,Lee2010,Lee2012}.
+\citep{ForeroRomero2010}, the substructure velocity required to
+produce such displacement
+\citep{Milosavljevic2007,Springel2007,Mastropietro20008} and its
+abundance in large N-body cosmological simulations
+\citep{Hayashi2006,Lee2012, Thompson2012}. It has also been used to
+constrain the dark matter particle self-interaction cross section and
+to explore possible extensions to the concordance cosmological model
+\citep{Farrar2007,Lee2010}.
 
@@
 displacement of $87\pm 14$\hkpc and a DM-DM separation of $186\pm
-30$\hkpc in \bullg, a group-like system with a total
+30$\hkpc in \bullg, a low mass cluster system with a total
 mass $2.4\pm 0.6 \times 10^{14}\Msun$ found in the the Strong Lensing
@@
 
-Groups around this mass are $\sim10$ times more abundant than clusters
-in the mass range of the Bullet Cluster $>10^{15}$\hMsun. This 
-should open up the possibility of finding Bullet Groups in large
-numbers to test $\Lambda$CDM. However, a larger abundance of small
-mass systems has to be weighted by the probability of being in a
-merger and  presenting a large displacement between the DM and
-gaseous components.  These two conditions (merger rates, maximum
-possible displacement) are a funcion of DM halo mass in $\Lambda$CDM
-cosmologies.  A detailed statistical study to estimate the DM-gas
-displacements of Bullets has been performed for clusters
-\citep{ForeroRomero2010} but not for lower mass systems.
+Using a Sheth-Mo-Tormen mass function at $z=0$, one can estimate that
+systems around this mass are $\sim 65$ times more abundant than massive
+clusters in the mass range of the Bullet Cluster $>10^{15}$\hMsun
+\citep{Sheth2001,hmfcalc}. This  should open up the possibility of
+finding Bullet-like groups in large numbers to test
+$\Lambda$CDM. However, a larger abundance of small mass systems has to
+be weighted by the probability of being in a merger and  presenting a
+large displacement between the DM and gaseous components.  These two
+conditions (merger rates, maximum possible displacement) are a funcion
+of DM halo mass in $\Lambda$CDM cosmologies.  A detailed statistical
+study to estimate the DM-gas displacements of bullets has been
+performed for clusters \citep{ForeroRomero2010} but not for lower mass
+systems.
 
@@
 We use the Bolshoi Run, a cosmological DM only simulation over a cubic
-volume of 250\hMpc comoving on a side. The simulation uses the ART
-code \citep{Kravtsov1997} to follow the evolution of a dark matter
-density field from $z=80$ to $z=0$ sampled with $2048^3$  particles. The
-cosmology used  corresponds to  the spatially flat concordance model
-with the following parameters:  the density parameter for matter (dark
-matter and baryons) $\Omega_m=0.27$, the density parameter for baryonic matter
+volume of 250\hMpc comoving on a side \citep{2011ApJ...740..120K}. The
+simulation uses the ART code \citep{Kravtsov1997} to follow the
+evolution of a dark matter density field from $z=80$ to $z=0$ sampled
+with $2048^3$  particles. The cosmology used  corresponds to  the
+spatially flat concordance model with the following parameters:  the
+density parameter for matter (dark matter and baryons)
+$\Omega_m=0.27$, the density parameter for baryonic matter
 $\Omega_b=0.0469$, the density parameter for dark energy
-$\Omega_{\Lambda}=0.73$, the Hubble parameter $h=0.7$, the
-slope of the primordial power spectrum $n=0.95$ and the amplitude of mass
+$\Omega_{\Lambda}=0.73$, the Hubble parameter $h=0.7$, the slope of
+the primordial power spectrum $n=0.95$ and the amplitude of mass
 density fluctuations (at redshift z$=$0) $\sigma_8=0.82$.  These
@@
 All the raw data used in this Letter are available through the
-Multidark database \footnote{\texttt{www.multidark.org}}
+Multidark database \footnote{\url{www.multidark.org}}
 \citep{Riebe2013}.  Furthermore, in order to facilitate the
@@
 the data and the source code available in a public
-repository \footnote{\texttt{https://github.com/Fernandez-Trincado/Bullet\_Groups-2014}}.
+repository \footnote{\url{https://github.com/Fernandez-Trincado/Bullet\_Groups-2014}}.
 
@@
 Each one of the pairs (host \& sub-halo) is considered as a
-potential Bullet system and is kept for the analysis described in the
+potential bullet system and is kept for the analysis described in the
 next Section  by using the sub-halos as the tracer of the sub-dominant
@@
 
-Bullet-like configurations have two dominand dark matter structures:
+Bullet-like configurations have two dominant dark matter structures:
 the host halo and the dominant sub-halo. We describe the kinematics of
@@
 $\vec{r{}}=\vec{r}_{\rm sub}-\vec{r}_{\rm host}$, where the subscripts $host$
-and $sub$ refer to the position of the minium of potential for the
-host and sub-halo in the frame of reference of the simulation,
-respectively.
+and $sub$ refer to the host and sub-halo, respectively. The positions
+$\vec{r}$ correspond to the minium of potential and the velocities
+$\vec{v}$ are computed as an average of the bulk velocities of all
+simulation particles in the structure of interest.
 
@@
 between two dominant DM clumps, $d_{\rm 2D}$, and the projected distance
-between the DM and the gas clumps, $d_{\rm 2D}^{\rm bar}$.
+between the DM and the gas clumps, $d_{\rm 2D}^{\rm bar}$. The
+projection is computed along the same axis for all halos at all
+redshifts, we present the result of the projection along the $z$-axis
+of the simulation.
 
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_1_V3.eps}
+\includegraphics[width=0.9\textwidth]{figure_1.pdf}
 \end{center}
@@
 with the projected 2D physical displacements also shows a vertical
-stripe with the estimated displacement for the Bullet-group reported
+stripe with the estimated displacement for the bullet group reported
 by \cite{Gastaldello}.
@@
 \begin{center}
-\includegraphics[width=1.0\textwidth]{figure_3_V3.eps}
+\includegraphics[width=1.0\textwidth]{figure_2.pdf}
 \end{center}
@@
   panel corresponds to clusters and the right panel to groups. The data
-  used to construct this histogram includes halos at all redshifts.}
+  used to construct this histogram includes halos at all
+  redshifts. This approximation to increase the statistical power of
+  the sample is justified because the redshift evolution of this plot
+  is weak.} 
 \label{fig:geometry}
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_3.eps}
+\includegraphics[width=0.9\textwidth]{figure_3.pdf}
 \end{center}
@@
 in a $\Lambda$CDM cosmology that could present observational features
-associated to a bullet-like event. This is motivated by the recent
-observational results of \citep{Gastaldello} where a system (\bullg)
+associated to a Bullet-like event. This is motivated by the recent
+observational results of \cite{Gastaldello} where a system (\bullg)
 on the mass range $1\times 10^{14}$\hMsun\ and velocity dispersion
@@
 a rough comparison using the observational criteria \citep{Foex2013,
-  Gastaldello} we find that the relative number of bullets
+  Gastaldello} we find that the relative number of Bullet-like systems
 (large DM-gas displacement) with respect to a general sample of

### 2014-04-16 paper/ms.tex
updated

@@
 
-\title{The Abundance of Bullet-like Groups in $\Lambda$CDM}
+\title{The Abundance of Bullet Groups in $\Lambda$CDM}
 \author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
@@
 produce such displacement
-\citep{Milosavljevic2007,Springel2007,Mastropietro20008} and its
+\citep{Milosavljevic2007,Springel2007,Mastropietro2008} and its
 abundance in large N-body cosmological simulations
@@
 We use the Bolshoi Run, a cosmological DM only simulation over a cubic
-volume of 250\hMpc comoving on a side \citep{2011ApJ...740..120K}. The
+volume of 250\hMpc comoving on a side \citep{2011ApJ...740..102K}. The
 simulation uses the ART code \citep{Kravtsov1997} to follow the
@@
 Each one of the pairs (host \& sub-halo) is considered as a
-potential bullet system and is kept for the analysis described in the
+potential Bullet-like system and is kept for the analysis described in the
 next Section  by using the sub-halos as the tracer of the sub-dominant
@@
 \end{center}
-\caption{2D histograms in the plane $\mu$-$D_{\rm off}$. The left
-  panel corresponds to clusters and the right panel to groups. The data
-  used to construct this histogram includes halos at all
-  redshifts. This approximation to increase the statistical power of
-  the sample is justified because the redshift evolution of this plot
-  is weak.} 
+\caption{2D histograms in the plane $\mu$-$D_{\rm off}$ describing the
+  geometry of the bullet encounter. The left
+  panel corresponds to clusters and the right panel to groups. 
+  The weak redshift evolution of the structure in these planes
+  allows us to include halos at all redshifts to construct these figures.
+  The three rectangles (continous, dashed, dashed-dotted)
+  delimit stages of interest in a head-on collision as described in
+  Section \ref{sec:geometry}.}
 \label{fig:geometry}
@@
 second pass through the center of the host halo \citep{Poole2006}.
+These regions are shown as three different rectangled in Figure
+\ref{fig:geometry}.
 
-The first region has $\mu\sim-1$ and $D_{\rm off}>0.6$, which
+The first region has $\mu<-0.9$ and $D_{\rm off}>0.6$, which
 locates the systems where a head-on collision has just started. The
-second region has $\mu\sim 1$ and $D_{\rm off}<0.6$; at this stage
+second region has $\mu>0.9$ and $D_{\rm off}<0.6$; at this stage
 the collision continues after the first crossing of the host's
@@
 displacements $D_{\rm off}>0.6$ suggests that this the maximum range of
-radii for the apogee.  The third region corresponds to $\mu\sim-1$
+radii for the apogee.  The third region corresponds to $\mu<-0.9$
 and $D_{\rm off}<0.6$ that is the the secondary infall after apogee.
@@
 \begin{center}
-\includegraphics[width=0.9\textwidth]{figure_3.pdf}
+\includegraphics[width=0.8\textwidth]{figure_3.pdf}
 \end{center}
@@
 
+We thank the referee for a report that improved the readibility of our
+results. 
 J.E.F-R acknowledges support from Vicerrector\'ia de

### 2014-04-16 paper/ms.tex
sent to coauthors

@@
 
-\title{The Abundance of Bullet Groups in $\Lambda$CDM}
+\title{The abundance of Bullet-Groups in $\Lambda$CDM}
 \author{J. G. Fern\'andez-Trincado$^{1,2,3}$, J. E. Forero-Romero$^1$,
@@
 large displacement between the DM and gaseous components.  These two
-conditions (merger rates, maximum possible displacement) are a funcion
+conditions (merger rates, maximum possible displacement) are a function
 of DM halo mass in $\Lambda$CDM cosmologies.  A detailed statistical
@@
 and $sub$ refer to the host and sub-halo, respectively. The positions
-$\vec{r}$ correspond to the minium of potential and the velocities
+$\vec{r}$ correspond to the minimum of potential and the velocities
 $\vec{v}$ are computed as an average of the bulk velocities of all
@@
 %
-This encondes information about the collision, i.e. cases of
+This encodes information about the collision, i.e. cases of
 $|\mu|\sim 1$ can be considered as head-on collisions while
@@
   allows us to include halos at all redshifts to construct these figures.
-  The three rectangles (continous, dashed, dashed-dotted)
+  The three rectangles (continuous, dashed, dashed-dotted)
   delimit stages of interest in a head-on collision as described in
@@
 
-Figure \ref{fig:geometry} presents the geometry of the intereactions using the 
+Figure \ref{fig:geometry} presents the geometry of the interactions using the 
 variables $\mu$ and $D_{\rm off}$. The first evident feature is that
-most of the configurations have head-on encouters, $|\mu|>0.9$
+most of the configurations have head-on encounters, $|\mu|>0.9$
 ($\theta\leq 30^{\circ}$), while only a minority with $|\mu|<0.9$ can
@@
 second pass through the center of the host halo \citep{Poole2006}.
-These regions are shown as three different rectangled in Figure
+These regions are shown as three different rectangles in Figure
 \ref{fig:geometry}.
@@
 trajectories have a DM-gas displacement equal to zero.  In systems
-with head-on collissions, $|\mu|>0.9$ the systems with $\mu<-0.9$ and
+with head-on collisions, $|\mu|>0.9$ the systems with $\mu<-0.9$ and
 large displacements $D_{\rm   off}>0.6$ most probably describe the
@@
 $d_{\rm   2D}^{\rm bar} = X_{\rm off} R_{\rm   vir}$, where $X_{\rm   off}$ is
-the offset computed between the minium of potential and the center of
+the offset computed between the minimum of potential and the center of
 mass for each host halo computed from all the matter inside the virial
@@
 in the SL2S sample. From the light distribution, only $34$ objects
-($\sim 42\%$) have regular isophotes, $33$ had ellongated
+($\sim 42\%$) have regular isophotes, $33$ had elongated
 isophotes (hints of merging system), and $13$ ($\sim 16\%$) had a
@@
 \caption{Integrated probability distribution for the estimated
-  DM-gas displacements in the group and cluster samples. Continous (dashed)
+  DM-gas displacements in the group and cluster samples. Continuous (dashed)
   lines correspond to clusters (groups). The continuous black line
@@
 sensibility: chances are larger to find bullets in systems with lower
-X-ray luminosities.
+X-ray luminosities.\\
+
+We thank the referee for a detailed report that improved the readability of
+this Letter.
 
@@
 
-We thank the referee for a report that improved the readibility of our
-results. 
-J.E.F-R acknowledges support from Vicerrector\'ia de
-Investigaciones through a FAPA starting grant.
-
 J.G.F-T acknowledges support from Universidad de los Andes de Bogot\'a
@@
 Venezuela.
+
+J.E.F-R acknowledges support from Vicerrector\'ia de
+Investigaciones through a FAPA starting grant.
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references} 
+\begin{thebibliography}{28}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Brada{\v c}} {et~al.}(2008){Brada{\v c}}, {Allen}, {Treu},
+  {Ebeling}, {Massey}, {Morris}, {von der Linden}, \& {Applegate}}]{Bradac2008}
+{Brada{\v c}}, M., {Allen}, S.~W., {Treu}, T., {Ebeling}, H., {Massey}, R.,
+  {Morris}, R.~G., {von der Linden}, A., \& {Applegate}, D. 2008, \apj, 687,
+  959
+
+\bibitem[{{Cabanac} {et~al.}(2007){Cabanac}, {Alard}, {Dantel-Fort}, {Fort},
+  {Gavazzi}, {Gomez}, {Kneib}, {Le F{\`e}vre}, {Mellier}, {Pello}, {Soucail},
+  {Sygnet}, \& {Valls-Gabaud}}]{Cabanac2007}
+{Cabanac}, R.~A., {Alard}, C., {Dantel-Fort}, M., {Fort}, B., {Gavazzi}, R.,
+  {Gomez}, P., {Kneib}, J.~P., {Le F{\`e}vre}, O., {Mellier}, Y., {Pello}, R.,
+  {Soucail}, G., {Sygnet}, J.~F., \& {Valls-Gabaud}, D. 2007, \aap, 461, 813
+
+\bibitem[{{Clowe} {et~al.}(2006){Clowe}, {Brada{\v c}}, {Gonzalez},
+  {Markevitch}, {Randall}, {Jones}, \& {Zaritsky}}]{Clowe2006}
+{Clowe}, D., {Brada{\v c}}, M., {Gonzalez}, A.~H., {Markevitch}, M., {Randall},
+  S.~W., {Jones}, C., \& {Zaritsky}, D. 2006, \apjl, 648, L109
+
+\bibitem[{{Dahle} {et~al.}(2013){Dahle}, {Sarazin}, {Lopez}, {Kouveliotou},
+  {Patel}, {Rol}, {van der Horst}, {Fynbo}, {Wijers}, {Burrows}, {Gehrels},
+  {Grupe}, {Ramirez-Ruiz}, \& {Micha{\l}owski}}]{Dahle2013}
+{Dahle}, H., {Sarazin}, C.~L., {Lopez}, L.~A., {Kouveliotou}, C., {Patel},
+  S.~K., {Rol}, E., {van der Horst}, A.~J., {Fynbo}, J., {Wijers}, R.~A.~M.~J.,
+  {Burrows}, D.~N., {Gehrels}, N., {Grupe}, D., {Ramirez-Ruiz}, E., \&
+  {Micha{\l}owski}, M.~J. 2013, \apj, 772, 23
+
+\bibitem[{{Dawson} {et~al.}(2012){Dawson}, {Wittman}, {Jee}, {Gee}, {Hughes},
+  {Tyson}, {Schmidt}, {Thorman}, {Brada{\v c}}, {Miyazaki}, {Lemaux}, {Utsumi},
+  \& {Margoniner}}]{Dawson2012}
+{Dawson}, W.~A., {Wittman}, D., {Jee}, M.~J., {Gee}, P., {Hughes}, J.~P.,
+  {Tyson}, J.~A., {Schmidt}, S., {Thorman}, P., {Brada{\v c}}, M., {Miyazaki},
+  S., {Lemaux}, B., {Utsumi}, Y., \& {Margoniner}, V.~E. 2012, \apjl, 747, L42
+
+\bibitem[{{Farrar} \& {Rosen}(2007)}]{Farrar2007}
+{Farrar}, G.~R., \& {Rosen}, R.~A. 2007, Physical Review Letters, 98, 171302
+
+\bibitem[{{Fo{\"e}x} {et~al.}(2013){Fo{\"e}x}, {Motta}, {Limousin}, {Verdugo},
+  {More}, {Cabanac}, {Gavazzi}, \& {Mu{\~n}oz}}]{Foex2013}
+{Fo{\"e}x}, G., {Motta}, V., {Limousin}, M., {Verdugo}, T., {More}, A.,
+  {Cabanac}, R., {Gavazzi}, R., \& {Mu{\~n}oz}, R.~P. 2013, \aap, 559, A105
+
+\bibitem[{{Forero-Romero} {et~al.}(2010){Forero-Romero}, {Gottl{\"o}ber}, \&
+  {Yepes}}]{ForeroRomero2010}
+{Forero-Romero}, J.~E., {Gottl{\"o}ber}, S., \& {Yepes}, G. 2010, \apj, 725,
+  598
+
+\bibitem[{{Gastaldello} {et~al.}(2014){Gastaldello}, {Limousin}, {Foex},
+  {Mu\~noz}, {Verdugo}, {Motta}, {More}, {Cabanac}, {Buote}, {Eckert},
+  {Ettori}, {Fritz}, {Ghizzardi}, {Humphrey}, {Meneghetti}, \&
+  {Rossetti}}]{Gastaldello}
+{Gastaldello}, F., {Limousin}, M., {Foex}, G., {Mu\~noz}, R., {Verdugo}, T.,
+  {Motta}, V., {More}, A., {Cabanac}, R., {Buote}, D., {Eckert}, D., {Ettori},
+  S., {Fritz}, A., {Ghizzardi}, S., {Humphrey}, P., {Meneghetti}, M., \&
+  {Rossetti}, M. 2014, \mnras\ accepted
+
+\bibitem[{{Hayashi} \& {White}(2006)}]{Hayashi2006}
+{Hayashi}, E., \& {White}, S.~D.~M. 2006, \mnras, 370, L38
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{hinshaw_etal13}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
+  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
+  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
+  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
+  {Wright}, E.~L. 2013, \apjs, 208, 19
+
+\bibitem[{{Klypin} {et~al.}(1999){Klypin}, {Gottl{\"o}ber}, {Kravtsov}, \&
+  {Khokhlov}}]{BDMb}
+{Klypin}, A., {Gottl{\"o}ber}, S., {Kravtsov}, A.~V., \& {Khokhlov}, A.~M.
+  1999, \apj, 516, 530
+
+\bibitem[{{Klypin} \& {Holtzman}(1997)}]{BDM}
+{Klypin}, A., \& {Holtzman}, J. 1997, ArXiv Astrophysics e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{2011ApJ...740..102K}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Kravtsov} {et~al.}(1997){Kravtsov}, {Klypin}, \&
+  {Khokhlov}}]{Kravtsov1997}
+{Kravtsov}, A.~V., {Klypin}, A.~A., \& {Khokhlov}, A.~M. 1997, \apjs, 111, 73
+
+\bibitem[{{Lee} \& {Baldi}(2012)}]{Lee2012}
+{Lee}, J., \& {Baldi}, M. 2012, \apj, 747, 45
+
+\bibitem[{{Lee} \& {Komatsu}(2010)}]{Lee2010}
+{Lee}, J., \& {Komatsu}, E. 2010, \apj, 718, 60
+
+\bibitem[{{Markevitch} {et~al.}(2004){Markevitch}, {Gonzalez}, {Clowe},
+  {Vikhlinin}, {Forman}, {Jones}, {Murray}, \& {Tucker}}]{Markevitch2004}
+{Markevitch}, M., {Gonzalez}, A.~H., {Clowe}, D., {Vikhlinin}, A., {Forman},
+  W., {Jones}, C., {Murray}, S., \& {Tucker}, W. 2004, \apj, 606, 819
+
+\bibitem[{{Mastropietro} \& {Burkert}(2008)}]{Mastropietro2008}
+{Mastropietro}, C., \& {Burkert}, A. 2008, \mnras, 389, 967
+
+\bibitem[{{Merten} {et~al.}(2011){Merten}, {Coe}, {Dupke}, {Massey}, {Zitrin},
+  {Cypriano}, {Okabe}, {Frye}, {Braglia}, {Jim{\'e}nez-Teja}, {Ben{\'{\i}}tez},
+  {Broadhurst}, {Rhodes}, {Meneghetti}, {Moustakas}, {Sodr{\'e}}, {Krick}, \&
+  {Bregman}}]{Merten2011}
+{Merten}, J., {Coe}, D., {Dupke}, R., {Massey}, R., {Zitrin}, A., {Cypriano},
+  E.~S., {Okabe}, N., {Frye}, B., {Braglia}, F.~G., {Jim{\'e}nez-Teja}, Y.,
+  {Ben{\'{\i}}tez}, N., {Broadhurst}, T., {Rhodes}, J., {Meneghetti}, M.,
+  {Moustakas}, L.~A., {Sodr{\'e}}, Jr., L., {Krick}, J., \& {Bregman}, J.~N.
+  2011, \mnras, 417, 333
+
+\bibitem[{{Milosavljevi{\'c}} {et~al.}(2007){Milosavljevi{\'c}}, {Koda},
+  {Nagai}, {Nakar}, \& {Shapiro}}]{Milosavljevic2007}
+{Milosavljevi{\'c}}, M., {Koda}, J., {Nagai}, D., {Nakar}, E., \& {Shapiro},
+  P.~R. 2007, \apjl, 661, L131
+
+\bibitem[{{More} {et~al.}(2012){More}, {Cabanac}, {More}, {Alard}, {Limousin},
+  {Kneib}, {Gavazzi}, \& {Motta}}]{More2012}
+{More}, A., {Cabanac}, R., {More}, S., {Alard}, C., {Limousin}, M., {Kneib},
+  J.-P., {Gavazzi}, R., \& {Motta}, V. 2012, \apj, 749, 38
+
+\bibitem[{{Murray} {et~al.}(2013){Murray}, {Power}, \& {Robotham}}]{hmfcalc}
+{Murray}, S.~G., {Power}, C., \& {Robotham}, A.~S.~G. 2013, Astronomy and
+  Computing, 3, 23
+
+\bibitem[{{Poole} {et~al.}(2006){Poole}, {Fardal}, {Babul}, {McCarthy},
+  {Quinn}, \& {Wadsley}}]{Poole2006}
+{Poole}, G.~B., {Fardal}, M.~A., {Babul}, A., {McCarthy}, I.~G., {Quinn}, T.,
+  \& {Wadsley}, J. 2006, \mnras, 373, 881
+
+\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
+  {Turchaninov}}]{Riebe2013}
+{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
+  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
+  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Sheth} {et~al.}(2001){Sheth}, {Mo}, \& {Tormen}}]{Sheth2001}
+{Sheth}, R.~K., {Mo}, H.~J., \& {Tormen}, G. 2001, \mnras, 323, 1
+
+\bibitem[{{Springel} \& {Farrar}(2007)}]{Springel2007}
+{Springel}, V., \& {Farrar}, G.~R. 2007, \mnras, 380, 911
+
+\bibitem[{{Thompson} \& {Nagamine}(2012)}]{Thompson2012}
+{Thompson}, R., \& {Nagamine}, K. 2012, \mnras, 419, 3560
+
+\end{thebibliography}
 

### 2014-04-16 paper/ms.tex
new figure

@@
 DLSCL J0916.2+2951 \citep{Dawson2012}, ZwCl 1234.0+02916
-\citep{Dahle2013}. Recently \citep{Gastaldello} observed a DM-gas
+\citep{Dahle2013}. Recently \cite{Gastaldello} observed a DM-gas
 displacement of $87\pm 14$\hkpc and a DM-DM separation of $186\pm

### 2014-04-17 paper/ms.tex
Update ms.tex
version for resubmission

@@
 }
-\email{jfernandezt87@gmail.com}
+\email{jfernandez@obs-besancon.fr}
 \email{je.forero@uniandes.edu.co}
@@
 $\vec{r}$ correspond to the minimum of potential and the velocities
-$\vec{v}$ are computed as an average of the bulk velocities of all
-simulation particles in the structure of interest.
+$\vec{v}$ are the center of mass velocities.
 
@@
 between the DM and the gas clumps, $d_{\rm 2D}^{\rm bar}$. The
-projection is computed along the same axis for all halos at all
-redshifts, we present the result of the projection along the $z$-axis
-of the simulation.
+projection is computed along the $z$-axis for all halos at all
+redshifts.
 
@@
 
-We thank the referee for a detailed report that improved the readability of
+We thank the referee for a detailed report that improved the clarity of
 this Letter.

### 2014-04-21 paper/ms.tex
new version for resubmission

@@
 abundance in large N-body cosmological simulations
-\citep{Hayashi2006,Lee2012, Thompson2012}. It has also been used to
+\citep{Hayashi2006,Lee2010, Thompson2012}. It has also been used to
 constrain the dark matter particle self-interaction cross section and
 to explore possible extensions to the concordance cosmological model
-\citep{Farrar2007,Lee2010}.
+\citep{Farrar2007,Lee2012}.
 
@@
 \caption{2D histograms in the plane $\mu$-$D_{\rm off}$ describing the
-  geometry of the bullet encounter. The left
-  panel corresponds to clusters and the right panel to groups. 
-  The weak redshift evolution of the structure in these planes
-  allows us to include halos at all redshifts to construct these figures.
-  The three rectangles (continuous, dashed, dashed-dotted)
-  delimit stages of interest in a head-on collision as described in
-  Section \ref{sec:geometry}.}
+  geometry of the bullet encounter. The left panel corresponds to
+  clusters and the right panel to groups.  The weak redshift evolution
+  of the structure in these planes allows us to include halos at all
+  redshifts to construct these figures. The three rectangles
+  (continuous, dashed, dot-dashed) roughly delimit stages of interest
+  in a head-on collision (initial infall, first crossing until apogee,
+  return after apogee) as described in Section 
+  \ref{sec:geometry}.}  
 \label{fig:geometry}
@@
 
-The first region has $\mu<-0.9$ and $D_{\rm off}>0.6$, which
-locates the systems where a head-on collision has just started. The
-second region has $\mu>0.9$ and $D_{\rm off}<0.6$; at this stage
-the collision continues after the first crossing of the host's
-center. The low number of halos with radial infalling velocities and
-displacements $D_{\rm off}>0.6$ suggests that this the maximum range of
-radii for the apogee.  The third region corresponds to $\mu<-0.9$
-and $D_{\rm off}<0.6$ that is the the secondary infall after apogee.
+The first region (continuous rectangle) has $\mu<-0.9$ and $D_{\rm
+  off}>0.6$, which locates the systems where a head-on collision has
+just started. The second region (dashed rectangle) has $\mu>0.9$ and
+$D_{\rm off}<0.6$; at this stage the collision continues after the
+first crossing of the host's center. The low number of halos with
+radial infalling velocities and displacements $D_{\rm off}>0.6$
+suggests that this the maximum range of radii for the apogee.  The
+third region (dot-dashed rectangle) corresponds to $\mu<-0.9$ and
+$D_{\rm off}<0.6$ that is the the secondary infall after apogee.
 
@@
 \bibliographystyle{apj}
-%\bibliography{references} 
 \begin{thebibliography}{28}
